### 2014-10-21 ms.tex
Dummy ApJ paper, fixes #5

\documentclass[chicago]{emulateapj}
\usepackage{graphicx,amsmath,natbib,bm}
\usepackage[none]{hyphenat}
\usepackage{amsfonts}
\usepackage[top=1.3in, bottom=-0.3in, left=0.9in, right=0.35in]{geometry}
\usepackage{times}
\linespread{1.01}

\shortauthors{Y. Hezaveh}
\begin{document}

\title{}
\author{Yashar D. Hezaveh, Phil Marshall}  
\affil{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, Stanford, CA, USA}

\begin{abstract}  
\noindent
\end{abstract}

\keywords{ black hole physics ---
gravitational lensing: strong ---
galaxies: formation ---
galaxies: high-redshift}

\section{introduction}

\section{Conclusion}

\acknowledgements{
}

\end{document}

### 2014-10-22 ms.tex
abstract written, added detection figure, #1

@@
 \linespread{1.01}
+\usepackage{enumitem}
 
@@
 
-\title{}
-\author{Yashar D. Hezaveh, Phil Marshall}  
+\title{Probing the inner kpc of massive lens galaxies with ALMA: Can the central images of strong lenses be detected?}
+\author{Yashar D. Hezaveh, Philip J. Marshall, Roger D. Blandford}  
 \affil{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, Stanford, CA, USA}
@@
 \noindent
+We examine the prospects of detecting demagnified images of gravitational lenses in observations of strongly lensed mm-wave molecular emission lines with ALMA.
+We model the lensing galaxies as a superposition of a dark matter component, a stellar population, and a central supermassive black hole and forecast the detection of the central images for a range of relevant parameters (e.g.
+stellar core and black hole mass).
+We find that over a large range of acceptable parameters, future deep observations of lensed molecular lines with ALMA will be able to detect the central images at $\gtrsim 3\sigma$ significance.
+We use Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios.
+
 \end{abstract}
+
+in Ferarrese 2006, $r_b$ varies from ~50 to 500 pc.
 

### 2014-10-23 ms.tex
caption for figure 2

@@
 
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, width=0.48\textwidth]{figures/f_02.eps}
+\centering
+\end{center}
+\caption{ Significance of detection of the central image as a function of the stellar core size.
+The colors correspond to different slopes of the stellar component.
+The solid curves correspond to a case without a SMBH while the dashed line show the result of a simulation which includes a $2\times10^8M_{\odot}$ SMBH at its center.
+\label{f:f2}}
+\end{figure}
+
 \section{Conclusion}

### 2014-10-23 ms.tex
sketching out introduction, #8

@@
 \usepackage{enumitem}
+\usepackage{framed}
 
@@
 \section{introduction}
+\begin{framed}
+Probing the inner 0.5 kpc is interesting because: \\ \\1) SMBHs are there \\2) Various DM models have different predictions \\3) The stellar population profile is contains information about past mergers and BH-stellar population interactions.
+\\
+\\
+Mapping the matter density and decomposing these different components can thus shed light on various astrophysical phenomena.
+%probing the inner 0.5 kpc of galaxies is interesting.
+1) they contain SMBHs and the relationship of the SMBH mass to galaxies is intriguing and interesting.
+Dark matter models also have different and interesting predictions for the density of the central regions of galaxies (e.g.
+cored DM, or SIDM predictions).
+In addition, the history of galaxy mergers and black hole-stellar population interactions can be encoded in the stellar light profiles, resulting in different stellar
+\end{framed}
+
+\begin{framed}
+Stellar light profiles:
+\\ \\
+1) Massive galaxies often exhibit cored surface brightness profiles.  \\% (Cores sizes of order 50 -- 500 pc).
+2) The most massive ellipticals are thought to form through gas-poor mergers.\\
+
+3) The central structure of a merger without gas is dominated by the more concentrated of the two progenitors: the steeper central density cusp survives. \\
+
+4) Since high-mass ellipticals are thought to be built from mergers of lower-mass ellipticals, which have steep central-density cusps, the cores in more massive ellipticals have to be the result of another (not merger) physical mechanism.
+\\
+
+5) The existence of cores thus, represents a challenge to our understanding of the merging process.\\
+
+6) ``Black hole scouring''  has been suggested to produce a core.
+\end{framed}
+
+\begin{framed}
+Explain ``Black hole scouring''.  \\
+...\\
+...\\
+...\\
+... whatever the mechanisms are, clear measurements of the central densities can be valuable to solve this puzzle and to shed light on the connection of SMBHs and galaxies. 
+\end{framed}
+
+\begin{framed}
+Strong lensing: \\  \\
+1) lensing is a well-known tool for mapping out mass \\ \\
+2) strong lenses have been used to measure the einstein mass (e.g., X et al.), and the density skopes (Y et al.). \\ \\
+3) Strong lensing formalism, predicts an odd number of images, with a central image that is \emph{demagnified} \\ \\
+4) it has been known that the flux (i.e.
+demagnification) of the central image is very sensitive to the very inner regions of the density profiles: very peaky, singular density profiles, demagnify the image by very large amounts, whereas cored or shallow profile will result in bright central images.
+\\ \\
+
+4) typically only an even number of images are observed,  suggesting that the central images are demagnified below the sensitivity of instruments. \\ \\
+
+5) Additionally, another reason for lack of detection is that the central image is located at the center of the lensing galaxy, where i) the sensitivity is lower, due to photon noise of the lens ii) it is difficult to distinguish the flux of the central image from the emission from the lens.
+iii) if in optical, since they pass through the centers of galaxies there's a high chance of large absorption (in the lens)
+\end{framed}
+
+\begin{framed}
+a review of central image observations, claims, and studies:\\ \\
+Winn et al 2004 \\ Rusin et al 2005 \\Inada et al 2005, etc.
+\end{framed}
+
+\begin{framed}
+Describe the newly discovered population of mm lenses + ALMA's observations: \\  \\
+1) strong lenses in mm were discovered (SPT, Herschel, etc.) \\ \\
+2) ALMA observations confirmed that they're all lensed and that the sources are at high z \\ \\
+3) because they were selected by flux, + the high sensitivity of ALMA $->$ SNR is very high \\ \\
+4) the sources have many molecular lines.
+If a central image of a \emph{molecular line} is observed it will be easily identifiable since it corresponds to the redshift of the source, and there will be no confusion that it may be associated with the lens.
+\\ \\
+5) since these lines are in mm, there's very little (if any) absorption in the lens, so the flux doesn't decrease due to absorption
+\end{framed}
+
+\begin{framed}
+motivation and description of the paper: \\ \\
+1) Long ALMA observations of these molecular lines are likely to be carried out for various reasons (e.g. power spectrum of dark matter, measuring the mass of background black holes) .  \\ \\
+2) In this paper we explore the possibility of detection of these central images in such deep observations, and investigate what we could learn about the innermost regions of galaxies from detection or non-detection of such central images.\\ \\
+3) the paper is organized as: section 2 describes the simulations, section 3 presents the results and discuss them and conclude in section 5 \\ \\
+4) we use $\Lambda$CDM cosmology of XXX
+\end{framed}
+
+\section{Simulations}
+\begin{framed} description
+\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
+\end{framed}
+
+\section{Results and Discussions}
+%\begin{framed}
+%\end{framed}
+
+%\begin{framed}
+%\end{framed}
+
+%\begin{framed}
+%\end{framed}
+
+%\begin{framed}
+%\end{framed}
+
+\newpage
 

### 2014-10-24 ms.tex
adding some placeholder figures
modifying fig 1: model density profile

@@
 
-in Ferarrese 2006, $r_b$ varies from ~50 to 500 pc.
+%in Ferarrese 2006, $r_b$ varies from ~50 to 500 pc.
 
@@
 \begin{framed} description
-\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
+We generate mock data cubes of gas emission in the source galaxy, lens the data cubes with a foreground halo, predict the ALMA visibilities, and use the visibilities to estimate the detection significance of the central image for various parameters.
+The gas in the source galaxy is modeled as a collection of 5 Gaussian clumps with FWHM of XX, distributed over XX kpc and each separated in a different channel.
+and an intrinsic velocity dispersion  of 10 $km/s$ (FWHM) similar to observations of \citet{Davis:13}. 
+The choice of two discrete rings is made to enforce resolving the inner 50 pc region for a black hole mass measurement.
+We point out, however, that assuming a more general case (e.g.
+an exponential disk) does not change the results \citep[see Figure 2 of ][]{Davis:2014}.
+The velocity integrated flux of the circumnuclear ring is set to 4 $mJy\, km/s$. 
+This value is calculated by scaling the flux of the circumnuclear CO gas in Arp 220 to to z=2 \citep{Sakamoto:99}.
+The rings are concentric and in circular orbits.
+The rotational velocity of each point in the rings is calculated based on the enclosed mass contributed from the galaxy mass model and the mass of the central black hole.
+The black hole is given a mass of $M_{\mathrm{BH}}=5\times 10^{8} M_{\odot}$.
+We model the galaxy density with an isothermal profile ($\rho\propto r^{-2}$) with a central velocity dispersion of 200 km/s. 
+The line-of-sight velocities are calculated to generate a frequency-position data cube.
+Figure \ref{f:f1} shows a velocity-position diagram extracted from the data cube.
+The data comprises 100 frequency channels covering 800 km/s.
+
+Each layer of the data cube is lensed with the foreground halo to  generate a lensed cube.
+We use a Singular Isothermal Ellipsoid (SIE) mass model for the lens galaxy \citep[$\rho\propto r^{-2}$,][]{Kormann:94}, placed at $z_l=0.5$ and place the source at $z_s=2.0$.
+The central velocity dispersion of the lens is set to 180 $km/s$, which is typical for galaxy-galaxy lensing systems \citep[e.g.][]{hezaveh:13b}.
+
+To predict the visibilities we calculate the ALMA $uv$-coverage for a 5-$hr$ long observation with the most extended antenna configuration (full array), using the $simobserve$ task of Common Astronomy Software Applications package, which results in an angular resolution of $\sim20\, \, milli$-$arcsec$ at an observing frequency of 240 GHz.
+The visibilities for each channel are calculated by computing the 2D Fourier transform of the corresponding layer of the data cube and resampling the Fourier transform maps over the uv-coverage. 
+The noise is estimated using ALMA sensitivity calculator for a channel width of 8 km/s at 240 GHz. 
+We use finite differencing of visibilities to calculate the Fisher information and the parameter covariance matrix to calculate the significance of black hole mass measurement.
+
+When the background source only consists of the two rings described above, the lens model parameters have large uncertainties and are mildly degenerate with the mass of the black hole. 
+A realistic source galaxy, however, will consists of many other components, extended over kilo-parsec scales, which if included in lens models, can strongly constrain the lens parameters.
+We run five simulations in which the background source is embedded in an extended Gaussian clump with a radius of 1 kpc and a flux of 1 Jy km/s \citep[typical for SMGs, see][]{Bothwell:12}.
+We find that in these simulations, the lens parameters are extremely constrained and the effect of marginalization over them barely reduces the significance of black hole mass measurements ($\lesssim 0.05\, \sigma$).
+This suggests that when the full structure of the source galaxies are included in models, the lens parameters do not significantly contribute to the black hole mass uncertainties.
+Therefore, to reduce the computational cost of simulations, we do not marginalize over the lens parameters.
+%\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
 \end{framed}
@@
 \centering
-\includegraphics[trim= 0 0 0 0, width=0.48\textwidth]{figures/f_02.eps}
+\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
+\centering
+\end{center}
+\caption{ illustration of the central image in 2 cases: 
+\label{f:f2}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_02.eps}
+\centering
+\end{center}
+\caption{ illustration of the central image in 2 cases: 
+\label{f:f2}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_03.eps}
 \centering
@@
 The solid curves correspond to a case without a SMBH while the dashed line show the result of a simulation which includes a $2\times10^8M_{\odot}$ SMBH at its center.
+\label{f:f2}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04.eps}
+\centering
+\end{center}
+\caption{ Covariance matrix of parameters for a few different scenarios.
 \label{f:f2}}

### 2014-10-24 ms.tex
modifying fig 1: model density profile

@@
 \end{center}
-\caption{ illustration of the central image in 2 cases: 
+\caption{ Model density profiles.
+The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
+the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006.
+The red solid curve shows our cored-powerlaw model that we use to approximate this stellar component.
+The solid black line shows the total matter density (dark plus stellar) of our model.
 \label{f:f2}}

### 2014-10-26 ms.tex
modifying fig 1: model density profile, close#9
sketch of discussion and new figures

@@
 
-\title{Probing the inner kpc of massive lens galaxies with ALMA: Can the central images of strong lenses be detected?}
+\title{Probing the inner kpc of massive galaxies with strong gravitational lensing}
 \author{Yashar D. Hezaveh, Philip J. Marshall, Roger D. Blandford}  
@@
 
+\newpage
 \section{Results and Discussions}
-%\begin{framed}
-%\end{framed}
+\begin{framed}
+\subsection{Detection of central images}
+1) We evaluate the detection significance of central images over a range of relevant parameters. \\ \\
+2) Figure 4 shows our results for a 10-hr long observation with ALMA\\ \\
+3) we show that, as expected, the image is fainter for steeper profile slopes. \\ \\
+4) the 0.9 value (combined with 0.1 DM) results in the isothermal profile, which has been shown to be consistent with strong lensing data \\ \\
+5) if that's the case, and in the absence of massive BHs, then stellar cores as small as $\sim80$ pc should allow a 5$\sigma$ detection of the central images. \\ \\
+5A) we note that for much shallower density profiles, the central image is actually \emph{magnified}, and therefore it's detection should be trivial.\\ \\
+6) the flux is significantly supressed by the central SMBH \\  \\
+7) the dashed curves show the same for a galaxy with a $2e8M_{\odot}$ SMBH. \\ \\
+8) we note that although for some parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is no chance of detecting the central image, over a significant fraction of allowed parameters the central image could be detected.
+\\ \\
+9) to calculate this plot we have used a configuration XX, because: it allows us to resolve the central image (if existent), while it is more sensitive that more extended configurations.
+In addition, this is the configuration that will be likely used for other projects/sciences.
+\end{framed}
 
-%\begin{framed}
-%\end{framed}
+\begin{framed}
+\subsection{SMBHs and the core size}
+1) in this section we study how well we can constrain the mass of the central black hole, the slope of the density and the size of the stellar core. \\ \\
+2) we choose a few models where the central image is detected OR not detected and use a Fisher analysis to determine the degeneracies between the parameters and the detection significance of each parameter.
+\\ \\
+3) we note that in the Fisher analysis we include all nuisance parameters (e.g. source position, size, etc.) and marginalize over them  \\ \\
+4) Figure 4 shows the parameters for a case with $R_{core}$=180 pc, $M_{BH}=1e8$ and $\gamma=1$.
+As seen from Figure 3,  this parameter combination results in a faint ($\sim3\sigma$) detection of the central image.
+\\ \\
+5) we note that the black hole mass is degenerate with the core size: a larger core, results in a brighter image, which can be supressed by a more massive BH. \\ \\
+6) The Fisher data show that the black hole mass cannot be measured with high significance in such observations ($1.16\sigma$) \\ \\
+7) however, interestingly, the degeneracy of the black hole mass and the size of the central core breaks at the high end. and the stellar core is measured with XX $\sigma$\\ \\
+8) this is likely because a very large core results in a fairly extended central images, which could be \emph{resolved} (see Figure 1), in that case, the flux suppression by a crazy massive black hole will result in a distinct dip in the central image  which can be used to distinguish the two.
+\\ \\
+9) we note that the constraints in this case will be of similar strength to those of Winn 2004. \\ \\ 
+10) in the case of very small core, and a massive black hole (no detection of the image) we only get an upper limits of $\sim$ and $\sim$ for the two. \\ \\
+11) and in case with massive core and massive black hole we measure both with high significance. 
+12) we note that all these parameter combinations are plausible choices, and therefore long observations such as these will be able to either measure these parameters with confidence or place strong constraints on them.
+
+\end{framed}
 
@@
 \newpage
-
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
-\centering
-\end{center}
-\caption{ Model density profiles.
-The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
-the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006.
-The red solid curve shows our cored-powerlaw model that we use to approximate this stellar component.
-The solid black line shows the total matter density (dark plus stellar) of our model.
-\label{f:f2}}
-\end{figure}
 
@@
 \centering
+\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
+\centering
+\end{center}
+\caption{ Model density profiles.
+The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
+the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006.
+The red solid curve shows our cored-power-law model that we use to approximate this stellar component.
+The solid black line shows the total matter density (dark plus stellar) of our model.
+\label{f:f2}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\centering
 \includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_03.eps}
@@
 \end{center}
-\caption{ Significance of detection of the central image as a function of the stellar core size.
+\caption{ Significance of detection of the central image as a function of the stellar core size for a 10-hr long ALMA observation.
 The colors correspond to different slopes of the stellar component.

### 2014-10-26 ms.tex
modifying introduction

@@
 \begin{framed}
-Probing the inner 0.5 kpc is interesting because: \\ \\1) SMBHs are there \\2) Various DM models have different predictions \\3) The stellar population profile is contains information about past mergers and BH-stellar population interactions.
-\\
-\\
-Mapping the matter density and decomposing these different components can thus shed light on various astrophysical phenomena.
+Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super massive black holes (SMBH), galaxy formation, and dark matter.
+It is now established that almost every massive galaxy harbors a SMBH at its center \citep[][]{} with a mass that strongly correlates with the mass of the host galaxy.
+In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions.
+\citep{}.
+Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g][]{rochaetal}.
+Mapping the matter density in the central regions of galaxies can therefore shed light on various astrophysical phenomena.
 %probing the inner 0.5 kpc of galaxies is interesting.
@@
 \begin{framed}
-Stellar light profiles:
-\\ \\
-1) Massive galaxies often exhibit cored surface brightness profiles.  \\% (Cores sizes of order 50 -- 500 pc).
-2) The most massive ellipticals are thought to form through gas-poor mergers.\\
-
-3) The central structure of a merger without gas is dominated by the more concentrated of the two progenitors: the steeper central density cusp survives. \\
-
-4) Since high-mass ellipticals are thought to be built from mergers of lower-mass ellipticals, which have steep central-density cusps, the cores in more massive ellipticals have to be the result of another (not merger) physical mechanism.
-\\
-
-5) The existence of cores thus, represents a challenge to our understanding of the merging process.\\
+%Stellar light profiles:
+%\\ \\
+Morphological studies of galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging between 50 to 500 pc \citep{e.g.ferrarese06}.
+These galaxies are thought to form through gas-poor mergers.
+In such mergers, the central structure of the resulting galaxy is dominated by the inner structure of the more concentrated progenitor.
+Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, which have steep profiles, the cores in massive ellipticals may result from a different (not merger) physical mechanism.
+The existence of cores in these galaxies thus represents a challenge to our understanding of the merging process.
 
@@
 \begin{framed}
-a review of central image observations, claims, and studies:\\ \\
-Winn et al 2004 \\ Rusin et al 2005 \\Inada et al 2005, etc.
+a review of central image observations and studies:\\ \\
+
+1) The individual and statistical properties of central images have been previously studied. (e.g. Wallington 1993, Evans \& Hunter 2002, Keeton 2003, ) \\ \\
+2) to avoid absorption by, and lack of contamination from the main lens, past studies focused on radio lens quasars. \\ \\
+3) for example, Rusin \&  Ma 2001 set constrains on the inner profiles of lens galaxies form observations of six two-image radio-loud lens systems \\ \\
+4) confusion between a central image, and faint radio emission from the lens galaxy, could be avoided by studying the radio spectrum of a candidate central image.   
+5) the only secure detection of a central image (based on its radio spectrum)  in a galaxy-mass lensing system, is PMNJ 1632?0033 (Winn et al. 2002, 2003, 2004),   \\ \\
+6) Winn et al 2004 used the detection of this central image to place constraints on the mass of the central SMBH.
 \end{framed}
@@
 2) ALMA observations confirmed that they're all lensed and that the sources are at high z \\ \\
-3) because they were selected by flux, + the high sensitivity of ALMA $->$ SNR is very high \\ \\
+3) because they were selected by flux, + the high sensitivity of ALMA $->$ SNR is high \\ \\
+3B) we note that in a 10 hr long observation ALMA can achieve a sensitivity of order 0.0164 mJy in a 500 km/s bandwidth, since the background sources have typical (intrinsic) average line fluxes of order 2-3 mJy, such observations will be able to detect images with magnification as low as $10^{-2}$ \\ \\
 4) the sources have many molecular lines.
@@
 7) the dashed curves show the same for a galaxy with a $2e8M_{\odot}$ SMBH. \\ \\
-8) we note that although for some parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is no chance of detecting the central image, over a significant fraction of allowed parameters the central image could be detected.
+8) we note that, as pointed out in Keeton 2003, there's a large range of possibilities for plausible lens parameters: although for some parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is no chance of detecting the central image, over a significant fraction of allowed parameters the central image could be detected.
 \\ \\
@@
 8) this is likely because a very large core results in a fairly extended central images, which could be \emph{resolved} (see Figure 1), in that case, the flux suppression by a crazy massive black hole will result in a distinct dip in the central image  which can be used to distinguish the two.
+Rusin  Keeton Winn 2005 %http://adsabs.harvard.edu/abs/2005ApJ...627L..93R
 \\ \\
+
 9) we note that the constraints in this case will be of similar strength to those of Winn 2004. \\ \\ 

### 2014-10-27 ms.tex
modifying introduction

@@
 \section{introduction}
-\begin{framed}
+%\begin{framed}
 Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super massive black holes (SMBH), galaxy formation, and dark matter.
@@
 In addition, the history of galaxy mergers and black hole-stellar population interactions can be encoded in the stellar light profiles, resulting in different stellar
-\end{framed}
+%\end{framed}
+
+%\begin{framed}
+%Stellar light profiles:
+%\\ \\
+Morphological studies of galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep{e.g.ferrarese06}.
+These galaxies are thought to form through gas-poor mergers.
+In such mergers, the central structure of the resulting galaxy is dominated by the inner structure of the more concentrated progenitor.
+Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy mergers.
+Cores in massive ellipticals, therefore, should be the result of different (not merger) mechanisms.
+``Black hole scouring'' is currently the only known plausible mechanism that could explain core-formation in these galaxies \citep{Thomas2014}.
+%\end{framed}
+
+%\begin{framed}
+It is thought that during a merger, the SMBHs of the two merging galaxies form a binary which sinks to the center of the potential.
+The two orbiting SMBH then dissipate angular momentum through three-body interactions with nearby central stars, pushing them to higher orbits and scouring out a core.
+This angular momentum loss then allows the two black holes to merge.
+\citep{Begelman et al.
+1980}
+Previous studies have shown that the core sizes in these galaxies scales with the mass of their SMBH in agreement with theoretical predictions (Graham 2004; Kormendy \& Bender 2009; Kormendy \& Ho 2013).
+Such measurements, are, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high angular resolutions.
+% ... whatever the mechanisms are, clear measurements of the central densities can be valuable to solve this puzzle and to shed light on the connection of SMBHs and galaxies. 
+%\end{framed}
 
 \begin{framed}
-%Stellar light profiles:
-%\\ \\
-Morphological studies of galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging between 50 to 500 pc \citep{e.g.ferrarese06}.
-These galaxies are thought to form through gas-poor mergers.
-In such mergers, the central structure of the resulting galaxy is dominated by the inner structure of the more concentrated progenitor.
-Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, which have steep profiles, the cores in massive ellipticals may result from a different (not merger) physical mechanism.
-The existence of cores in these galaxies thus represents a challenge to our understanding of the merging process.
-
-6) ``Black hole scouring''  has been suggested to produce a core.
-\end{framed}
-
-\begin{framed}
-Explain ``Black hole scouring''.  \\
-...\\
-...\\
-...\\
-... whatever the mechanisms are, clear measurements of the central densities can be valuable to solve this puzzle and to shed light on the connection of SMBHs and galaxies. 
-\end{framed}
-
-\begin{framed}
-Strong lensing: \\  \\
-1) lensing is a well-known tool for mapping out mass \\ \\
-2) strong lenses have been used to measure the einstein mass (e.g., X et al.), and the density skopes (Y et al.). \\ \\
+Strong gravitational lensing is a powerful tool for mapping out matter distribution.
+Among other things, strong lenses have been used to constrain galaxy masses  \citep[e.g.][]{}, density profiles \citep[][]{}, abundance of dark matter subhalos \citep[][]{}, etc.
+\\ \\
 3) Strong lensing formalism, predicts an odd number of images, with a central image that is \emph{demagnified} \\ \\

### 2014-10-27 ms.tex
modifying introduction

@@
 \shortauthors{Y. Hezaveh}
+
+\usepackage{color}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
+\newcommand{\red}{\textcolor{red}}
+
 \begin{document}
@@
 
-\begin{framed}
-Strong gravitational lensing is a powerful tool for mapping out matter distribution.
-Among other things, strong lenses have been used to constrain galaxy masses  \citep[e.g.][]{}, density profiles \citep[][]{}, abundance of dark matter subhalos \citep[][]{}, etc.
-\\ \\
-3) Strong lensing formalism, predicts an odd number of images, with a central image that is \emph{demagnified} \\ \\
-4) it has been known that the flux (i.e.
-demagnification) of the central image is very sensitive to the very inner regions of the density profiles: very peaky, singular density profiles, demagnify the image by very large amounts, whereas cored or shallow profile will result in bright central images.
-\\ \\
+%\begin{framed}
+Strong gravitational lensing is a powerful tool for probing matter distribution in distant galaxies.
+Among other things, strong lenses have been used to constrain galaxy masses  \citep[e.g.][]{}, density profiles \citep[e.g.][]{}, and abundance of dark matter subhalos \citep[e.g.][]{}.
+Strong lensing formalism indicates that the number of lensed images should always be odd.
+For double and quad image configurations, a third and a fifth image are predicted to exist near the centers of lensing galaxies.
+Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult.
+It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep singular density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter.
+%Lack of detection of central images in almost all lenses suggests steep central density profiles in lens galaxies.
+In addition to their low flux, the fact that central images coincide with the emission from lens galaxies makes their detection even harder.
+If observed in optical, absorption in the central dense regions of the lens make the central images even dimmer, while the photon noise from the lens emission further reduces the sensitivity.
+Moreover, distinguishing the central images from emission originating in the lens galaxies is extremely  challenging.
 
-4) typically only an even number of images are observed,  suggesting that the central images are demagnified below the sensitivity of instruments. \\ \\
+%5) Additionally, another reason for lack of detection is that the central image is located at the center of the lensing galaxy, where i) the sensitivity is lower, due to photon noise of the lens ii) it is difficult to distinguish the flux of the central image from the emission from the lens.
+iii) if in optical, since they pass through the centers of galaxies there's a high chance of large absorption (in the lens)
 
-5) Additionally, another reason for lack of detection is that the central image is located at the center of the lensing galaxy, where i) the sensitivity is lower, due to photon noise of the lens ii) it is difficult to distinguish the flux of the central image from the emission from the lens.
-iii) if in optical, since they pass through the centers of galaxies there's a high chance of large absorption (in the lens)
-\end{framed}
+%Such central images, however, have been very rarely detected, suggesting that steep density profiles of galaxies render them 
+%4) typically only an even number of images are observed,  suggesting that the central images are demagnified below the sensitivity of instruments. \\ \\
+
+%\end{framed}
 
 \begin{framed}
-a review of central image observations and studies:\\ \\
+\red{needs work}
+The individual behavior \citep{} and statistical properties of central images in lens populations have been extensively studied (e.g.
+Wallington 1993, Evans \& Hunter 2002, Keeton 2003),  suggesting that central images could have a wide range of magnifications.
+Observational searches for these images have found a number of candidates \citep[e.g.][]{}, however, only one secure detection of a central image exists to date \citep{winn:2004}.
+To avoid the possibility of absorption in the lens, most studies have focused on strongly lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from faint emission from the lens galaxies.
 
-1) The individual and statistical properties of central images have been previously studied. (e.g. Wallington 1993, Evans \& Hunter 2002, Keeton 2003, ) \\ \\
-2) to avoid absorption by, and lack of contamination from the main lens, past studies focused on radio lens quasars. \\ \\
-3) for example, Rusin \&  Ma 2001 set constrains on the inner profiles of lens galaxies form observations of six two-image radio-loud lens systems \\ \\
-4) confusion between a central image, and faint radio emission from the lens galaxy, could be avoided by studying the radio spectrum of a candidate central image.   
-5) the only secure detection of a central image (based on its radio spectrum)  in a galaxy-mass lensing system, is PMNJ 1632?0033 (Winn et al. 2002, 2003, 2004),   \\ \\
-6) Winn et al 2004 used the detection of this central image to place constraints on the mass of the central SMBH.
+%To avoid confusion between a central image and faint radio emission from the lens galaxies
+
+%a review of central image observations and studies:\\ \\
+%1) The individual and statistical properties of central images have been previously studied. (e.g. Wallington 1993, Evans \& Hunter 2002, Keeton 2003, ) \\ \\
+%2) to avoid absorption by, and lack of contamination from the main lens, past studies focused on radio lens quasars. \\ \\
+%3) for example, Rusin \&  Ma 2001 set constrains on the inner profiles of lens galaxies form observations of six two-image radio-loud lens systems \\ \\
+%4) confusion between a central image, and faint radio emission from the lens galaxy, could be avoided by studying the radio spectrum of a candidate central image.   
+%5) the only secure detection of a central image (based on its radio spectrum)  in a galaxy-mass lensing system, is PMNJ 1632?0033 (Winn et al. 2002, 2003, 2004),   \\ \\
+%6) Winn et al 2004 used the detection of this central image to place constraints on the mass of the central SMBH.
 \end{framed}

### 2014-10-27 ms.tex
modifying introduction

@@
 
-\begin{framed}
+%\begin{framed}
 \red{needs work}
@@
 %6) Winn et al 2004 used the detection of this central image to place constraints on the mass of the central SMBH.
-\end{framed}
+%\end{framed}
 
-\begin{framed}
-Describe the newly discovered population of mm lenses + ALMA's observations: \\  \\
-1) strong lenses in mm were discovered (SPT, Herschel, etc.) \\ \\
-2) ALMA observations confirmed that they're all lensed and that the sources are at high z \\ \\
-3) because they were selected by flux, + the high sensitivity of ALMA $->$ SNR is high \\ \\
-3B) we note that in a 10 hr long observation ALMA can achieve a sensitivity of order 0.0164 mJy in a 500 km/s bandwidth, since the background sources have typical (intrinsic) average line fluxes of order 2-3 mJy, such observations will be able to detect images with magnification as low as $10^{-2}$ \\ \\
-4) the sources have many molecular lines.
+%\begin{framed}
+A new large population of strong lenses has recently been discovered \citep{}.
+These systems were initially discovered as bright point sources in wide area mm/submm surveys \citep{}.
+Follow-up observations have confirmed that they constitute a large population of strong lenses \citep{}.
+In particular, ALMA observations of these sources has revealed that the background galaxies are starburst, high redshift galaxies, containing a wealth of cold molecular gas \cite{}.
+These observations proved that the extremely high flux of the sources in combination with the high sensitivity of ALMA results in a very high signal to noise ratios (the lens models in Hezaveh et al 2013 were based on $\sim50$ s-long observations).
+Motivated by the discovery of this population and the operation of ALMA, in this letter we revisit the issue of detecting central images.
+Deep ALMA observations of molecular lines in these sources are likely to be carried out for various reasons (e.g.
+power spectrum of dark matter, measuring the mass of SMBH in background galaxies).
+If a central image of a lensed molecular line is detected, it will be readily identifiable since it will correspond to the redshift of the source, leaving no doubt about its origin.
+In addition, since these lines are in mm-bands, the line fluxes are very unlikely to be suppressed due to absorption in the lens.
+
+%doesn't decrease due to absorption
+%little (if any) absorption in the lens, so the flux doesn't decrease due to absorption
+%Since the sources have many molecular lines. 
+%Describe the newly discovered population of mm lenses + ALMA's observations: \\  \\
+%1) strong lenses in mm were discovered (SPT, Herschel, etc.) \\ \\
+%2) ALMA observations confirmed that they're all lensed and that the sources are at high z \\ \\
+%3) because they were selected by flux, + the high sensitivity of ALMA $->$ SNR is high \\ \\
+%3B) we note that in a 10 hr long observation ALMA can achieve a sensitivity of order 0.0164 mJy in a 500 km/s bandwidth, since the background sources have typical (intrinsic) average line fluxes of order 2-3 mJy, such observations will be able to detect images with magnification as low as $10^{-2}$ \\ \\
+%4) the sources have many molecular lines.
 If a central image of a \emph{molecular line} is observed it will be easily identifiable since it corresponds to the redshift of the source, and there will be no confusion that it may be associated with the lens.
 \\ \\
-5) since these lines are in mm, there's very little (if any) absorption in the lens, so the flux doesn't decrease due to absorption
-\end{framed}
+%5) since these lines are in mm, there's very little (if any) absorption in the lens, so the flux doesn't decrease due to absorption
+%\end{framed}
 
-\begin{framed}
-motivation and description of the paper: \\ \\
-1) Long ALMA observations of these molecular lines are likely to be carried out for various reasons (e.g. power spectrum of dark matter, measuring the mass of background black holes) .  \\ \\
-2) In this paper we explore the possibility of detection of these central images in such deep observations, and investigate what we could learn about the innermost regions of galaxies from detection or non-detection of such central images.\\ \\
-3) the paper is organized as: section 2 describes the simulations, section 3 presents the results and discuss them and conclude in section 5 \\ \\
-4) we use $\Lambda$CDM cosmology of XXX
-\end{framed}
+ In this letter, we explore the possibility of detecting the central lensed images in such deep observations and investigate the constraints that could be placed on the core size, mass of SMBHs, and the slope of the density profiles from detection, or non-detection of such images.
+In Section 2 we describe the simulations, in Section 3 we present the results and discuss them, and finally conclude in Section 4.
+We use a flat $\Lambda$CDM cosmology with $h=0.71$ and $\Omega_M=0.267$.
+
+% the distribution of matter in the innermost regions of galaxies from detection or non-detection of such central images.\\ \\
+%3) the paper is organized as: section 2 describes the simulations, section 3 presents the results and discuss them and conclude in section 5 \\ \\
+%4) we use $\Lambda$CDM cosmology of XXX
+
+%\begin{framed}
+%motivation and description of the paper: \\ \\
+%1) Long ALMA observations of these molecular lines are likely to be carried out for various reasons (e.g. power spectrum of dark matter, measuring the mass of background black holes) .  \\ \\
+%2) In this paper we explore the possibility of detection of these central images in such deep observations, and investigate what we could learn about the innermost regions of galaxies from detection or non-detection of such central images.\\ \\
+%3) the paper is organized as: section 2 describes the simulations, section 3 presents the results and discuss them and conclude in section 5 \\ \\
+%4) we use $\Lambda$CDM cosmology of XXX
+%\end{framed}
 

### 2014-10-27 ms.tex
modifying introduction

@@
 Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super massive black holes (SMBH), galaxy formation, and dark matter.
-It is now established that almost every massive galaxy harbors a SMBH at its center \citep[][]{} with a mass that strongly correlates with the mass of the host galaxy.
+It is now established that almost every massive galaxy harbors a SMBH at its center with a mass that strongly correlates with the mass of the host galaxy \citep{Kormendy:95,Ferrarese:00,Gebhardt:00,Tremaine:02,Kormendy:13}.
 In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions.
 \citep{}.
-Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g][]{rochaetal}.
-Mapping the matter density in the central regions of galaxies can therefore shed light on various astrophysical phenomena.
+Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g][]{Rocha:13}.
+Mapping the matter density in the central regions of galaxies can thus shed light on various astrophysical phenomena.
 %probing the inner 0.5 kpc of galaxies is interesting.
@@
 Cores in massive ellipticals, therefore, should be the result of different (not merger) mechanisms.
-``Black hole scouring'' is currently the only known plausible mechanism that could explain core-formation in these galaxies \citep{Thomas2014}.
+``Black hole scouring'' is currently the only known plausible mechanism that could explain core-formation in these galaxies \citep{Thomas:14}.
 %\end{framed}
@@
 \red{needs work}
-The individual behavior \citep{} and statistical properties of central images in lens populations have been extensively studied (e.g.
-Wallington 1993, Evans \& Hunter 2002, Keeton 2003),  suggesting that central images could have a wide range of magnifications.
-Observational searches for these images have found a number of candidates \citep[e.g.][]{}, however, only one secure detection of a central image exists to date \citep{winn:2004}.
+The individual behavior \citep{} and statistical properties of central images in lens populations have been extensively studied \citep[e.g.][]{Wallington:93, Evans:02, Keeton:03},  suggesting that central images could have a wide range of magnifications.
+Observational searches for these images have found a number of candidates \citep[e.g.][]{Inada:05}, however, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.\red{(Inada:08 is a cluster?)}
 To avoid the possibility of absorption in the lens, most studies have focused on strongly lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from faint emission from the lens galaxies.
@@
 \section{Simulations}
-\begin{framed} description
-We generate mock data cubes of gas emission in the source galaxy, lens the data cubes with a foreground halo, predict the ALMA visibilities, and use the visibilities to estimate the detection significance of the central image for various parameters.
-The gas in the source galaxy is modeled as a collection of 5 Gaussian clumps with FWHM of XX, distributed over XX kpc and each separated in a different channel.
-and an intrinsic velocity dispersion  of 10 $km/s$ (FWHM) similar to observations of \citet{Davis:13}. 
-The choice of two discrete rings is made to enforce resolving the inner 50 pc region for a black hole mass measurement.
-We point out, however, that assuming a more general case (e.g.
-an exponential disk) does not change the results \citep[see Figure 2 of ][]{Davis:2014}.
-The velocity integrated flux of the circumnuclear ring is set to 4 $mJy\, km/s$. 
-This value is calculated by scaling the flux of the circumnuclear CO gas in Arp 220 to to z=2 \citep{Sakamoto:99}.
-The rings are concentric and in circular orbits.
-The rotational velocity of each point in the rings is calculated based on the enclosed mass contributed from the galaxy mass model and the mass of the central black hole.
-The black hole is given a mass of $M_{\mathrm{BH}}=5\times 10^{8} M_{\odot}$.
-We model the galaxy density with an isothermal profile ($\rho\propto r^{-2}$) with a central velocity dispersion of 200 km/s. 
-The line-of-sight velocities are calculated to generate a frequency-position data cube.
-Figure \ref{f:f1} shows a velocity-position diagram extracted from the data cube.
-The data comprises 100 frequency channels covering 800 km/s.
+We generate lensed images of background sources, predict ALMA visibilities, and use them to estimate the detection significance of central images for various parameters.
+We simulate the velocity integrated flux of a high J CO line.
+The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy Jy over a XX km/s band.
 
-Each layer of the data cube is lensed with the foreground halo to  generate a lensed cube.
-We use a Singular Isothermal Ellipsoid (SIE) mass model for the lens galaxy \citep[$\rho\propto r^{-2}$,][]{Kormann:94}, placed at $z_l=0.5$ and place the source at $z_s=2.0$.
-The central velocity dispersion of the lens is set to 180 $km/s$, which is typical for galaxy-galaxy lensing systems \citep[e.g.][]{hezaveh:13b}.
+We model the lens potential as a sum of three components: dark matter, stellar population and central SMBH.
+The dark matter is modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile \citep{}.
+As by pointed out by \citep{Keeton:03}, due to its extreme flatness in these regimes, the dark matter component has negligible influence on the central images.
+The stellar population is modeled as a a core power-law, $\Sigma\propto (r^2+s^2)^{\gamma}$.
+Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curved).
+The grey dashed curves show a few example of core-sersic models with parameters from \citep{f06}.
+We note that although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles.
+The black hole is modeled as a simple point mass at the center of the potential. In this work we assume that all the three components are concentric.
+
+The lens mass is set to XX $M_{\odot}$ resulting in an Einstein radius of $\sim XX''$, in agreement with galaxy-galaxy strong lenses.
+We divide this mass equally (in a radius of 10 kpc) between stellar and dark matter.
 
@@
 
-When the background source only consists of the two rings described above, the lens model parameters have large uncertainties and are mildly degenerate with the mass of the black hole. 
-A realistic source galaxy, however, will consists of many other components, extended over kilo-parsec scales, which if included in lens models, can strongly constrain the lens parameters.
-We run five simulations in which the background source is embedded in an extended Gaussian clump with a radius of 1 kpc and a flux of 1 Jy km/s \citep[typical for SMGs, see][]{Bothwell:12}.
-We find that in these simulations, the lens parameters are extremely constrained and the effect of marginalization over them barely reduces the significance of black hole mass measurements ($\lesssim 0.05\, \sigma$).
-This suggests that when the full structure of the source galaxies are included in models, the lens parameters do not significantly contribute to the black hole mass uncertainties.
-Therefore, to reduce the computational cost of simulations, we do not marginalize over the lens parameters.
-%\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
-\end{framed}
+For simulations where we calculate the detection significance of the demagnified image, we compute the magnification at every pixel in the image plane and generate maps with and without the the demagnified flux and evaluate the detection significance of the central image by comparing the two images.
+In other simulations where the constrains on parameters are needed, we use a Fisher analysis to compute the full covariance of all parameters.
+We then marginalize over the nuisance parameters (e.g.
+source position, lens ellipticity) to calculate the marginalized likelihood of the relevant parameters.
+
+%\begin{framed} description
+
+%The gas in the source galaxy is modeled as a collection of 5 Gaussian clumps with FWHM of XX, distributed over XX kpc and each separated in a different channel.
+%and an intrinsic velocity dispersion  of 10 $km/s$ (FWHM) similar to observations of \citet{Davis:13}. 
+%The choice of two discrete rings is made to enforce resolving the inner 50 pc region for a black hole mass measurement.
+We point out, however, that assuming a more general case (e.g.
+an exponential disk) does not change the results \citep[see Figure 2 of ][]{Davis:2014}.
+%The velocity integrated flux of the circumnuclear ring is set to 4 $mJy\, km/s$. 
+%This value is calculated by scaling the flux of the circumnuclear CO gas in Arp 220 to to z=2 \citep{Sakamoto:99}.
+%The rings are concentric and in circular orbits.
+The rotational velocity of each point in the rings is calculated based on the enclosed mass contributed from the galaxy mass model and the mass of the central black hole.
+The black hole is given a mass of $M_{\mathrm{BH}}=5\times 10^{8} M_{\odot}$.
+%We model the galaxy density with an isothermal profile ($\rho\propto r^{-2}$) with a central velocity dispersion of 200 km/s. 
+%The line-of-sight velocities are calculated to generate a frequency-position data cube.
+Figure \ref{f:f1} shows a velocity-position diagram extracted from the data cube.
+The data comprises 100 frequency channels covering 800 km/s.
+
+%Each layer of the data cube is lensed with the foreground halo to  generate a lensed cube.
+We use a Singular Isothermal Ellipsoid (SIE) mass model for the lens galaxy \citep[$\rho\propto r^{-2}$,][]{Kormann:94}, placed at $z_l=0.5$ and place the source at $z_s=2.0$.
+The central velocity dispersion of the lens is set to 180 $km/s$, which is typical for galaxy-galaxy lensing systems \citep[e.g.][]{hezaveh:13b}.
+
+%\end{framed}
 
@@
 
+\bibliographystyle{apj}
+\bibliography{references}
+
 \end{document}

### 2014-10-27 ms.tex
modifying introduction

@@
 Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super massive black holes (SMBH), galaxy formation, and dark matter.
-It is now established that almost every massive galaxy harbors a SMBH at its center with a mass that strongly correlates with the mass of the host galaxy \citep{Kormendy:95,Ferrarese:00,Gebhardt:00,Tremaine:02,Kormendy:13}.
+It is now established that almost every massive galaxy harbors a SMBH at its center with a mass that strongly correlates with the mass of the host galaxy \citep{Kormendy:95,Ferrarese:00,Gebhardt:00,Tremaine:02}.
 In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions.
-\citep{}.
+\citep[e.g][]{Barnes:92,Ebisuzaki:91}.
 Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g][]{Rocha:13}.
@@
 %\\ \\
-Morphological studies of galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep{e.g.ferrarese06}.
+Morphological studies of galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep[e.g.,][]{Ferrarese:06}.
 These galaxies are thought to form through gas-poor mergers.
@@
 It is thought that during a merger, the SMBHs of the two merging galaxies form a binary which sinks to the center of the potential.
-The two orbiting SMBH then dissipate angular momentum through three-body interactions with nearby central stars, pushing them to higher orbits and scouring out a core.
-This angular momentum loss then allows the two black holes to merge.
-\citep{Begelman et al.
-1980}
-Previous studies have shown that the core sizes in these galaxies scales with the mass of their SMBH in agreement with theoretical predictions (Graham 2004; Kormendy \& Bender 2009; Kormendy \& Ho 2013).
-Such measurements, are, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high angular resolutions.
+The two orbiting SMBHs then dissipate angular momentum through three-body interactions with nearby central stars, pushing them to higher orbits and scouring out a core.
+This angular momentum loss then allows the two black holes to merge \citep{Begelman:80}.
+Previous studies have shown that the core sizes in these galaxies scales with the mass of their SMBHs, in agreement with theoretical predictions \citep{Kormendy:09,Kormendy:13}.
+Such measurements, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high physical resolutions.
 % ... whatever the mechanisms are, clear measurements of the central densities can be valuable to solve this puzzle and to shed light on the connection of SMBHs and galaxies. 
@@
 %\begin{framed}
-A new large population of strong lenses has recently been discovered \citep{}.
-These systems were initially discovered as bright point sources in wide area mm/submm surveys \citep{}.
-Follow-up observations have confirmed that they constitute a large population of strong lenses \citep{}.
-In particular, ALMA observations of these sources has revealed that the background galaxies are starburst, high redshift galaxies, containing a wealth of cold molecular gas \cite{}.
-These observations proved that the extremely high flux of the sources in combination with the high sensitivity of ALMA results in a very high signal to noise ratios (the lens models in Hezaveh et al 2013 were based on $\sim50$ s-long observations).
-Motivated by the discovery of this population and the operation of ALMA, in this letter we revisit the issue of detecting central images.
-Deep ALMA observations of molecular lines in these sources are likely to be carried out for various reasons (e.g.
-power spectrum of dark matter, measuring the mass of SMBH in background galaxies).
+A new large population of strong lenses has recently been discovered.
+These systems were initially detected as bright point sources in wide area mm/submm surveys \citep{vieira:10,negrello:10}.
+Follow-up observations have confirmed that they constitute a large population of strong lenses \citep{vieira:13, hezaveh:13b, bussmann:13}.
+In particular, ALMA observations of these sources have revealed that the background galaxies are starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
+These observations showed that the extreme brightness the sources in combination with the high sensitivity of ALMA results in very high signal to noise ratios \citep[e.g.
+the lens models in][were based on $\sim50$ second long observations]{hezaveh:13b}.
+Motivated by the discovery of this population and the operation of ALMA, here we revisit the issue of detecting central images.
+Deep ALMA observations of molecular lines in these sources are likely to be carried out for various reasons \citep[e.g.,][]{hezaveh:14a,hezaveh:14b}.
 If a central image of a lensed molecular line is detected, it will be readily identifiable since it will correspond to the redshift of the source, leaving no doubt about its origin.

### 2014-10-27 ms.tex
modifying introduction

@@
 We generate lensed images of background sources, predict ALMA visibilities, and use them to estimate the detection significance of central images for various parameters.
-We simulate the velocity integrated flux of a high J CO line.
-The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy Jy over a XX km/s band.
+We simulate observations of a high-$J$ CO line.
+The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a XX km/s band.
 
 We model the lens potential as a sum of three components: dark matter, stellar population and central SMBH.
-The dark matter is modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile \citep{}.
+The dark matter is modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile \citep{Golse:02}.
 As by pointed out by \citep{Keeton:03}, due to its extreme flatness in these regimes, the dark matter component has negligible influence on the central images.
@@
 Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curved).
-The grey dashed curves show a few example of core-sersic models with parameters from \citep{f06}.
+The grey dashed curves show a few example of core-sersic models with parameters taken from \citet{Ferrarese:06}.
 We note that although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles.
@@
 \caption{ illustration of the central image in 2 cases: 
-\label{f:f2}}
+\label{fig1}}
 \end{figure}
@@
 The solid black line shows the total matter density (dark plus stellar) of our model.
-\label{f:f2}}
+\label{fig2}}
 \end{figure}

### 2014-10-28 ms.tex
modifying layout
modifying everything

@@
 %\\ \\
-Morphological studies of galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep[e.g.,][]{Ferrarese:06}.
+Studies of local galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep[e.g.,][]{Ferrarese:06}.
 These galaxies are thought to form through gas-poor mergers.
@@
 Cores in massive ellipticals, therefore, should be the result of different (not merger) mechanisms.
-``Black hole scouring'' is currently the only known plausible mechanism that could explain core-formation in these galaxies \citep{Thomas:14}.
+``Black hole scouring'' is a plausible mechanism that can explain core-formation in these galaxies \citep{Thomas:14}.
 %\end{framed}
@@
 It is thought that during a merger, the SMBHs of the two merging galaxies form a binary which sinks to the center of the potential.
-The two orbiting SMBHs then dissipate angular momentum through three-body interactions with nearby central stars, pushing them to higher orbits and scouring out a core.
+The two orbiting SMBHs then dissipate angular momentum through three-body interactions with nearby central stars, pushing the stars to higher orbits and ``scouring out'' a core.
 This angular momentum loss then allows the two black holes to merge \citep{Begelman:80}.
-Previous studies have shown that the core sizes in these galaxies scales with the mass of their SMBHs, in agreement with theoretical predictions \citep{Kormendy:09,Kormendy:13}.
+Previous studies have shown that the core sizes in these galaxies scale with the mass of their SMBHs, in agreement with theoretical predictions \citep{Kormendy:09,Kormendy:13}.
 Such measurements, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high physical resolutions.
@@
 %\begin{framed}
-Strong gravitational lensing is a powerful tool for probing matter distribution in distant galaxies.
+Strong gravitational lensing is a powerful tool for probing the matter distribution in distant galaxies.
 Among other things, strong lenses have been used to constrain galaxy masses  \citep[e.g.][]{}, density profiles \citep[e.g.][]{}, and abundance of dark matter subhalos \citep[e.g.][]{}.
-Strong lensing formalism indicates that the number of lensed images should always be odd.
+The strong lensing theory indicates that the number of lensed images should always be odd.
 For double and quad image configurations, a third and a fifth image are predicted to exist near the centers of lensing galaxies.
-Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult.
+Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep{}.
 It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep singular density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter.
@@
 In addition to their low flux, the fact that central images coincide with the emission from lens galaxies makes their detection even harder.
-If observed in optical, absorption in the central dense regions of the lens make the central images even dimmer, while the photon noise from the lens emission further reduces the sensitivity.
-Moreover, distinguishing the central images from emission originating in the lens galaxies is extremely  challenging.
+Distinguishing the central images from emission originating in the lens galaxies is extremely challenging.
+Moreover, if observed in the optical, absorption in the central dense regions of the lens can make the central images even dimmer, while the photon noise from the lens emission further reduces the sensitivity.
 
@@
 %\begin{framed}
-A new large population of strong lenses has recently been discovered.
+A new large population of strong lenses has recently been discovered in mm-bands.
 These systems were initially detected as bright point sources in wide area mm/submm surveys \citep{vieira:10,negrello:10}.
 Follow-up observations have confirmed that they constitute a large population of strong lenses \citep{vieira:13, hezaveh:13b, bussmann:13}.
-In particular, ALMA observations of these sources have revealed that the background galaxies are starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
-These observations showed that the extreme brightness the sources in combination with the high sensitivity of ALMA results in very high signal to noise ratios \citep[e.g.
-the lens models in][were based on $\sim50$ second long observations]{hezaveh:13b}.
+In particular, ALMA observations of these sources have revealed that the background galaxies are dusty, starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
+These observations showed that the extreme brightness of the sources in combination with the high sensitivity of ALMA results in very high signal to noise ratios \citep[e.g.
+the lens models in][were based on just $\sim50$ second long observations]{hezaveh:13b}.
 Motivated by the discovery of this population and the operation of ALMA, here we revisit the issue of detecting central images.
-Deep ALMA observations of molecular lines in these sources are likely to be carried out for various reasons \citep[e.g.,][]{hezaveh:14a,hezaveh:14b}.
+Deep ALMA observations of molecular line emission in these sources are likely to be carried out for various reasons \citep[e.g.,][]{hezaveh:14a,hezaveh:14b}.
 If a central image of a lensed molecular line is detected, it will be readily identifiable since it will correspond to the redshift of the source, leaving no doubt about its origin.
@@
 
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_02.eps}
+\centering
+\end{center}
+\caption{ illustration of the central image in 2 cases: 
+\label{fig1}}
+\end{figure}
+
 \section{Simulations}
@@
 
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
+\centering
+\end{center}
+\caption{ Model density profiles.
+The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
+the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006.
+The red solid curve shows our cored-power-law model that we use to approximate this stellar component.
+The solid black line shows the total matter density (dark plus stellar) of our model.
+\label{fig2}}
+\end{figure}
+
 %\begin{framed} description
@@
 
-\newpage
+%\newpage
 \section{Results and Discussions}
+\subsection{Detection of central images with ALMA}
+In this section, we estimate the detection significance of central images of molecular lines with ALMA.
+As discussed earlier, the flux of the central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
+Figure \ref{fig:3} shows the detection significant of the central image for a range of these parameters in a 10-h long ALMA observation.
+The grey curves (dark to light) correspond to profiles with slope of $\gamma=0.9, 1.0, 1.1,$ and 1.2.
+As seen in this figure, larger stellar cores result in brighter images.
+Lensing studies have shown that the total profiles of galaxies are very close to vein isothermal.
+In case of an isothermal profile, and with a core size larger than XX pc and a $10^8M_{\odot}$ black hole, such observations should be able to detect the central image with more than $XX\sigma$.
+We note that for significantly shallower ($\gamma<0.8$) and cored density profiles, the central image is \emph{magnified} and its detection should be trivial.
+SMBHs can also have a significant influence on the magnification and flux of the central images. More massive SMBHs demagnify the images on scales comparable to their Einstein radius size. 
+The dashed curves in Figure \ref{fig:3} show the suppression of image flux due to existence of a $2\times10^8M_{\odot}$ SMBH.
+
+As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, realistic parameters produce a wide range of predictions for the flux of the central images.
+Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of plausible parameter space the central images could be detected.
+
 \begin{framed}
-\subsection{Detection of central images}
-1) We evaluate the detection significance of central images over a range of relevant parameters. \\ \\
-2) Figure 4 shows our results for a 10-hr long observation with ALMA\\ \\
-3) we show that, as expected, the image is fainter for steeper profile slopes. \\ \\
-4) the 0.9 value (combined with 0.1 DM) results in the isothermal profile, which has been shown to be consistent with strong lensing data \\ \\
-5) if that's the case, and in the absence of massive BHs, then stellar cores as small as $\sim80$ pc should allow a 5$\sigma$ detection of the central images. \\ \\
-5A) we note that for much shallower density profiles, the central image is actually \emph{magnified}, and therefore it's detection should be trivial.\\ \\
-6) the flux is significantly supressed by the central SMBH \\  \\
-7) the dashed curves show the same for a galaxy with a $2e8M_{\odot}$ SMBH. \\ \\
-8) we note that, as pointed out in Keeton 2003, there's a large range of possibilities for plausible lens parameters: although for some parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is no chance of detecting the central image, over a significant fraction of allowed parameters the central image could be detected.
+%1) We evaluate the detection significance of central images over a range of relevant parameters. \\ \\
+%2) Figure 4 shows our results for a 10-hr long observation with ALMA\\ \\
+%3) we show that, as expected, the image is fainter for steeper profile slopes. \\ \\
+%4) the 0.9 value (combined with 0.1 DM) results in the isothermal profile, which has been shown to be consistent with strong lensing data \\ \\
+%5) if that's the case, and in the absence of massive BHs, then stellar cores as small as $\sim80$ pc should allow a 5$\sigma$ detection of the central images. \\ \\
+%5A) we note that for much shallower density profiles, the central image is actually \emph{magnified}, and therefore it's detection should be trivial.\\ \\
+%6) the flux is significantly supressed by the central SMBH \\  \\
+%7) the dashed curves show the same for a galaxy with a $2e8M_{\odot}$ SMBH. \\ \\
+%8) we note that, as pointed out in Keeton 2003, there's a large range of possibilities for plausible lens parameters: although for some parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is no chance of detecting the central image, over a significant fraction of allowed parameters the central image could be detected.
 \\ \\
@@
 
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_03.eps}
+\centering
+\end{center}
+\caption{ Significance of detection of the central image as a function of the stellar core size for a 10-hr long ALMA observation.
+The colors correspond to different slopes of the stellar component.
+The solid curves correspond to a case without a SMBH while the dashed line show the result of a simulation which includes a $2\times10^8M_{\odot}$ SMBH at its center.
+\label{fig:3}}
+\end{figure}
+
+\subsection{SMBHs and the core size}
+Here, we study how deep observations of molecular lines can constrain the slope of the density profile, the size of the stellar core, and the mass of the SMBHs.
+We study a few cases in which the central images are detected as well as few scenarios in which they are below the $<3\sigma$ detection limit.
+We use a Fisher analysis to investigate the degeneracies among parameters and the constraints that could be placed on them.
+We include all our model parameters in the Fisher matrix, and marginalize over the nuisance parameters (e.g.
+intrinsic source flux and position), to obtain the marginalized likelihood of the relevant parameters.
+ Figure \ref{fig:4} shows the parameters for a case with $R_{core}$=180 pc, $M_{BH}=1e8$ and $\gamma=1$.
+As seen in Figure \ref{fig:3},  this parameter combination results in a faint ($\sim3\sigma$) detection of the central image.
+
 \begin{framed}
-\subsection{SMBHs and the core size}
-1) in this section we study how well we can constrain the mass of the central black hole, the slope of the density and the size of the stellar core. \\ \\
-2) we choose a few models where the central image is detected OR not detected and use a Fisher analysis to determine the degeneracies between the parameters and the detection significance of each parameter.
+%1) in this section we study how well we can constrain the mass of the central black hole, the slope of the density and the size of the stellar core. \\ \\
+%2) we choose a few models where the central image is detected OR not detected and use a Fisher analysis to determine the degeneracies between the parameters and the detection significance of each parameter.
 \\ \\
-3) we note that in the Fisher analysis we include all nuisance parameters (e.g. source position, size, etc.) and marginalize over them  \\ \\
-4) Figure 4 shows the parameters for a case with $R_{core}$=180 pc, $M_{BH}=1e8$ and $\gamma=1$.
+%3) we note that in the Fisher analysis we include all nuisance parameters (e.g. source position, size, etc.) and marginalize over them  \\ \\
+%4) Figure 4 shows the parameters for a case with $R_{core}$=180 pc, $M_{BH}=1e8$ and $\gamma=1$.
 As seen from Figure 3,  this parameter combination results in a faint ($\sim3\sigma$) detection of the central image.
@@
 
-\newpage
-
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_02.eps}
-\centering
-\end{center}
-\caption{ illustration of the central image in 2 cases: 
-\label{fig1}}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
-\centering
-\end{center}
-\caption{ Model density profiles.
-The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
-the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006.
-The red solid curve shows our cored-power-law model that we use to approximate this stellar component.
-The solid black line shows the total matter density (dark plus stellar) of our model.
-\label{fig2}}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_03.eps}
-\centering
-\end{center}
-\caption{ Significance of detection of the central image as a function of the stellar core size for a 10-hr long ALMA observation.
-The colors correspond to different slopes of the stellar component.
-The solid curves correspond to a case without a SMBH while the dashed line show the result of a simulation which includes a $2\times10^8M_{\odot}$ SMBH at its center.
-\label{f:f2}}
-\end{figure}
+%\newpage
 
@@
 \caption{ Covariance matrix of parameters for a few different scenarios.
-\label{f:f2}}
+\label{fig:4}}
 \end{figure}
@@
 \section{Conclusion}
+We examined the possibility of detecting central, demagnified images of strongly lensed molecular lines with ALMA.
+We find that there is a non-negligible space of realistic and plausible parameters that result in a high significance detection of the central images.
+We showed that such deep observations can either allow a measurement of the mass of the central SMBH and the stellar core size, or place strong limits on them (if not detected).
 

### 2014-11-02 ms.tex
modifying everything

@@
 In addition, since these lines are in mm-bands, the line fluxes are very unlikely to be suppressed due to absorption in the lens.
-
-%doesn't decrease due to absorption
-%little (if any) absorption in the lens, so the flux doesn't decrease due to absorption
-%Since the sources have many molecular lines. 
-%Describe the newly discovered population of mm lenses + ALMA's observations: \\  \\
-%1) strong lenses in mm were discovered (SPT, Herschel, etc.) \\ \\
-%2) ALMA observations confirmed that they're all lensed and that the sources are at high z \\ \\
-%3) because they were selected by flux, + the high sensitivity of ALMA $->$ SNR is high \\ \\
-%3B) we note that in a 10 hr long observation ALMA can achieve a sensitivity of order 0.0164 mJy in a 500 km/s bandwidth, since the background sources have typical (intrinsic) average line fluxes of order 2-3 mJy, such observations will be able to detect images with magnification as low as $10^{-2}$ \\ \\
-%4) the sources have many molecular lines.
-If a central image of a \emph{molecular line} is observed it will be easily identifiable since it corresponds to the redshift of the source, and there will be no confusion that it may be associated with the lens.
-\\ \\
-%5) since these lines are in mm, there's very little (if any) absorption in the lens, so the flux doesn't decrease due to absorption
-%\end{framed}
+In contrast to lensed quasars, these sources are extended over hundreds of parsecs and can cover a larger area of the source plane.
+This can allow them to occupy the less demagnified regions of the source plane, allowing a higher flux for the central image \citep[the opposite effect of magnification damping due to extended sources,, see e.g.][]{hezaveh:11}.
 
  In this letter, we explore the possibility of detecting the central lensed images in such deep observations and investigate the constraints that could be placed on the core size, mass of SMBHs, and the slope of the density profiles from detection, or non-detection of such images.
+We also examine if binary SMBHs can possibly be detected in such observations.
  In Section 2 we describe the simulations, in Section 3 we present the results and discuss them, and finally conclude in Section 4.
@@
 \subsection{Detection of central images with ALMA}
-In this section, we estimate the detection significance of central images of molecular lines with ALMA.
-As discussed earlier, the flux of the central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
-Figure \ref{fig:3} shows the detection significant of the central image for a range of these parameters in a 10-h long ALMA observation.
-The grey curves (dark to light) correspond to profiles with slope of $\gamma=0.9, 1.0, 1.1,$ and 1.2.
+%In this section, we estimate the detection significance of central lensed images of molecular lines with ALMA. 
+As discussed earlier, the fluxes of central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
+Figure \ref{fig:3} shows the detection significant of a central image for a range of these parameters in a 10-h long ALMA observation.
+The grey curves (dark to light) correspond to profiles with slopes of $\gamma=0.9, 1.0, 1.1,$ and 1.2.
 As seen in this figure, larger stellar cores result in brighter images.
-Lensing studies have shown that the total profiles of galaxies are very close to vein isothermal.
-In case of an isothermal profile, and with a core size larger than XX pc and a $10^8M_{\odot}$ black hole, such observations should be able to detect the central image with more than $XX\sigma$.
-We note that for significantly shallower ($\gamma<0.8$) and cored density profiles, the central image is \emph{magnified} and its detection should be trivial.
-SMBHs can also have a significant influence on the magnification and flux of the central images. More massive SMBHs demagnify the images on scales comparable to their Einstein radius size. 
-The dashed curves in Figure \ref{fig:3} show the suppression of image flux due to existence of a $2\times10^8M_{\odot}$ SMBH.
+%Lensing studies have shown that the total profiles of galaxies are very close to isothermal \red{cite{}}.
+When $\gamma=1.0$ and with a core size larger than 150 pc, such observations should be able to detect the central images with more than $5\sigma$ significance.
+For significantly shallower ($\gamma<0.8$) profile slopes with larger cores, the central image is \emph{magnified} and its detection should be trivial.
+The magnification and flux of central images is also influenced by SMBHs.
+SMBHs demagnify the images on scales comparable to the size of their Einstein radii.
+The dashed curves in Figure \ref{fig:3} show the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.
 
-As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, realistic parameters produce a wide range of predictions for the flux of the central images.
-Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of plausible parameter space the central images could be detected.
+As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, plausible parameters (e.g.
+core sizes) predict  a wide range of magnifications for   central images.
+Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
 
-\begin{framed}
+We also find that the detection significance of the central images can increase by about $3\sigma$ for an extended source with a radius of 1 kpc compared to a point source.
+Since extended sources cover a larger area of the source plane, which may include regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
+%\begin{framed}
 %1) We evaluate the detection significance of central images over a range of relevant parameters. \\ \\
@@
 \\ \\
-9) to calculate this plot we have used a configuration XX, because: it allows us to resolve the central image (if existent), while it is more sensitive that more extended configurations.
+%9) to calculate this plot we have used a configuration XX, because: it allows us to resolve the central image (if existent), while it is more sensitive that more extended configurations.
 In addition, this is the configuration that will be likely used for other projects/sciences.
-\end{framed}
+%\end{framed}
 
@@
 \centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_03.eps}
+\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{figures/f_03.eps}
 \centering
 \end{center}
-\caption{ Significance of detection of the central image as a function of the stellar core size for a 10-hr long ALMA observation.
-The colors correspond to different slopes of the stellar component.
-The solid curves correspond to a case without a SMBH while the dashed line show the result of a simulation which includes a $2\times10^8M_{\odot}$ SMBH at its center.
+\caption{ Detection significance of a central image as a function of the stellar core size for a 10-hr long ALMA observation.
+The gray shades correspond to different slopes for the stellar component.
+The solid curves correspond to a case without a SMBH while the dashed curves show the results when a $2\times10^8M_{\odot}$ SMBH is placed at the center of the lens.
+The source has a Gaussian light profile with an rms of 600 pc. The red curves show the same predictions when $\gamma=1$, for a source with rms of 300 pc.
 \label{fig:3}}
@@
 \subsection{SMBHs and the core size}
-Here, we study how deep observations of molecular lines can constrain the slope of the density profile, the size of the stellar core, and the mass of the SMBHs.
-We study a few cases in which the central images are detected as well as few scenarios in which they are below the $<3\sigma$ detection limit.
-We use a Fisher analysis to investigate the degeneracies among parameters and the constraints that could be placed on them.
-We include all our model parameters in the Fisher matrix, and marginalize over the nuisance parameters (e.g.
-intrinsic source flux and position), to obtain the marginalized likelihood of the relevant parameters.
- Figure \ref{fig:4} shows the parameters for a case with $R_{core}$=180 pc, $M_{BH}=1e8$ and $\gamma=1$.
-As seen in Figure \ref{fig:3},  this parameter combination results in a faint ($\sim3\sigma$) detection of the central image.
-
-\begin{framed}
-%1) in this section we study how well we can constrain the mass of the central black hole, the slope of the density and the size of the stellar core. \\ \\
-%2) we choose a few models where the central image is detected OR not detected and use a Fisher analysis to determine the degeneracies between the parameters and the detection significance of each parameter.
-\\ \\
-%3) we note that in the Fisher analysis we include all nuisance parameters (e.g. source position, size, etc.) and marginalize over them  \\ \\
-%4) Figure 4 shows the parameters for a case with $R_{core}$=180 pc, $M_{BH}=1e8$ and $\gamma=1$.
-As seen from Figure 3,  this parameter combination results in a faint ($\sim3\sigma$) detection of the central image.
-\\ \\
-5) we note that the black hole mass is degenerate with the core size: a larger core, results in a brighter image, which can be supressed by a more massive BH. \\ \\
-6) The Fisher data show that the black hole mass cannot be measured with high significance in such observations ($1.16\sigma$) \\ \\
-7) however, interestingly, the degeneracy of the black hole mass and the size of the central core breaks at the high end. and the stellar core is measured with XX $\sigma$\\ \\
-8) this is likely because a very large core results in a fairly extended central images, which could be \emph{resolved} (see Figure 1), in that case, the flux suppression by a crazy massive black hole will result in a distinct dip in the central image  which can be used to distinguish the two.
-Rusin  Keeton Winn 2005 %http://adsabs.harvard.edu/abs/2005ApJ...627L..93R
-\\ \\
-
-9) we note that the constraints in this case will be of similar strength to those of Winn 2004. \\ \\ 
-10) in the case of very small core, and a massive black hole (no detection of the image) we only get an upper limits of $\sim$ and $\sim$ for the two. \\ \\
-11) and in case with massive core and massive black hole we measure both with high significance. 
-12) we note that all these parameter combinations are plausible choices, and therefore long observations such as these will be able to either measure these parameters with confidence or place strong constraints on them.
-
-\end{framed}
+We studied the constraints that deep observations of molecular lines can place on the slope of the density profile, the size of the stellar core, and the mass of the SMBHs. 
+We performed a Fisher analysis to examine the constrains and parameter degeneracies in simulations in which the central images are detected, as well as those in which they are below the detection limit.
+All model parameters were included in the Fisher matrix, and nuisance parameters were later marginalize over (e.g.
+intrinsic source flux and position) to obtain the marginalized likelihood of the relevant parameters.
+ Figure \ref{fig:4} shows the parameter covariance for two examples with different core radii (top panel:  $R_{core}$=170 pc, bottom panel: $R_{core}$=450 pc).
+% . As seen in Figure \ref{fig:3},  this parameter combination results in a $\sim3\sigma$ detection of the central image. 
+We found that when $\gamma=1$, cores sizes larger than 100 pc can be measured with high significance. As seen in top panel of Figure \ref{fig:4}, 
+the mass of SMBH is degenerate with the core size: larger cores result in brighter images, whose flux can be supressed by a more massive SMBH.
+This degeneracy,  however,  breaks when the core size is very large. 
+Large cores produce more extended central images that are spatially resolved.
+The distortion caused by a SMBH can distort this image on smaller scales, resulting in a distinct dip in its surface brightness.
+%, which breaks the degeneracy of the SMBH with the core size (for point sources this will be observed as the plotting of the central image by the SMBH).
+%Rusin  Keeton Winn 2005
+We found that for cores $\gtrsim200$ pc, SMBH masses could be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits on the mass of SMBHs can be placed.
+We also find that when the core size is larger, the constraints on the density profile slope are stronger.
 
 %\begin{framed}
+%9) we note that the constraints in this case will be of similar strength to those of Winn 2004. \\ \\ 
+%12) we note that all these parameter combinations are plausible choices, and therefore long observations such as these will be able to either measure these parameters with confidence or place strong constraints on them.
 %\end{framed}
-
-%\begin{framed}
-%\end{framed}
-
-%\newpage
 
@@
 \centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04.eps}
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04_A.eps}
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04_B.eps}
 \centering
@@
 
+\subsection{Detection of Binary SMBHs}
+We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on the lensed central images. 
+We randomly placed two SMBHs in a circle with a radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses .
+
+We found that in most cases, it is not possible to measure the mass of both SMBHs due to the degeneracies between their masses and their positions.
+However, in a few simulation, we encountered configurations that allowed a detection of both SMBH masses.
+The constraints in such observations come from the distortion in the resolved \emph{shape} of the central image.
+
+%found cases with a shallow potential and a large stellar core, which result in bright central images, we found certain configurations in which the resolved shape of the central image can allow a detection of the masses of both SMBHs.
+
+To estimate the probability of such events we simulated 200 realizations of the positions of the SMBHs for high resolution (50 mas) 40-h long observations.
+We used various core sizes to examine the effect of central image magnification on the binary SMBHs mass measurements.
+
+%for a case with $\gamma_s=0.8$ and $R_{core}=150$ pc,
+
+We found that in XX\% of the simulations both SMBHs were detected. 
+  Although this number may seems promising, the prospects of such measurements will be limited by the number of discovered bright central images, which based on their current dearth, may be very few.
+  For larger core sizes and shallower profiles, which result in yet larger and brighter central images, the sensitivity to SMBHs \emph{decreases} again, due to the size of the image becoming larger than the Einstein radius of the SMBHs (analogous to the decrease in sensitivity to subhalos due to large source sizes).
+If such large cores are ever detected, spectral decomposition may allow increasing the sensitivity to the effects of the SMBHs \citep{hezaveh:13a}.
+
+Since suitability for such measurements will depend on the core size and slope of the stellar light, future high resolution observations with thirty meter telescopes, may help select systems with the right range of morphological parameters, to be followed up.
+
+Note that since the background source is extended, the flux subpression is \emph{less}
+
 \section{Conclusion}
-We examined the possibility of detecting central, demagnified images of strongly lensed molecular lines with ALMA.
-We find that there is a non-negligible space of realistic and plausible parameters that result in a high significance detection of the central images.
-We showed that such deep observations can either allow a measurement of the mass of the central SMBH and the stellar core size, or place strong limits on them (if not detected).
+We examined the prospects of detecting central, demagnified images of strongly lensed molecular lines with ALMA.
+We found that there is a non-negligible space of realistic and plausible parameters that result in a high significance detection of the central images.
+We showed that such deep observations can either allow a measurement of the mass of the central SMBH and the stellar core size, or place strong limits on them.
+We also studied the possibility of detecting binary SMBHs and found that under special conditions there is a non-zero probability of measuring the masses of both SMBHs, although suitable central images for such measurements may be very rare.
 
 \acknowledgements{
-}
+Acknowledge NSF?}
 
@@
 
+%\input{ms.bbl}
+
 \end{document}

### 2014-11-03 ms.tex
modifying everything

@@
 \section{Simulations}
-We generate lensed images of background sources, predict ALMA visibilities, and use them to estimate the detection significance of central images for various parameters.
-We simulate observations of a high-$J$ CO line.
-The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a XX km/s band.
+We generated lensed images of background sources, predicted ALMA visibilities, and used them to estimate the detection significance of central images for various parameters.
+We simulated observations of a high-$J$ CO line.
+The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band.
 
-We model the lens potential as a sum of three components: dark matter, stellar population and central SMBH.
-The dark matter is modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile \citep{Golse:02}.
+We modeled the lens potential as a sum of three components: dark matter, stellar population and central SMBH.
+The dark matter was modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile \citep{Golse:02}.
 As by pointed out by \citep{Keeton:03}, due to its extreme flatness in these regimes, the dark matter component has negligible influence on the central images.
-The stellar population is modeled as a a core power-law, $\Sigma\propto (r^2+s^2)^{\gamma}$.
+The stellar population is modeled as a a core power-law, $\Sigma\propto (r^2+R_{\mathrm{core}}^2)^{\gamma}$.
 Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curved).
 The grey dashed curves show a few example of core-sersic models with parameters taken from \citet{Ferrarese:06}.
-We note that although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles.
-The black hole is modeled as a simple point mass at the center of the potential. In this work we assume that all the three components are concentric.
+Although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles.
+The black hole was modeled as a simple point mass at the center of the potential. We assumed that all the three components are concentric.
+The stellar and dark mass of the lens were normalized such that they each add up to $1.5\times10^11 M_{\odot}$ in a radius of 10 kpc.
+The resulting Einstein radius if of order 1 arcsec, in agreement with galaxy-galaxy strong lenses \citep[e.g.,][]{}.
+%lens mass was set to XX $M_{\odot}$ resulting in an Einstein radius of $\sim XX''$, in agreement with galaxy-galaxy strong lenses.
+We divide this mass equally (in a radius of 10 kpc) between stellar and dark matter.
+To predict the visibilities we calculated the ALMA $uv$-coverage for a 5-$hr$ long observation (full array), using the $simobserve$ task of Common Astronomy Software Applications package, for an observing frequency of 150 GHz.
+The visibilities for each channel were calculated by computing the 2D Fourier transform of the surface brightness data maps and resampling the Fourier transform maps over the uv-coverage. 
+The noise was estimated using ALMA sensitivity calculator for a channel width of 400 km/s at 150 GHz.
 
-The lens mass is set to XX $M_{\odot}$ resulting in an Einstein radius of $\sim XX''$, in agreement with galaxy-galaxy strong lenses.
-We divide this mass equally (in a radius of 10 kpc) between stellar and dark matter.
-
-To predict the visibilities we calculate the ALMA $uv$-coverage for a 5-$hr$ long observation with the most extended antenna configuration (full array), using the $simobserve$ task of Common Astronomy Software Applications package, which results in an angular resolution of $\sim20\, \, milli$-$arcsec$ at an observing frequency of 240 GHz.
-The visibilities for each channel are calculated by computing the 2D Fourier transform of the corresponding layer of the data cube and resampling the Fourier transform maps over the uv-coverage. 
-The noise is estimated using ALMA sensitivity calculator for a channel width of 8 km/s at 240 GHz. 
-We use finite differencing of visibilities to calculate the Fisher information and the parameter covariance matrix to calculate the significance of black hole mass measurement.
-
-For simulations where we calculate the detection significance of the demagnified image, we compute the magnification at every pixel in the image plane and generate maps with and without the the demagnified flux and evaluate the detection significance of the central image by comparing the two images.
-In other simulations where the constrains on parameters are needed, we use a Fisher analysis to compute the full covariance of all parameters.
-We then marginalize over the nuisance parameters (e.g.
+For simulations where we calculated the detection significance of the demagnified image, we computed the magnification at every pixel in the image plane and generated maps with and without the the demagnified flux and evaluated the detection significance of the central image by comparing the two images.
+In other simulations where the constrains on parameters are needed, we used a Fisher analysis to compute the full covariance of all parameters.
+We used finite differencing of visibilities to calculate the gradients, and marginalize over the nuisance parameters (e.g.
 source position, lens ellipticity) to calculate the marginalized likelihood of the relevant parameters.
@@
 \subsection{Detection of Binary SMBHs}
-We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on the lensed central images. 
-We randomly placed two SMBHs in a circle with a radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses .
+We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on lensed central images. 
+We randomly placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
+We found that in most cases, it is not possible to measure the mass of both SMBHs, either because they are not near the central images or due to the degeneracy between their masses, their positions, and the core radius, or because the distortions in the central images are unresolved.
+However, when the central images are fairly extended (due to a shallow density slope and a large core size), a larger fraction of the inner 1 kpc region is covered by the central image, increasing the probability of lensing by SMBHs.
+Such images also have larger fluxes, increasing the snr of the observations and they also allow for the detection of fairly separated SMBHs.
+In this case the SMBHs can affect different parts of the central image, reducing the degeneracy between their masses.
+Under such conditions, we found some configurations that allowed a detection of both SMBH masses.
+The constraints on SMBH masses in such observations arise from the distortions in the resolved \emph{shape} of the central images.
+Figure \ref{fig:5} shows an example of such configuration when $\gamma = 0.9$ and $R_{\mathrm{core}}=300$ pc.
+Left panel shows the central image without the effects of SMBHs and the right panel shows its morphology in presence of two SMBHs.
 
-We found that in most cases, it is not possible to measure the mass of both SMBHs due to the degeneracies between their masses and their positions.
-However, in a few simulation, we encountered configurations that allowed a detection of both SMBH masses.
-The constraints in such observations come from the distortion in the resolved \emph{shape} of the central image.
+%Such distortions, however, can only be marginally resolved with ALMA, and very long integrations may be required
+
+%The positions of the SMBHs are marked with red crosses.
 
@@
 
-To estimate the probability of such events we simulated 200 realizations of the positions of the SMBHs for high resolution (50 mas) 40-h long observations.
-We used various core sizes to examine the effect of central image magnification on the binary SMBHs mass measurements.
+To estimate the probability of configurations which allow detection of binary SMBHs, we simulated many realizations of the positions of the SMBHs for a high resolution (50 mas) 50-h long observation. 
+We found that $\lesssim5\%$ of the simulations, in which the core size was larger than 200 pc, both SMBHs were detected. 
+  Although this number may seems promising, the prospects of such measurements will be limited by the number of discovered bright central images, which based on their current dearth, may be very few.
+We conclude that only under very rare conditions, and with very long observations ($>40$ hours), central image may allow us to probe binary SMBHs.
+The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses \citep{}.
 
-%for a case with $\gamma_s=0.8$ and $R_{core}=150$ pc,
-
-We found that in XX\% of the simulations both SMBHs were detected. 
-  Although this number may seems promising, the prospects of such measurements will be limited by the number of discovered bright central images, which based on their current dearth, may be very few.
-  For larger core sizes and shallower profiles, which result in yet larger and brighter central images, the sensitivity to SMBHs \emph{decreases} again, due to the size of the image becoming larger than the Einstein radius of the SMBHs (analogous to the decrease in sensitivity to subhalos due to large source sizes).
-If such large cores are ever detected, spectral decomposition may allow increasing the sensitivity to the effects of the SMBHs \citep{hezaveh:13a}.
-
-Since suitability for such measurements will depend on the core size and slope of the stellar light, future high resolution observations with thirty meter telescopes, may help select systems with the right range of morphological parameters, to be followed up.
-
-Note that since the background source is extended, the flux subpression is \emph{less}
+%Since the suitability for such measurements will depend on the core size and slope of the stellar light, future high resolution observations with thirty meter telescopes, may help select systems with the right range of morphological parameters, to be followed up.
 
@@
 We showed that such deep observations can either allow a measurement of the mass of the central SMBH and the stellar core size, or place strong limits on them.
-We also studied the possibility of detecting binary SMBHs and found that under special conditions there is a non-zero probability of measuring the masses of both SMBHs, although suitable central images for such measurements may be very rare.
+We also studied the possibility of detecting binary SMBHs and found that only under very rare conditions central images may allow detection of both SMBHs.
 

### 2014-11-03 ms.tex
modifying everything

@@
 As discussed earlier, the fluxes of central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
-Figure \ref{fig:3} shows the detection significant of a central image for a range of these parameters in a 10-h long ALMA observation.
+Figure \ref{fig:3} shows the detection significance of a central image for a range of these parameters in a 10-h long ALMA observation.
 The grey curves (dark to light) correspond to profiles with slopes of $\gamma=0.9, 1.0, 1.1,$ and 1.2.
@@
 The magnification and flux of central images is also influenced by SMBHs.
-SMBHs demagnify the images on scales comparable to the size of their Einstein radii.
+SMBHs demagnify the images on scales comparable to the size of their Einstein radii ($\sim30$ mas for a $2\times10^8M_{\odot}$ SMBH).
 The dashed curves in Figure \ref{fig:3} show the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.
@@
 core sizes) predict  a wide range of magnifications for   central images.
-Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
+Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2\times10^8 M_{\odot}$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
 
 We also find that the detection significance of the central images can increase by about $3\sigma$ for an extended source with a radius of 1 kpc compared to a point source.
-Since extended sources cover a larger area of the source plane, which may include regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
+Since extended sources occupy a larger area of the source plane, which may cover regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
 %\begin{framed}
@@
 \subsection{SMBHs and the core size}
-We studied the constraints that deep observations of molecular lines can place on the slope of the density profile, the size of the stellar core, and the mass of the SMBHs. 
+We studied the constraints that could be placed on the slope of the density profile, the size of the stellar core, and the mass of the SMBHs in such deep observations. 
 We performed a Fisher analysis to examine the constrains and parameter degeneracies in simulations in which the central images are detected, as well as those in which they are below the detection limit.
@@
 % . As seen in Figure \ref{fig:3},  this parameter combination results in a $\sim3\sigma$ detection of the central image. 
-We found that when $\gamma=1$, cores sizes larger than 100 pc can be measured with high significance. As seen in top panel of Figure \ref{fig:4}, 
+We found that when $\gamma=1$, core sizes larger than 100 pc can be measured with high significance. As seen in top panel of Figure \ref{fig:4}, 
 the mass of SMBH is degenerate with the core size: larger cores result in brighter images, whose flux can be supressed by a more massive SMBH.
@@
 %Rusin  Keeton Winn 2005
-We found that for cores $\gtrsim200$ pc, SMBH masses could be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits on the mass of SMBHs can be placed.
+We found that for cores with a radius larger than $200$ pc, central SMBH masses could be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits on the mass of SMBHs can be placed.
 We also find that when the core size is larger, the constraints on the density profile slope are stronger.
@@
 To estimate the probability of configurations which allow detection of binary SMBHs, we simulated many realizations of the positions of the SMBHs for a high resolution (50 mas) 50-h long observation. 
-We found that $\lesssim5\%$ of the simulations, in which the core size was larger than 200 pc, both SMBHs were detected. 
-  Although this number may seems promising, the prospects of such measurements will be limited by the number of discovered bright central images, which based on their current dearth, may be very few.
-We conclude that only under very rare conditions, and with very long observations ($>40$ hours), central image may allow us to probe binary SMBHs.
+We found that $\sim10\%$ of the simulations, in which the core size was larger than 200 pc, both SMBHs were detected. 
+This number is much larger than what is calculated in \citet{Li:12}, since they estimated  the probabilities for point sources, appropriate for lensed quasar samples.
+The extended structure of the background source can significantly increase the probability of
+
+  Although this number may seems promising, the prospects of such measurements will be limited by the number of discovered bright central images, which based on their current dearth, may be few.
+We conclude that, only under rare conditions, and with very long observations ($>40$ hours), central image may allow us to probe binary SMBHs.
 The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses \citep{}.
 
+%The magnified images of the lens allow a detailed reconstruction of the background source.
+It is therefore easy to distinguish that the structure in the central image is not due to the structure of the source, but are caused by lensing by binary SMBHs.
 %Since the suitability for such measurements will depend on the core size and slope of the stellar light, future high resolution observations with thirty meter telescopes, may help select systems with the right range of morphological parameters, to be followed up.
 
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 20 0 20 0, width=0.45\textwidth]{figures/f_05.eps}
+\centering
+\end{center}
+\caption{ Lensing of a central image by two SMBHs with masses of $4\times 10^8M_{\odot}$.
+The left panel shows the simulated central image.
+The red crosses show the positions of the SMBHs.
+The white circle has a radius of 1 kpc  from the center of the galaxy.
+The right panel shows the same data after convolution with the ALMA beam.
+The beam is shown in the lower panel.
+\label{fig:5}}
+\end{figure}
+
 \section{Conclusion}
-We examined the prospects of detecting central, demagnified images of strongly lensed molecular lines with ALMA.
+We have examined the prospects of detecting central, demagnified images of strongly lensed molecular lines with ALMA.
 We found that there is a non-negligible space of realistic and plausible parameters that result in a high significance detection of the central images.

### 2014-11-03 ms.tex
modifying everything

@@
 
-\shortauthors{Y. Hezaveh}
+\shortauthors{Y. Hezaveh et al.}
 
@@
 We examine the prospects of detecting demagnified images of gravitational lenses in observations of strongly lensed mm-wave molecular emission lines with ALMA.
-We model the lensing galaxies as a superposition of a dark matter component, a stellar population, and a central supermassive black hole and forecast the detection of the central images for a range of relevant parameters (e.g.
+We model the lensing galaxies as a superposition of a dark matter component, a stellar component, and a central supermassive black hole and forecast the detection of the central images for a range of relevant parameters (e.g.
 stellar core and black hole mass).
-We find that over a large range of acceptable parameters, future deep observations of lensed molecular lines with ALMA will be able to detect the central images at $\gtrsim 3\sigma$ significance.
-We use Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios.
+We find that over a large range of acceptable parameters, future deep observations of lensed molecular lines with ALMA should be able to detect the central images at $\gtrsim 3\sigma$ significance.
+We use a Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios and find that for large stellar cores, both the core size and the mass of the central SMBHs could be measured.
+We also study the prospects of detecting binary SMBHs in such observations, and find that only under very rare condition such observations could be
 
@@
 
-%\begin{framed}
-\red{needs work}
-The individual behavior \citep{} and statistical properties of central images in lens populations have been extensively studied \citep[e.g.][]{Wallington:93, Evans:02, Keeton:03},  suggesting that central images could have a wide range of magnifications.
-Observational searches for these images have found a number of candidates \citep[e.g.][]{Inada:05}, however, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.\red{(Inada:08 is a cluster?)}
-To avoid the possibility of absorption in the lens, most studies have focused on strongly lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from faint emission from the lens galaxies.
+The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.][]{Wallington:93, Evans:02, Keeton:03}.
+These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}.
+Observational searches for these images have found a number of candidates \citep[e.g.][]{}. Although observations
+of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:05}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.
+To avoid the possibility of absorption in the lens, most searches have focused on strongly lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies.
 
@@
 In contrast to lensed quasars, these sources are extended over hundreds of parsecs and can cover a larger area of the source plane.
-This can allow them to occupy the less demagnified regions of the source plane, allowing a higher flux for the central image \citep[the opposite effect of magnification damping due to extended sources,, see e.g.][]{hezaveh:11}.
+This can allow them to occupy the less demagnified regions of the source plane, allowing a higher flux for the central image \citep[the opposite effect of magnification damping due to extended sources, see e.g.,][]{hezaveh:11}.
 
- In this letter, we explore the possibility of detecting the central lensed images in such deep observations and investigate the constraints that could be placed on the core size, mass of SMBHs, and the slope of the density profiles from detection, or non-detection of such images.
+ In this letter, we explore the possibility of detecting central lensed images in such deep observations and investigate the constraints that could be placed on the core size, mass of SMBHs, and the slope of the density profiles from detection, or non-detection of such images.
 We also examine if binary SMBHs can possibly be detected in such observations.
@@
 \end{center}
-\caption{ Covariance matrix of parameters for a few different scenarios.
+\caption{ Parameter covariance matrices for two simulations (after marginalization over nuisance parameters).
+Top panel shows that when the core size is small the mass of the SMBH is not measured and only an upper limit can be placed on it.
+The bottom panel, shows that for larger core sizes, the mass of the SMBH could be measured by high significance.
 \label{fig:4}}

### 2014-11-03 ms.tex
modifying everything

@@
 We use a Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios and find that for large stellar cores, both the core size and the mass of the central SMBHs could be measured.
-We also study the prospects of detecting binary SMBHs in such observations, and find that only under very rare condition such observations could be
+We also study the prospects of detecting binary SMBHs with such observations, and find that under rare conditions we may be able to measure the massed of both SMBHs using the distortions of the central images.
 
@@
 %In this section, we estimate the detection significance of central lensed images of molecular lines with ALMA. 
-As discussed earlier, the fluxes of central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
+The fluxes of central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
 Figure \ref{fig:3} shows the detection significance of a central image for a range of these parameters in a 10-h long ALMA observation.
 The grey curves (dark to light) correspond to profiles with slopes of $\gamma=0.9, 1.0, 1.1,$ and 1.2.
-As seen in this figure, larger stellar cores result in brighter images.
-%Lensing studies have shown that the total profiles of galaxies are very close to isothermal \red{cite{}}.
+The source has a Gaussian profile with an rms of 600 pc and the lensed images have a fold configuration. 
+As seen in this figure, larger stellar cores result in brighter images. %Lensing studies have shown that the total profiles of galaxies are very close to isothermal \red{cite{}}. 
 When $\gamma=1.0$ and with a core size larger than 150 pc, such observations should be able to detect the central images with more than $5\sigma$ significance.
-For significantly shallower ($\gamma<0.8$) profile slopes with larger cores, the central image is \emph{magnified} and its detection should be trivial.
+For significantly shallower ($\gamma<0.8$) profiles and larger cores, the central image is \emph{magnified} and its detection should be trivial.
 The magnification and flux of central images is also influenced by SMBHs.
@@
 
-As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, plausible parameters (e.g.
-core sizes) predict  a wide range of magnifications for   central images.
+As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, plausible parameters predict  a wide range of magnifications for   central images.
 Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2\times10^8 M_{\odot}$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
 
-We also find that the detection significance of the central images can increase by about $3\sigma$ for an extended source with a radius of 1 kpc compared to a point source.
+We also find that the detection significance of the central images can significantly increase for an extended source with a radius of 1 kpc compared to a point source.
 Since extended sources occupy a larger area of the source plane, which may cover regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
+The red curves in Figure \ref{fig:3} show the drop in the flux of the image for a smaller (300 pc) source.
 %\begin{framed}
@@
 \subsection{SMBHs and the core size}
-We studied the constraints that could be placed on the slope of the density profile, the size of the stellar core, and the mass of the SMBHs in such deep observations. 
+Here, we study the constraints that could be placed on the slope of the density profile, the size of the stellar core, and the mass of the SMBHs in such deep observations. 
 We performed a Fisher analysis to examine the constrains and parameter degeneracies in simulations in which the central images are detected, as well as those in which they are below the detection limit.
@@
 %Rusin  Keeton Winn 2005
-We found that for cores with a radius larger than $200$ pc, central SMBH masses could be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits on the mass of SMBHs can be placed.
+We find that for cores with a radius larger than $200$ pc, central SMBH masses can be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits on the mass of SMBHs can be placed.
 We also find that when the core size is larger, the constraints on the density profile slope are stronger.
@@
 We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on lensed central images. 
-We randomly placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
+We placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in a random position incise a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
 We found that in most cases, it is not possible to measure the mass of both SMBHs, either because they are not near the central images or due to the degeneracy between their masses, their positions, and the core radius, or because the distortions in the central images are unresolved.
@@
 We conclude that, only under rare conditions, and with very long observations ($>40$ hours), central image may allow us to probe binary SMBHs.
-The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses \citep{}.
+The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses.
 
@@
 \acknowledgements{
-Acknowledge NSF?}
+\red{Acknowledge NSF?}}
 

### 2014-11-03 ms.tex
modifying everything

@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references}
 
 %\input{ms.bbl}
+\begin{thebibliography}{28}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Barnes} \& {Hernquist}(1992)}]{Barnes:92}
+{Barnes}, J.~E., \& {Hernquist}, L. 1992, \araa, 30, 705
+
+\bibitem[{{Begelman} {et~al.}(1980){Begelman}, {Blandford}, \&
+  {Rees}}]{Begelman:80}
+{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1980, \nat, 287, 307
+
+\bibitem[{{Bussmann} {et~al.}(2013){Bussmann}, {P{\'e}rez-Fournon}, {Amber},
+  {Calanog}, {Gurwell}, {Dannerbauer}, {De Bernardis}, {Fu}, {Harris}, {Krips},
+  {Lapi}, {Maiolino}, {Omont}, {Riechers}, {Wardlow}, {Baker}, {Birkinshaw},
+  {Bock}, {Bourne}, {Clements}, {Cooray}, {De Zotti}, {Dunne}, {Dye}, {Eales},
+  {Farrah}, {Gavazzi}, {Gonz{\'a}lez Nuevo}, {Hopwood}, {Ibar}, {Ivison},
+  {Laporte}, {Maddox}, {Mart{\'{\i}}nez-Navajas}, {Michalowski}, {Negrello},
+  {Oliver}, {Roseboom}, {Scott}, {Serjeant}, {Smith}, {Smith}, {Streblyanska},
+  {Valiante}, {van der Werf}, {Verma}, {Vieira}, {Wang}, \&
+  {Wilner}}]{bussmann:13}
+{Bussmann}, R.~S., {P{\'e}rez-Fournon}, I., {Amber}, S., {et~al.} 2013, \apj,
+  779, 25, 1309.0836
+
+\bibitem[{{Ebisuzaki} {et~al.}(1991){Ebisuzaki}, {Makino}, \&
+  {Okumura}}]{Ebisuzaki:91}
+{Ebisuzaki}, T., {Makino}, J., \& {Okumura}, S.~K. 1991, \nat, 354, 212
+
+\bibitem[{{Evans} \& {Hunter}(2002)}]{Evans:02}
+{Evans}, N.~W., \& {Hunter}, C. 2002, \apj, 575, 68, astro-ph/0204206
+
+\bibitem[{{Ferrarese} \& {Merritt}(2000)}]{Ferrarese:00}
+{Ferrarese}, L., \& {Merritt}, D. 2000, \apjl, 539, L9, astro-ph/0006053
+
+\bibitem[{{Ferrarese} {et~al.}(2006){Ferrarese}, {C{\^o}t{\'e}}, {Jord{\'a}n},
+  {Peng}, {Blakeslee}, {Piatek}, {Mei}, {Merritt}, {Milosavljevi{\'c}},
+  {Tonry}, \& {West}}]{Ferrarese:06}
+{Ferrarese}, L., {C{\^o}t{\'e}}, P., {Jord{\'a}n}, A., {et~al.} 2006, \apjs,
+  164, 334, astro-ph/0602297
+
+\bibitem[{{Gebhardt} {et~al.}(2000){Gebhardt}, {Bender}, {Bower}, {Dressler},
+  {Faber}, {Filippenko}, {Green}, {Grillmair}, {Ho}, {Kormendy}, {Lauer},
+  {Magorrian}, {Pinkney}, {Richstone}, \& {Tremaine}}]{Gebhardt:00}
+{Gebhardt}, K., {Bender}, R., {Bower}, G., {et~al.} 2000, \apjl, 539, L13,
+  astro-ph/0006289
+
+\bibitem[{{Golse} \& {Kneib}(2002)}]{Golse:02}
+{Golse}, G., \& {Kneib}, J.-P. 2002, \aap, 390, 821, astro-ph/0112138
+
+\bibitem[{{Hezaveh} {et~al.}(2014){Hezaveh}, {Dalal}, {Holder}, {Kisner}, \&
+  {Kuhlen}}]{hezaveh:14a}
+{Hezaveh}, Y., {Dalal}, N., {Holder}, G., {Kisner}, T., \& {Kuhlen}, M. 2014,
+  ArXiv e-prints, 1403.2720
+
+\bibitem[{{Hezaveh}(2014)}]{hezaveh:14b}
+{Hezaveh}, Y.~D. 2014, \apjl, 791, L41, 1408.3631
+
+\bibitem[{{Hezaveh} \& {Holder}(2011)}]{hezaveh:11}
+{Hezaveh}, Y.~D., \& {Holder}, G.~P. 2011, \apj, 734, 52, 1010.0998
+
+\bibitem[{{Hezaveh} {et~al.}(2013){Hezaveh}, {Marrone}, {Fassnacht}, {Spilker},
+  {Vieira}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss}, {Benson},
+  {Bleem}, {Bothwell}, {Brodwin}, {Carlstrom}, {Chang}, {Chapman}, {Crawford},
+  {Crites}, {De Breuck}, {de Haan}, {Dobbs}, {Fomalont}, {George}, {Gladders},
+  {Gonzalez}, {Greve}, {Halverson}, {High}, {Holder}, {Holzapfel}, {Hoover},
+  {Hrubes}, {Husband}, {Hunter}, {Keisler}, {Lee}, {Leitch}, {Lueker},
+  {Luong-Van}, {Malkan}, {McIntyre}, {McMahon}, {Mehl}, {Menten}, {Meyer},
+  {Mocanu}, {Murphy}, {Natoli}, {Padin}, {Plagge}, {Reichardt}, {Rest}, {Ruel},
+  {Ruhl}, {Sharon}, {Schaffer}, {Shaw}, {Shirokoff}, {Stalder}, {Staniszewski},
+  {Stark}, {Story}, {Vanderlinde}, {Wei{\ss}}, {Welikala}, \&
+  {Williamson}}]{hezaveh:13b}
+{Hezaveh}, Y.~D., {Marrone}, D.~P., {Fassnacht}, C.~D., {et~al.} 2013, \apj,
+  767, 132, 1303.2722
+
+\bibitem[{{Inada} {et~al.}(2005){Inada}, {Oguri}, {Keeton}, {Eisenstein},
+  {Castander}, {Chiu}, {Hall}, {Hennawi}, {Johnston}, {Pindor}, {Richards},
+  {Rix}, {Schneider}, \& {Zheng}}]{Inada:05}
+{Inada}, N., {Oguri}, M., {Keeton}, C.~R., {et~al.} 2005, \pasj, 57, L7,
+  astro-ph/0503310
+
+\bibitem[{{Keeton}(2003)}]{Keeton:03}
+{Keeton}, C.~R. 2003, \apj, 582, 17, astro-ph/0206243
+
+\bibitem[{{Kormendy} \& {Bender}(2009)}]{Kormendy:09}
+{Kormendy}, J., \& {Bender}, R. 2009, \apjl, 691, L142, 0901.3778
+
+\bibitem[{{Kormendy} \& {Ho}(2013)}]{Kormendy:13}
+{Kormendy}, J., \& {Ho}, L.~C. 2013, \araa, 51, 511, 1304.7762
+
+\bibitem[{{Kormendy} \& {Richstone}(1995)}]{Kormendy:95}
+{Kormendy}, J., \& {Richstone}, D. 1995, \araa, 33, 581
+
+\bibitem[{{Li} {et~al.}(2012){Li}, {Mao}, {Gao}, {Loeb}, \& {di
+  Stefano}}]{Li:12}
+{Li}, N., {Mao}, S., {Gao}, L., {Loeb}, A., \& {di Stefano}, R. 2012, \mnras,
+  419, 2424, 1110.0887
+
+\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
+  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
+  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
+  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
+  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
+  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
+  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
+  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
+  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
+  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
+  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
+  {Maloney}, {Matsuhara}, {Michaowski}, {Murphy}, {Naylor}, {Nguyen},
+  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
+  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{negrello:10}
+{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330,
+  800, 1011.1255
+
+\bibitem[{{Rocha} {et~al.}(2013){Rocha}, {Peter}, {Bullock}, {Kaplinghat},
+  {Garrison-Kimmel}, {O{\~n}orbe}, \& {Moustakas}}]{Rocha:13}
+{Rocha}, M., {Peter}, A.~H.~G., {Bullock}, J.~S., {et~al.} 2013, \mnras, 430,
+  81, 1208.3025
+
+\bibitem[{{Thomas} {et~al.}(2014){Thomas}, {Saglia}, {Bender}, {Erwin}, \&
+  {Fabricius}}]{Thomas:14}
+{Thomas}, J., {Saglia}, R.~P., {Bender}, R., {Erwin}, P., \& {Fabricius}, M.
+  2014, \apj, 782, 39, 1311.3783
+
+\bibitem[{{Tremaine} {et~al.}(2002){Tremaine}, {Gebhardt}, {Bender}, {Bower},
+  {Dressler}, {Faber}, {Filippenko}, {Green}, {Grillmair}, {Ho}, {Kormendy},
+  {Lauer}, {Magorrian}, {Pinkney}, \& {Richstone}}]{Tremaine:02}
+{Tremaine}, S., {Gebhardt}, K., {Bender}, R., {et~al.} 2002, \apj, 574, 740,
+  astro-ph/0203468
+
+\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
+  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
+  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
+  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
+  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
+  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
+  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
+  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
+  {Zenteno}}]{vieira:10}
+{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
+  763, 0912.2338
+
+\bibitem[{{Vieira} {et~al.}(2013){Vieira}, {Marrone}, {Chapman}, {De Breuck},
+  {Hezaveh}, {Wei{$\beta$}}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss},
+  {Benson}, {Biggs}, {Bleem}, {Bock}, {Bothwell}, {Bradford}, {Brodwin},
+  {Carlstrom}, {Chang}, {Crawford}, {Crites}, {de Haan}, {Dobbs}, {Fomalont},
+  {Fassnacht}, {George}, {Gladders}, {Gonzalez}, {Greve}, {Gullberg},
+  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hoover}, {Hrubes}, {Hunter},
+  {Keisler}, {Lee}, {Leitch}, {Lueker}, {Luong-van}, {Malkan}, {McIntyre},
+  {McMahon}, {Mehl}, {Menten}, {Meyer}, {Mocanu}, {Murphy}, {Natoli}, {Padin},
+  {Plagge}, {Reichardt}, {Rest}, {Ruel}, {Ruhl}, {Sharon}, {Schaffer}, {Shaw},
+  {Shirokoff}, {Spilker}, {Stalder}, {Staniszewski}, {Stark}, {Story},
+  {Vanderlinde}, {Welikala}, \& {Williamson}}]{vieira:13}
+{Vieira}, J.~D., {Marrone}, D.~P., {Chapman}, S.~C., {et~al.} 2013, \nat, 495,
+  344, 1303.2723
+
+\bibitem[{{Wallington} \& {Narayan}(1993)}]{Wallington:93}
+{Wallington}, S., \& {Narayan}, R. 1993, \apj, 403, 517
+
+\bibitem[{{Wei{\ss}} {et~al.}(2013){Wei{\ss}}, {De Breuck}, {Marrone},
+  {Vieira}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss}, {Benson},
+  {B{\'e}thermin}, {Biggs}, {Bleem}, {Bock}, {Bothwell}, {Bradford}, {Brodwin},
+  {Carlstrom}, {Chang}, {Chapman}, {Crawford}, {Crites}, {de Haan}, {Dobbs},
+  {Downes}, {Fassnacht}, {George}, {Gladders}, {Gonzalez}, {Greve},
+  {Halverson}, {Hezaveh}, {High}, {Holder}, {Holzapfel}, {Hoover}, {Hrubes},
+  {Husband}, {Keisler}, {Lee}, {Leitch}, {Lueker}, {Luong-Van}, {Malkan},
+  {McIntyre}, {McMahon}, {Mehl}, {Menten}, {Meyer}, {Murphy}, {Padin},
+  {Plagge}, {Reichardt}, {Rest}, {Rosenman}, {Ruel}, {Ruhl}, {Schaffer},
+  {Shirokoff}, {Spilker}, {Stalder}, {Staniszewski}, {Stark}, {Story},
+  {Vanderlinde}, {Welikala}, \& {Williamson}}]{Weiss:13}
+{Wei{\ss}}, A., {De Breuck}, C., {Marrone}, D.~P., {et~al.} 2013, \apj, 767,
+  88, 1303.2726
+
+\bibitem[{{Winn} {et~al.}(2004){Winn}, {Rusin}, \& {Kochanek}}]{Winn:04}
+{Winn}, J.~N., {Rusin}, D., \& {Kochanek}, C.~S. 2004, \nat, 427, 613,
+  astro-ph/0312136
+
+\end{thebibliography}
 

### 2014-11-05 ms.tex
modifying everything

--- 2014-11-03 ms.tex
@@
 stellar core and black hole mass).
-We find that over a large range of acceptable parameters, future deep observations of lensed molecular lines with ALMA should be able to detect the central images at $\gtrsim 3\sigma$ significance.
-We use a Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios and find that for large stellar cores, both the core size and the mass of the central SMBHs could be measured.
-We also study the prospects of detecting binary SMBHs with such observations, and find that under rare conditions we may be able to measure the massed of both SMBHs using the distortions of the central images.
+We find that over a large range of plausible parameters, future deep observations of lensed molecular lines with ALMA should be able to detect the central images at $\gtrsim 3\sigma$ significance.
+We use a Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios and find that for large stellar cores, both the core size and the mass of the central SMBHs can be accurately measured.
+We also study the prospects of detecting binary SMBHs with such observations and find that only under rare conditions and with very long integrations ($\sim$40-hr) the massed of both SMBHs may be measured using the distortions of central images.
 
@@
 gravitational lensing: strong ---
-galaxies: formation ---
-galaxies: high-redshift}
+galaxies: formation}
 
@@
 It is now established that almost every massive galaxy harbors a SMBH at its center with a mass that strongly correlates with the mass of the host galaxy \citep{Kormendy:95,Ferrarese:00,Gebhardt:00,Tremaine:02}.
-In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions.
-\citep[e.g][]{Barnes:92,Ebisuzaki:91}.
-Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g][]{Rocha:13}.
+In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions \citep[e.g.,][]{Barnes:92,Ebisuzaki:91}.
+Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g.,][]{Rocha:13}.
 Mapping the matter density in the central regions of galaxies can thus shed light on various astrophysical phenomena.
@@
 Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy mergers.
-Cores in massive ellipticals, therefore, should be the result of different (not merger) mechanisms.
+Cores in massive ellipticals, therefore, may be the result of a different (not merger) process.
 ``Black hole scouring'' is a plausible mechanism that can explain core-formation in these galaxies \citep{Thomas:14}.
@@
 %\begin{framed}
-It is thought that during a merger, the SMBHs of the two merging galaxies form a binary which sinks to the center of the potential.
+It is thought that during a merger, the SMBHs of the two merging galaxies form a binary, which sinks to the center of the potential.
 The two orbiting SMBHs then dissipate angular momentum through three-body interactions with nearby central stars, pushing the stars to higher orbits and ``scouring out'' a core.
@@
 For double and quad image configurations, a third and a fifth image are predicted to exist near the centers of lensing galaxies.
-Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep{}.
+Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.
 It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep singular density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter.
 %Lack of detection of central images in almost all lenses suggests steep central density profiles in lens galaxies.
+
 In addition to their low flux, the fact that central images coincide with the emission from lens galaxies makes their detection even harder.
@@
 of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:05}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.
-To avoid the possibility of absorption in the lens, most searches have focused on strongly lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies.
+To avoid the possibility of absorption in the lens, most searches have focused on lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies.
 
@@
 In particular, ALMA observations of these sources have revealed that the background galaxies are dusty, starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
-These observations showed that the extreme brightness of the sources in combination with the high sensitivity of ALMA results in very high signal to noise ratios \citep[e.g.
-the lens models in][were based on just $\sim50$ second long observations]{hezaveh:13b}.
+These observations showed that the extreme brightness of the sources, in combination with the high sensitivity of ALMA, result in very high signal to noise observations \citep[e.g., the lens models in][were based on just $\sim50$ second long observations]{hezaveh:13b}.
 Motivated by the discovery of this population and the operation of ALMA, here we revisit the issue of detecting central images.
@@
 If a central image of a lensed molecular line is detected, it will be readily identifiable since it will correspond to the redshift of the source, leaving no doubt about its origin.
-In addition, since these lines are in mm-bands, the line fluxes are very unlikely to be suppressed due to absorption in the lens.
+In addition, since these lines are in mm-wave, the line fluxes are very unlikely to be suppressed by absorption in the lens.
 In contrast to lensed quasars, these sources are extended over hundreds of parsecs and can cover a larger area of the source plane.
-This can allow them to occupy the less demagnified regions of the source plane, allowing a higher flux for the central image \citep[the opposite effect of magnification damping due to extended sources, see e.g.,][]{hezaveh:11}.
+This can allow them to occupy the less demagnified regions of the source plane, allowing a higher flux for the central image \citep[similar to magnification damping of highly magnified images due to finite source effects, see e.g.,][]{hezaveh:11}.
 
  In this letter, we explore the possibility of detecting central lensed images in such deep observations and investigate the constraints that could be placed on the core size, mass of SMBHs, and the slope of the density profiles from detection, or non-detection of such images.
-We also examine if binary SMBHs can possibly be detected in such observations.
+We also examine if
+ such observations can possibly detect binary SMBHs, using the distortions they may cause in the central images. 
  In Section 2 we describe the simulations, in Section 3 we present the results and discuss them, and finally conclude in Section 4.
@@
 We simulated observations of a high-$J$ CO line.
-The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band.
+The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band \citep{Bothwell:12}.
 
-We modeled the lens potential as a sum of three components: dark matter, stellar population and central SMBH.
-The dark matter was modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile \citep{Golse:02}.
-As by pointed out by \citep{Keeton:03}, due to its extreme flatness in these regimes, the dark matter component has negligible influence on the central images.
-The stellar population is modeled as a a core power-law, $\Sigma\propto (r^2+R_{\mathrm{core}}^2)^{\gamma}$.
-Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curved).
-The grey dashed curves show a few example of core-sersic models with parameters taken from \citet{Ferrarese:06}.
-Although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles.
+We modeled the lens potential as a sum of three components: dark matter, stellar population and a central SMBH.
+The dark matter component was modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile in the innermost regions \citep{Golse:02}.
+As  pointed out by \citet{Keeton:03}, due to its extreme flatness in these regimes, the dark matter component has negligible influence on the central images.
+The stellar population is modeled as a a cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma}$.
+Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curve).
+The grey dashed curves show a few examples of core-sersic models with parameters taken from \citet{Ferrarese:06}.
+Although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles in the inner few kpc.
 The black hole was modeled as a simple point mass at the center of the potential. We assumed that all the three components are concentric.
-The stellar and dark mass of the lens were normalized such that they each add up to $1.5\times10^11 M_{\odot}$ in a radius of 10 kpc.
-The resulting Einstein radius if of order 1 arcsec, in agreement with galaxy-galaxy strong lenses \citep[e.g.,][]{}.
+The stellar and dark mass of the lens were normalized such that they each contain $1.5\times10^{11} M_{\odot}$ in a radius of 10 kpc.
+The resulting Einstein radius is of order 1 arcsec, in agreement with galaxy-galaxy strong lenses \citep[e.g.,][]{}.
 %lens mass was set to XX $M_{\odot}$ resulting in an Einstein radius of $\sim XX''$, in agreement with galaxy-galaxy strong lenses.
 We divide this mass equally (in a radius of 10 kpc) between stellar and dark matter.
-To predict the visibilities we calculated the ALMA $uv$-coverage for a 5-$hr$ long observation (full array), using the $simobserve$ task of Common Astronomy Software Applications package, for an observing frequency of 150 GHz.
-The visibilities for each channel were calculated by computing the 2D Fourier transform of the surface brightness data maps and resampling the Fourier transform maps over the uv-coverage. 
+To predict the visibilities we calculated the ALMA $uv$-coverage of a 10-$hr$ long observation (full array), using the $simobserve$ task of Common Astronomy Software Applications package, for an observing frequency of 150 GHz.
+The model visibilities were calculated by computing the 2D Fourier transform of the surface brightness data maps and resampling the Fourier transform maps over the $uv$-coverage. 
 The noise was estimated using ALMA sensitivity calculator for a channel width of 400 km/s at 150 GHz.
@@
 \centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04_A.eps}
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04_B.eps}
+\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04.eps}
 \centering

### 2014-11-05 ms.tex
modifying everything

@@
 \centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_02.eps}
+\includegraphics[trim= 10 0 0 0, clip, width=0.5\textwidth]{figures/f_02.eps}
 \centering
 \end{center}
-\caption{ illustration of the central image in 2 cases: 
+\caption{ Left panel shows the strongly lensed images of a background source, when the lensing potential is very steep and cuspy, resulting in large demagnification (and disappearance) of the central image.
+The right panel shows images for the same lens parameters and a core of 400 pc.
+The red box is centered on the  central image.
 \label{fig1}}
@@
 \centering
-\includegraphics[trim= 0 0 0 0, width=0.45\textwidth]{figures/f_04.eps}
+\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{figures/f_04.eps}
 \centering
@@
 \centering
-\includegraphics[trim= 20 0 20 0, width=0.45\textwidth]{figures/f_05.eps}
+\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{figures/f_05.eps}
 \centering

### 2014-11-05 ms.tex
modifying everything

@@
 These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}.
-Observational searches for these images have found a number of candidates \citep[e.g.][]{}. Although observations
-of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:05}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.
-To avoid the possibility of absorption in the lens, most searches have focused on lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies.
+Observational searches for these images have found a number of candidates. Although observations
+of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:08}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.
+To avoid the possibility of absorption in the lens, most searches have focused on lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies \citep[e.g.,][]{Zhang:07}.
 

### 2014-11-05 ms.tex
modifying everything

@@
 In such mergers, the central structure of the resulting galaxy is dominated by the inner structure of the more concentrated progenitor.
-Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy mergers.
+Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy merger.
 Cores in massive ellipticals, therefore, may be the result of a different (not merger) process.
@@
 Deep ALMA observations of molecular line emission in these sources are likely to be carried out for various reasons \citep[e.g.,][]{hezaveh:14a,hezaveh:14b}.
-If a central image of a lensed molecular line is detected, it will be readily identifiable since it will correspond to the redshift of the source, leaving no doubt about its origin.
+If a central image of a lensed molecular line is detected in such observations, it will be readily identifiable, since it will correspond to the redshift of the source, leaving no doubt about its origin.
 In addition, since these lines are in mm-wave, the line fluxes are very unlikely to be suppressed by absorption in the lens.
 In contrast to lensed quasars, these sources are extended over hundreds of parsecs and can cover a larger area of the source plane.
-This can allow them to occupy the less demagnified regions of the source plane, allowing a higher flux for the central image \citep[similar to magnification damping of highly magnified images due to finite source effects, see e.g.,][]{hezaveh:11}.
+This can allow them to overlap with the less demagnified regions of the source plane, further increasing the flux of the central images \citep[analogous to magnification damping of highly magnified images due to finite source effects, see e.g.,][]{hezaveh:11}.
 
@@
 We simulated observations of a high-$J$ CO line.
-The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band \citep{Bothwell:12}.
+The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band, a typical value for high redshift dusty galaxies \citep{Bothwell:12}.
 
@@
 For simulations where we calculated the detection significance of the demagnified image, we computed the magnification at every pixel in the image plane and generated maps with and without the the demagnified flux and evaluated the detection significance of the central image by comparing the two images.
-In other simulations where the constrains on parameters are needed, we used a Fisher analysis to compute the full covariance of all parameters.
+In other simulations, where the constrains on parameters are needed, we used a Fisher analysis to compute the full covariance of all parameters.
 We used finite differencing of visibilities to calculate the gradients, and marginalize over the nuisance parameters (e.g.
@@
 \centering
-\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
+\includegraphics[trim= 0 0 5 6, clip, width=0.5\textwidth]{figures/f_01.eps}
 \centering
@@
 
-%\newpage
+\newpage
+
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{figures/f_03.eps}
+\centering
+\end{center}
+\caption{ Detection significance of a central image, as a function of the stellar core size for a 10-hr long ALMA observation. 
+The fiducial model (solid black curve) corresponds to $\gamma_{stellar}=1.0$, $M_{\mathrm{BH}}=2\times10^8 M_{\odot}$, and a source size of 500 pc (radius).
+The dashed black curve shows the detection significance when the SMBH is removed and the solid red curve shows the effect of a steeper density profile ($\gamma_{\mathrm{stellar}}=1.1$).
+The solid blue and gray dotted curves show the detections for a source with a radius of 1 kpc and 250 pc respectively.
+%The gray shades correspond to different slopes for the stellar component.
+The solid curves correspond to a case without a SMBH while the dashed curves show the results when a $2\times10^8M_{\odot}$ SMBH is placed at the center of the lens.
+%The source has a Gaussian light profile with an rms of 600 pc. The red curves show the same predictions when $\gamma=1$, for a source with rms of 300 pc.
+\label{fig:3}}
+\end{figure}
+
 \section{Results and Discussions}
@@
 Figure \ref{fig:3} shows the detection significance of a central image for a range of these parameters in a 10-h long ALMA observation.
-The grey curves (dark to light) correspond to profiles with slopes of $\gamma=0.9, 1.0, 1.1,$ and 1.2.
-The source has a Gaussian profile with an rms of 600 pc and the lensed images have a fold configuration. 
+The figure shows the detection significance of the demagnified central flux, as a function of the stellar core size.
+The fiducial model (black curve) has a stellar profile slope of $\gamma_s=1.0$, and a $2\times10^8M_{\odot}$ SMBH, with a background source 
+with a Gaussian profile with an rms of 500 pc.  The red curve shows the effect of a steeper density slope, suppressing the flux of the central image.
+
 As seen in this figure, larger stellar cores result in brighter images. %Lensing studies have shown that the total profiles of galaxies are very close to isothermal \red{cite{}}. 
-When $\gamma=1.0$ and with a core size larger than 150 pc, such observations should be able to detect the central images with more than $5\sigma$ significance.
+In the absence of a massive black hole, when $\gamma=1.0$ and with a core size larger than 150 pc, such observations should be able to detect the central images with more than $5\sigma$ significance.
 For significantly shallower ($\gamma<0.8$) profiles and larger cores, the central image is \emph{magnified} and its detection should be trivial.
@@
 As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, plausible parameters predict  a wide range of magnifications for   central images.
-Although for some plausible parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2\times10^8 M_{\odot}$,$R_{core}<300 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
+Although for some parameter combinations (e.g., $\gamma_{s}=1.1,$ $M_{BH} = 2\times10^8 M_{\odot}$,$R_{core}<200 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
 
@@
 Since extended sources occupy a larger area of the source plane, which may cover regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
-The red curves in Figure \ref{fig:3} show the drop in the flux of the image for a smaller (300 pc) source.
+The solid blue curve in Figure \ref{fig:3} shows increase in the flux of the demagnified image for a larger source (with a radius of 1 kpc).
+In contrast, the flux of a source with a radius of 250 pc is severely supressed, largely by the central SMBH (dotted grey curve).
+As such, it is important to consider that various
+
 %\begin{framed}
@@
 
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{figures/f_03.eps}
-\centering
-\end{center}
-\caption{ Detection significance of a central image as a function of the stellar core size for a 10-hr long ALMA observation.
-The gray shades correspond to different slopes for the stellar component.
-The solid curves correspond to a case without a SMBH while the dashed curves show the results when a $2\times10^8M_{\odot}$ SMBH is placed at the center of the lens.
-The source has a Gaussian light profile with an rms of 600 pc. The red curves show the same predictions when $\gamma=1$, for a source with rms of 300 pc.
-\label{fig:3}}
-\end{figure}
-
 \subsection{SMBHs and the core size}
@@
 intrinsic source flux and position) to obtain the marginalized likelihood of the relevant parameters.
- Figure \ref{fig:4} shows the parameter covariance for two examples with different core radii (top panel:  $R_{core}$=170 pc, bottom panel: $R_{core}$=450 pc).
+ Figure \ref{fig:4} shows the parameter covariance for two simulations with different core radii (black contours:  $R_{core}$=170 pc, red contours: $R_{core}$=400 pc).
 % . As seen in Figure \ref{fig:3},  this parameter combination results in a $\sim3\sigma$ detection of the central image. 
-We found that when $\gamma=1$, core sizes larger than 100 pc can be measured with high significance. As seen in top panel of Figure \ref{fig:4}, 
-the mass of SMBH is degenerate with the core size: larger cores result in brighter images, whose flux can be supressed by a more massive SMBH.
-This degeneracy,  however,  breaks when the core size is very large. 
-Large cores produce more extended central images that are spatially resolved.
+We found that when $\gamma=1$, core sizes larger than 100 pc can be measured with high significance. As seen in Figure \ref{fig:4}, 
+for small cores, the mass of SMBH is highly degenerate with the core size: larger cores result in brighter images, whose flux can be supressed by a more massive SMBH.
+This degeneracy,  however,  is reduced when the core size is very large: large cores produce more extended central images that are spatially resolved.
 The distortion caused by a SMBH can distort this image on smaller scales, resulting in a distinct dip in its surface brightness.
@@
 %Rusin  Keeton Winn 2005
-We find that for cores with a radius larger than $200$ pc, central SMBH masses can be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits on the mass of SMBHs can be placed.
+We find that for cores with a radius larger than $200$ pc, central SMBH masses can be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits can be placed on the mass of SMBHs.
 We also find that when the core size is larger, the constraints on the density profile slope are stronger.
@@
 We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on lensed central images. 
-We placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in a random position incise a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
-We found that in most cases, it is not possible to measure the mass of both SMBHs, either because they are not near the central images or due to the degeneracy between their masses, their positions, and the core radius, or because the distortions in the central images are unresolved.
+We placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in random positions inside a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
+We found that in most cases, it is not possible to measure the mass of both SMBHs, either because they are not near the central images or due to the degeneracy between their masses, their positions, and the core radius.
+%, or because the distortions in the central images are unresolved.
 However, when the central images are fairly extended (due to a shallow density slope and a large core size), a larger fraction of the inner 1 kpc region is covered by the central image, increasing the probability of lensing by SMBHs.
-Such images also have larger fluxes, increasing the snr of the observations and they also allow for the detection of fairly separated SMBHs.
+Such images also have larger fluxes, increasing the signal to noise of the observations and they also allow for the detection of fairly separated SMBHs.
 In this case the SMBHs can affect different parts of the central image, reducing the degeneracy between their masses.
-Under such conditions, we found some configurations that allowed a detection of both SMBH masses.
+Under such conditions, we found configurations that allowed a detection of both SMBH masses.
 The constraints on SMBH masses in such observations arise from the distortions in the resolved \emph{shape} of the central images.
@@
 
-To estimate the probability of configurations which allow detection of binary SMBHs, we simulated many realizations of the positions of the SMBHs for a high resolution (50 mas) 50-h long observation. 
+To estimate the probability of configurations which allow detection of binary SMBHs, we simulated many realizations of the positions of the SMBHs for a high resolution (50 mas) 40-h long observation. 
 We found that $\sim10\%$ of the simulations, in which the core size was larger than 200 pc, both SMBHs were detected. 
 This number is much larger than what is calculated in \citet{Li:12}, since they estimated  the probabilities for point sources, appropriate for lensed quasar samples.
-The extended structure of the background source can significantly increase the probability of
+The extended structure of the background sources studied here can significantly increase the probability of overlapping the black hole caustics, increasing the lensing cross-section by SMBHs.
 

### 2014-11-05 ms.tex
modifying everything

@@
 \caption{ Parameter covariance matrices for two simulations (after marginalization over nuisance parameters).
-Top panel shows that when the core size is small the mass of the SMBH is not measured and only an upper limit can be placed on it.
-The bottom panel, shows that for larger core sizes, the mass of the SMBH could be measured by high significance.
+Black curves show that when the core size is small, the mass of the SMBH is not measured with high precision and only an upper limit can be placed on it.
+The bottom panel, shows that for larger core sizes, the mass of the SMBH could be measured with high significance.
 \label{fig:4}}

### 2014-11-05 ms.tex
modifying everything

@@
 The solid blue curve in Figure \ref{fig:3} shows increase in the flux of the demagnified image for a larger source (with a radius of 1 kpc).
-In contrast, the flux of a source with a radius of 250 pc is severely supressed, largely by the central SMBH (dotted grey curve).
-As such, it is important to consider that various
+In contrast, the flux of a source with a radius of 250 pc can be severely supressed (dotted grey curve).
+As such, more extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, are the most ideal targets for such observations.
 
@@
 Figure \ref{fig:5} shows an example of such configuration when $\gamma = 0.9$ and $R_{\mathrm{core}}=300$ pc.
-Left panel shows the central image without the effects of SMBHs and the right panel shows its morphology in presence of two SMBHs.
+Left panel shows the central image without the simulated central image, with the positions of SMBHs marked with red crosses.
+The distortion in the central image by the SMBHs is clearly visible.
+The right panel shows the same image after convolution with ALMA beam.
 

### 2014-11-06 ms.tex
modifying everything
adding fig 5
PJM acknowldgements

@@
 
-\section{Conclusion}
+\section{Conclusions}
 We have examined the prospects of detecting central, demagnified images of strongly lensed molecular lines with ALMA.
@@
 \acknowledgements{
-\red{Acknowledge NSF?}}
+We thank Risa Wechsler and Matt Becker for interesting discussions.
+\red{YH acknowledges support from the NSF ...}
+The work of PJM was supported in part by the U.S.
+Department of Energy under contract number DE-AC02-76SF00515.
+}
 

### 2014-11-07 ms.tex
modifications

@@
 Strong gravitational lensing is a powerful tool for probing the matter distribution in distant galaxies.
-Among other things, strong lenses have been used to constrain galaxy masses  \citep[e.g.][]{}, density profiles \citep[e.g.][]{}, and abundance of dark matter subhalos \citep[e.g.][]{}.
+Among other things, strong lenses have been used to constrain galaxy masses, density profiles, and abundance of dark matter subhalos \citep[e.g.][]{dalal:02, Gavazzi:07, Bolton:08}.
 The strong lensing theory indicates that the number of lensed images should always be odd.
@@
 Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.
-It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep singular density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter.
+It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
 %Lack of detection of central images in almost all lenses suggests steep central density profiles in lens galaxies.
@@
 \centering
-\includegraphics[trim= 10 0 0 0, clip, width=0.5\textwidth]{figures/f_02.eps}
+\includegraphics[trim= 10 0 0 0, clip, width=0.5\textwidth]{f_02.eps}
 \centering
@@
 \label{fig1}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 5 6, clip, width=0.48\textwidth]{f_01.eps}
+\centering
+\end{center}
+\vspace{-1mm}
+\caption{ Model density profiles.
+The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
+the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese et al.
+(2006).
+The red solid curve shows our cored-power-law model that we use to approximate this stellar component.
+The solid black line shows the total matter density (dark plus stellar) of our model.
+\label{fig2}}
+\vspace{-1.5mm}
 \end{figure}
@@
 The stellar and dark mass of the lens were normalized such that they each contain $1.5\times10^{11} M_{\odot}$ in a radius of 10 kpc.
-The resulting Einstein radius is of order 1 arcsec, in agreement with galaxy-galaxy strong lenses \citep[e.g.,][]{}.
+The resulting Einstein radius is of order 1 arcsec, in agreement with galaxy-galaxy strong lenses \citep[e.g.,][]{hezaveh:13b}.
 %lens mass was set to XX $M_{\odot}$ resulting in an Einstein radius of $\sim XX''$, in agreement with galaxy-galaxy strong lenses.
 We divide this mass equally (in a radius of 10 kpc) between stellar and dark matter.
-To predict the visibilities we calculated the ALMA $uv$-coverage of a 10-$hr$ long observation (full array), using the $simobserve$ task of Common Astronomy Software Applications package, for an observing frequency of 150 GHz.
+To predict the visibilities, we calculated the ALMA $uv$-coverage of a 10-$hr$ long observation (full array), using the $simobserve$ task of Common Astronomy Software Applications package, for an observing frequency of 150 GHz.
 The model visibilities were calculated by computing the 2D Fourier transform of the surface brightness data maps and resampling the Fourier transform maps over the $uv$-coverage. 
@@
 source position, lens ellipticity) to calculate the marginalized likelihood of the relevant parameters.
-
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 0 0 5 6, clip, width=0.5\textwidth]{figures/f_01.eps}
-\centering
-\end{center}
-\caption{ Model density profiles.
-The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions.
-the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006.
-The red solid curve shows our cored-power-law model that we use to approximate this stellar component.
-The solid black line shows the total matter density (dark plus stellar) of our model.
-\label{fig2}}
-\end{figure}
 
@@
 
-\newpage
+%\newpage
 
@@
 \centering
-\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{figures/f_03.eps}
+\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{f_03.eps}
 \centering
@@
 This degeneracy,  however,  is reduced when the core size is very large: large cores produce more extended central images that are spatially resolved.
-The distortion caused by a SMBH can distort this image on smaller scales, resulting in a distinct dip in its surface brightness.
+The distortion caused by a SMBH can distort this image on smaller scales, resulting in a distinct \emph{dip} in its surface brightness.
 %, which breaks the degeneracy of the SMBH with the core size (for point sources this will be observed as the plotting of the central image by the SMBH).
 %Rusin  Keeton Winn 2005
-We find that for cores with a radius larger than $200$ pc, central SMBH masses can be measured with high significance (e.g., bottom panel of Figure \ref{fig:4}), but for smaller core sizes, only upper limits can be placed on the mass of SMBHs.
+We find that for cores with a radius larger than $200$ pc, central SMBH masses can be measured with high significance (e.g., red contours in Figure \ref{fig:4}), but for smaller core sizes, only upper limits can be placed on the mass of SMBHs.
 We also find that when the core size is larger, the constraints on the density profile slope are stronger.
@@
 \centering
-\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{figures/f_04.eps}
+\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{f_04.eps}
 \centering
@@
 Such images also have larger fluxes, increasing the signal to noise of the observations and they also allow for the detection of fairly separated SMBHs.
-In this case the SMBHs can affect different parts of the central image, reducing the degeneracy between their masses.
+In this case, the SMBHs can affect different parts of the central image, reducing the degeneracy between their masses.
 Under such conditions, we found configurations that allowed a detection of both SMBH masses.
@@
 The right panel shows the same image after convolution with ALMA beam.
+Both SMBHs are detected at $\sim5\sigma$.
 
@@
 \centering
-\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{figures/f_05.eps}
+\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{f_05.eps}
 \centering
@@
 We thank Risa Wechsler and Matt Becker for interesting discussions.
-\red{YH acknowledges support from the NSF ...}
+YH acknowledges support from the NSF grant 0807458.
 The work of PJM was supported in part by the U.S.
@@
 
-%\input{ms.bbl}
-
 \end{document}

### 2014-11-10 ms.tex
implemented rogers comments

@@
 We examine the prospects of detecting demagnified images of gravitational lenses in observations of strongly lensed mm-wave molecular emission lines with ALMA.
-We model the lensing galaxies as a superposition of a dark matter component, a stellar component, and a central supermassive black hole and forecast the detection of the central images for a range of relevant parameters (e.g.
+We model the lensing galaxies as a superposition of a dark matter component, a stellar component, and a central supermassive black hole and assess the detectability of the central images for a range of relevant parameters (e.g.
 stellar core and black hole mass).
-We find that over a large range of plausible parameters, future deep observations of lensed molecular lines with ALMA should be able to detect the central images at $\gtrsim 3\sigma$ significance.
+We find that over a large range of plausible parameters, future deep observations of lensed molecular lines with ALMA should enable  detection of the central images at $\gtrsim 3\sigma$ significance.
 We use a Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios and find that for large stellar cores, both the core size and the mass of the central SMBHs can be accurately measured.
-We also study the prospects of detecting binary SMBHs with such observations and find that only under rare conditions and with very long integrations ($\sim$40-hr) the massed of both SMBHs may be measured using the distortions of central images.
+We also study the prospects for detecting binary SMBHs with such observations and find that only under rare conditions and with very long integrations ($\sim$40-hr) the masses of both SMBHs may be measured using the distortions of central images.
 
@@
 %\begin{framed}
-Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super massive black holes (SMBH), galaxy formation, and dark matter.
+Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super-massive black holes (SMBH), galaxy formation, and dark matter.
 It is now established that almost every massive galaxy harbors a SMBH at its center with a mass that strongly correlates with the mass of the host galaxy \citep{Kormendy:95,Ferrarese:00,Gebhardt:00,Tremaine:02}.
-In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions \citep[e.g.,][]{Barnes:92,Ebisuzaki:91}.
+In addition, the distribution of stellar populations in central regions of galaxies contains information about their past merger histories and SMBH-stellar population interactions \citep[e.g.,][]{Barnes:92,Ebisuzaki:91,Barnabe:14}.
 Various dark matter models also predict different structures for the central regions of dark matter halos \citep[e.g.,][]{Rocha:13}.
@@
 Studies of local galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep[e.g.,][]{Ferrarese:06}.
-These galaxies are thought to form through gas-poor mergers.
+These galaxies are thought to form through gas-poor or ``dry'' mergers.
 In such mergers, the central structure of the resulting galaxy is dominated by the inner structure of the more concentrated progenitor.
 Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy merger.
-Cores in massive ellipticals, therefore, may be the result of a different (not merger) process.
-``Black hole scouring'' is a plausible mechanism that can explain core-formation in these galaxies \citep{Thomas:14}.
+Cores in massive ellipticals, therefore, may be the result of a different process, such as
+``black hole scouring'' \citep{Thomas:14}.
 %\end{framed}
@@
 The two orbiting SMBHs then dissipate angular momentum through three-body interactions with nearby central stars, pushing the stars to higher orbits and ``scouring out'' a core.
-This angular momentum loss then allows the two black holes to merge \citep{Begelman:80}.
+This angular momentum loss may then allow the two black holes to merge \citep{Begelman:80}.
 Previous studies have shown that the core sizes in these galaxies scale with the mass of their SMBHs, in agreement with theoretical predictions \citep{Kormendy:09,Kormendy:13}.
-Such measurements, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high physical resolutions.
+It should be emphasized that these black holes are expected to be present and may have larger masses than in comparable nearby galaxies \citep{Bennert:10}.
+Direct measurements, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high physical resolutions.
 % ... whatever the mechanisms are, clear measurements of the central densities can be valuable to solve this puzzle and to shed light on the connection of SMBHs and galaxies. 
@@
 Among other things, strong lenses have been used to constrain galaxy masses, density profiles, and abundance of dark matter subhalos \citep[e.g.][]{dalal:02, Gavazzi:07, Bolton:08}.
-The strong lensing theory indicates that the number of lensed images should always be odd.
-For double and quad image configurations, a third and a fifth image are predicted to exist near the centers of lensing galaxies.
-Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.
+For double and quad image configurations, the theory of strong lensing predicts a third and a fifth image near the centers of lensing galaxies.
+Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making its detection difficult \citep[e.g.,][]{Jackson:13}.
 It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
@@
 In particular, ALMA observations of these sources have revealed that the background galaxies are dusty, starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
-These observations showed that the extreme brightness of the sources, in combination with the high sensitivity of ALMA, result in very high signal to noise observations \citep[e.g., the lens models in][were based on just $\sim50$ second long observations]{hezaveh:13b}.
+These observations showed that the extreme brightness of the sources, in combination with the high sensitivity of ALMA, result in very high signal to noise observations\footnote{For example, the lens models in \citet{hezaveh:13b} were based on just $\sim50$ second long observations.}.
 Motivated by the discovery of this population and the operation of ALMA, here we revisit the issue of detecting central images.
@@
 In addition, since these lines are in mm-wave, the line fluxes are very unlikely to be suppressed by absorption in the lens.
-In contrast to lensed quasars, these sources are extended over hundreds of parsecs and can cover a larger area of the source plane.
+In contrast to lensed quasars, the sources are extended over hundreds of parsecs and suffer a range of demagnifications.
  This can allow them to overlap with the less demagnified regions of the source plane, further increasing the flux of the central images \citep[analogous to magnification damping of highly magnified images due to finite source effects, see e.g.,][]{hezaveh:11}.
@@
 \centering
-\includegraphics[trim= 10 0 0 0, clip, width=0.5\textwidth]{f_02.eps}
+\includegraphics[trim= 10 0 0 0, clip, width=0.48\textwidth]{f_02.eps}
 \centering
@@
 
-We modeled the lens potential as a sum of three components: dark matter, stellar population and a central SMBH.
+We modeled the lens potential as a sum of three components: dark matter, stellar population and a single central SMBH.
 The dark matter component was modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile in the innermost regions \citep{Golse:02}.
-As  pointed out by \citet{Keeton:03}, due to its extreme flatness in these regimes, the dark matter component has negligible influence on the central images.
+As  pointed out by \citet{Keeton:03}, due to its expected flatness in these regimes, the dark matter component has negligible influence on the central images \red{(although models with dark matter cusps have been entertained)}.
 The stellar population is modeled as a a cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma}$.
@@
 Although the cored power-law model used in this work does not account for the slope of the stellar distribution below the core break, it is a close fit and a reasonable model to approximate the observed stellar light profiles in the inner few kpc.
-The black hole was modeled as a simple point mass at the center of the potential. We assumed that all the three components are concentric.
+The black hole was modeled as a simple point mass at the center of the potential.
+We assumed that all the three components are concentric, \red{though we note that two- and three-black hole interactions may may invalidate this assumption.}
 The stellar and dark mass of the lens were normalized such that they each contain $1.5\times10^{11} M_{\odot}$ in a radius of 10 kpc.
@@
 %In this section, we estimate the detection significance of central lensed images of molecular lines with ALMA. 
-The fluxes of central images strongly depend on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
+The fluxes of central images depend principally on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
 Figure \ref{fig:3} shows the detection significance of a central image for a range of these parameters in a 10-h long ALMA observation.
@@
 In contrast, the flux of a source with a radius of 250 pc can be severely supressed (dotted grey curve).
-As such, more extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, are the most ideal targets for such observations.
+As the source galaxies are undergoing prodigious star formation, these large source sizes are reasonable and in agreement with observations \cite{hezaveh:13b}.
+More extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, are therefore the most ideal targets for such observations.% \red{which lines are optimal as a function of zs?}
+
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{f_04.eps}
+\centering
+\end{center}
+\caption{ Parameter covariance matrices for two simulations (after marginalization over nuisance parameters).
+Black curves show that when the core size is small, the mass of the SMBH is not measured with high precision and only an upper limit can be placed on it.
+The bottom panel, shows that for larger core sizes, the mass of the SMBH could be measured with high significance.
+\label{fig:4}}
+\end{figure}
 
@@
 \centering
-\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{f_04.eps}
+\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{f_05.eps}
 \centering
 \end{center}
-\caption{ Parameter covariance matrices for two simulations (after marginalization over nuisance parameters).
-Black curves show that when the core size is small, the mass of the SMBH is not measured with high precision and only an upper limit can be placed on it.
-The bottom panel, shows that for larger core sizes, the mass of the SMBH could be measured with high significance.
-\label{fig:4}}
+\caption{ Lensing of a central image by two SMBHs with masses of $4\times 10^8M_{\odot}$.
+The left panel shows the simulated central image.
+The red crosses show the positions of the SMBHs.
+The white circle has a radius of 1 kpc  from the center of the galaxy.
+The right panel shows the same data after convolution with the ALMA beam.
+The beam is shown in the lower panel.
+\label{fig:5}}
 \end{figure}
@@
 We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on lensed central images. 
+\red{In principle, several black holes could be held up in ??? orbits in these young massive galaxies.}
 We placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in random positions inside a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
@@
 We conclude that, only under rare conditions, and with very long observations ($>40$ hours), central image may allow us to probe binary SMBHs.
-The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses.
+The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses and the dynamical evolution of the black holes.
 
@@
 %Since the suitability for such measurements will depend on the core size and slope of the stellar light, future high resolution observations with thirty meter telescopes, may help select systems with the right range of morphological parameters, to be followed up.
-
-\begin{figure}
-\begin{center}
-\centering
-\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{f_05.eps}
-\centering
-\end{center}
-\caption{ Lensing of a central image by two SMBHs with masses of $4\times 10^8M_{\odot}$.
-The left panel shows the simulated central image.
-The red crosses show the positions of the SMBHs.
-The white circle has a radius of 1 kpc  from the center of the galaxy.
-The right panel shows the same data after convolution with the ALMA beam.
-The beam is shown in the lower panel.
-\label{fig:5}}
-\end{figure}
 
@@
 We also studied the possibility of detecting binary SMBHs and found that only under very rare conditions central images may allow detection of both SMBHs.
+Successful execution of such programs could teach us much about evolution of galactic nuclei.
 

### 2014-11-10 ms.tex
implemented rogers comments

@@
 As the source galaxies are undergoing prodigious star formation, these large source sizes are reasonable and in agreement with observations \cite{hezaveh:13b}.
-More extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, are therefore the most ideal targets for such observations.% \red{which lines are optimal as a function of zs?}
+More extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, are therefore the most ideal targets for such observations.
 

### 2015-01-01 ms.tex
cleaning up the tex file

@@
 We examine the prospects of detecting demagnified images of gravitational lenses in observations of strongly lensed mm-wave molecular emission lines with ALMA.
-We model the lensing galaxies as a superposition of a dark matter component, a stellar component, and a central supermassive black hole and assess the detectability of the central images for a range of relevant parameters (e.g.
-stellar core and black hole mass).
+We model the lensing galaxies as a superposition of a dark matter component, a stellar component, and a central supermassive black hole and assess the detectability of the central images for a range of relevant parameters (e.g., stellar core and black hole mass).
 We find that over a large range of plausible parameters, future deep observations of lensed molecular lines with ALMA should enable  detection of the central images at $\gtrsim 3\sigma$ significance.
@@
 
-%in Ferarrese 2006, $r_b$ varies from ~50 to 500 pc.
-
 \keywords{ black hole physics ---
@@
 \section{introduction}
-%\begin{framed}
 Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super-massive black holes (SMBH), galaxy formation, and dark matter.
@@
 Mapping the matter density in the central regions of galaxies can thus shed light on various astrophysical phenomena.
-%probing the inner 0.5 kpc of galaxies is interesting.
-1) they contain SMBHs and the relationship of the SMBH mass to galaxies is intriguing and interesting.
-Dark matter models also have different and interesting predictions for the density of the central regions of galaxies (e.g.
-cored DM, or SIDM predictions).
-In addition, the history of galaxy mergers and black hole-stellar population interactions can be encoded in the stellar light profiles, resulting in different stellar
-%\end{framed}
 
-%\begin{framed}
-%Stellar light profiles:
-%\\ \\
-Studies of local galaxies in optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep[e.g.,][]{Ferrarese:06}.
+Studies of local galaxies at optical wavelengths have shown that, unlike their lower-mass counterparts, the most massive elliptical galaxies often exhibit cored stellar light profiles, with core sizes ranging from 50 to 500 pc \citep[e.g.,][]{Ferrarese:06}.
 These galaxies are thought to form through gas-poor or ``dry'' mergers.
 In such mergers, the central structure of the resulting galaxy is dominated by the inner structure of the more concentrated progenitor.
-Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy merger.
+Since high-mass ellipticals are thought to form from mergers of their lower-mass counterparts, with steep profiles, the existence of cores in these galaxies represents a challenge to our understanding of galaxy evolution.
 Cores in massive ellipticals, therefore, may be the result of a different process, such as
 ``black hole scouring'' \citep{Thomas:14}.
-%\end{framed}
 
-%\begin{framed}
 It is thought that during a merger, the SMBHs of the two merging galaxies form a binary, which sinks to the center of the potential.
@@
 Direct measurements, however have been limited to low redshifts, since both dynamical measurements to constrain the stellar and SMBH masses, and morphological measurements to constrain core sizes require very high physical resolutions.
-% ... whatever the mechanisms are, clear measurements of the central densities can be valuable to solve this puzzle and to shed light on the connection of SMBHs and galaxies. 
-%\end{framed}
 
-%\begin{framed}
 Strong gravitational lensing is a powerful tool for probing the matter distribution in distant galaxies.
-Among other things, strong lenses have been used to constrain galaxy masses, density profiles, and abundance of dark matter subhalos \citep[e.g.][]{dalal:02, Gavazzi:07, Bolton:08}.
+Among other things, strong lenses have been used to constrain galaxy masses, density profiles, and abundance of dark matter subhalos \citep[e.g.,][]{dalal:02, Gavazzi:07, Bolton:08}.
 For double and quad image configurations, the theory of strong lensing predicts a third and a fifth image near the centers of lensing galaxies.
@@
 It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
-%Lack of detection of central images in almost all lenses suggests steep central density profiles in lens galaxies.
 
@@
 Distinguishing the central images from emission originating in the lens galaxies is extremely challenging.
-Moreover, if observed in the optical, absorption in the central dense regions of the lens can make the central images even dimmer, while the photon noise from the lens emission further reduces the sensitivity.
+If observed in the optical, absorption in the central dense regions of the lens can make the central images even dimmer, while the photon noise from the lens emission further reduces the sensitivity.
 
-%5) Additionally, another reason for lack of detection is that the central image is located at the center of the lensing galaxy, where i) the sensitivity is lower, due to photon noise of the lens ii) it is difficult to distinguish the flux of the central image from the emission from the lens.
-iii) if in optical, since they pass through the centers of galaxies there's a high chance of large absorption (in the lens)
-
-%Such central images, however, have been very rarely detected, suggesting that steep density profiles of galaxies render them 
-%4) typically only an even number of images are observed,  suggesting that the central images are demagnified below the sensitivity of instruments. \\ \\
-
-%\end{framed}
-
-The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.][]{Wallington:93, Evans:02, Keeton:03}.
+The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.,][]{Wallington:93, Evans:02, Keeton:03}.
 These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}.
 Observational searches for these images have found a number of candidates. Although observations
-of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:08}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.
-To avoid the possibility of absorption in the lens, most searches have focused on lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies \citep[e.g.,][]{Zhang:07}.
+of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:08}, only one secure detection of a central image of a galaxy-scale lens exists to date \citep{Winn:04}.
+To avoid the possibility of absorption in the lens, most searches have focused on lensed radio sources.
+The radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies \citep[e.g.,][]{Zhang:07}.
 
-%To avoid confusion between a central image and faint radio emission from the lens galaxies
-
-%a review of central image observations and studies:\\ \\
-%1) The individual and statistical properties of central images have been previously studied. (e.g. Wallington 1993, Evans \& Hunter 2002, Keeton 2003, ) \\ \\
-%2) to avoid absorption by, and lack of contamination from the main lens, past studies focused on radio lens quasars. \\ \\
-%3) for example, Rusin \&  Ma 2001 set constrains on the inner profiles of lens galaxies form observations of six two-image radio-loud lens systems \\ \\
-%4) confusion between a central image, and faint radio emission from the lens galaxy, could be avoided by studying the radio spectrum of a candidate central image.   
-%5) the only secure detection of a central image (based on its radio spectrum)  in a galaxy-mass lensing system, is PMNJ 1632?0033 (Winn et al. 2002, 2003, 2004),   \\ \\
-%6) Winn et al 2004 used the detection of this central image to place constraints on the mass of the central SMBH.
-%\end{framed}
-
-%\begin{framed}
-A new large population of strong lenses has recently been discovered in mm-bands.
+A new large population of strong lenses has recently been discovered in mm-wave.
 These systems were initially detected as bright point sources in wide area mm/submm surveys \citep{vieira:10,negrello:10}.
 Follow-up observations have confirmed that they constitute a large population of strong lenses \citep{vieira:13, hezaveh:13b, bussmann:13}.
-In particular, ALMA observations of these sources have revealed that the background galaxies are dusty, starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
+In particular, high resolution ALMA followup observations of these sources have revealed that the background galaxies are dusty, starburst, high redshift galaxies, containing a wealth of cold molecular gas \citep{Weiss:13}.
 These observations showed that the extreme brightness of the sources, in combination with the high sensitivity of ALMA, result in very high signal to noise observations\footnote{For example, the lens models in \citet{hezaveh:13b} were based on just $\sim50$ second long observations.}.
@@
 In addition, since these lines are in mm-wave, the line fluxes are very unlikely to be suppressed by absorption in the lens.
-In contrast to lensed quasars, the sources are extended over hundreds of parsecs and suffer a range of demagnifications.
- This can allow them to overlap with the less demagnified regions of the source plane, further increasing the flux of the central images \citep[analogous to magnification damping of highly magnified images due to finite source effects, see e.g.,][]{hezaveh:11}.
+In contrast to lensed quasars, the sources are extended over hundreds of parsecs and suffer a range of demagnifications, further increasing the flux of the central images \citep[analogous to magnification damping of highly magnified images due to finite source effects, see e.g.,][]{hezaveh:11}.
 
@@
 
-% the distribution of matter in the innermost regions of galaxies from detection or non-detection of such central images.\\ \\
-%3) the paper is organized as: section 2 describes the simulations, section 3 presents the results and discuss them and conclude in section 5 \\ \\
-%4) we use $\Lambda$CDM cosmology of XXX
-
-%\begin{framed}
-%motivation and description of the paper: \\ \\
-%1) Long ALMA observations of these molecular lines are likely to be carried out for various reasons (e.g. power spectrum of dark matter, measuring the mass of background black holes) .  \\ \\
-%2) In this paper we explore the possibility of detection of these central images in such deep observations, and investigate what we could learn about the innermost regions of galaxies from detection or non-detection of such central images.\\ \\
-%3) the paper is organized as: section 2 describes the simulations, section 3 presents the results and discuss them and conclude in section 5 \\ \\
-%4) we use $\Lambda$CDM cosmology of XXX
-%\end{framed}
-
 \begin{figure}
@@
 \centering
-\includegraphics[trim= 10 0 0 0, clip, width=0.48\textwidth]{f_02.eps}
+\includegraphics[trim= 10 0 0 0, clip, width=0.48\textwidth]{figures/f_02.eps}
 \centering
@@
 \centering
-\includegraphics[trim= 0 0 5 6, clip, width=0.48\textwidth]{f_01.eps}
+\includegraphics[trim= 0 0 5 6, clip, width=0.48\textwidth]{figures/f_01.eps}
 \centering
@@
 We simulated observations of a high-$J$ CO line.
-The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band, a typical value for high redshift dusty galaxies \citep{Bothwell:12}.
+The line is assumed to have a velocity integrated flux of 1 Jy km/s and a FWHM of 400 km/s, resulting in an average flux of 2.5 mJy over a 400 km/s band, a typical value for high redshift, dusty galaxies \citep{Bothwell:12}.
 
@@
 The dark matter component was modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile in the innermost regions \citep{Golse:02}.
-As  pointed out by \citet{Keeton:03}, due to its expected flatness in these regimes, the dark matter component has negligible influence on the central images \red{(although models with dark matter cusps have been entertained)}.
-The stellar population is modeled as a a cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma}$.
+As  pointed out by \citet{Keeton:03}, due to its expected flatness in these regimes, the dark matter component has negligible influence on the central images (although models with dark matter cusps have been entertained).
+The stellar population is modeled as a a cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma_s}$.
 Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curve).
@@
 The black hole was modeled as a simple point mass at the center of the potential.
-We assumed that all the three components are concentric, \red{though we note that two- and three-black hole interactions may may invalidate this assumption.}
+We assumed that all the three components are concentric, though we note that two- and three-black hole interactions may invalidate this assumption.
 The stellar and dark mass of the lens were normalized such that they each contain $1.5\times10^{11} M_{\odot}$ in a radius of 10 kpc.
 The resulting Einstein radius is of order 1 arcsec, in agreement with galaxy-galaxy strong lenses \citep[e.g.,][]{hezaveh:13b}.
-%lens mass was set to XX $M_{\odot}$ resulting in an Einstein radius of $\sim XX''$, in agreement with galaxy-galaxy strong lenses.
-We divide this mass equally (in a radius of 10 kpc) between stellar and dark matter.
 To predict the visibilities, we calculated the ALMA $uv$-coverage of a 10-$hr$ long observation (full array), using the $simobserve$ task of Common Astronomy Software Applications package, for an observing frequency of 150 GHz.
@@
 
-For simulations where we calculated the detection significance of the demagnified image, we computed the magnification at every pixel in the image plane and generated maps with and without the the demagnified flux and evaluated the detection significance of the central image by comparing the two images.
-In other simulations, where the constrains on parameters are needed, we used a Fisher analysis to compute the full covariance of all parameters.
-We used finite differencing of visibilities to calculate the gradients, and marginalize over the nuisance parameters (e.g.
-source position, lens ellipticity) to calculate the marginalized likelihood of the relevant parameters.
-
-%\begin{framed} description
-
-%The gas in the source galaxy is modeled as a collection of 5 Gaussian clumps with FWHM of XX, distributed over XX kpc and each separated in a different channel.
-%and an intrinsic velocity dispersion  of 10 $km/s$ (FWHM) similar to observations of \citet{Davis:13}. 
-%The choice of two discrete rings is made to enforce resolving the inner 50 pc region for a black hole mass measurement.
-We point out, however, that assuming a more general case (e.g.
-an exponential disk) does not change the results \citep[see Figure 2 of ][]{Davis:2014}.
-%The velocity integrated flux of the circumnuclear ring is set to 4 $mJy\, km/s$. 
-%This value is calculated by scaling the flux of the circumnuclear CO gas in Arp 220 to to z=2 \citep{Sakamoto:99}.
-%The rings are concentric and in circular orbits.
-The rotational velocity of each point in the rings is calculated based on the enclosed mass contributed from the galaxy mass model and the mass of the central black hole.
-The black hole is given a mass of $M_{\mathrm{BH}}=5\times 10^{8} M_{\odot}$.
-%We model the galaxy density with an isothermal profile ($\rho\propto r^{-2}$) with a central velocity dispersion of 200 km/s. 
-%The line-of-sight velocities are calculated to generate a frequency-position data cube.
-Figure \ref{f:f1} shows a velocity-position diagram extracted from the data cube.
-The data comprises 100 frequency channels covering 800 km/s.
-
-%Each layer of the data cube is lensed with the foreground halo to  generate a lensed cube.
-We use a Singular Isothermal Ellipsoid (SIE) mass model for the lens galaxy \citep[$\rho\propto r^{-2}$,][]{Kormann:94}, placed at $z_l=0.5$ and place the source at $z_s=2.0$.
-The central velocity dispersion of the lens is set to 180 $km/s$, which is typical for galaxy-galaxy lensing systems \citep[e.g.][]{hezaveh:13b}.
-
-%\end{framed}
-
-%\newpage
+For simulations where we calculated the detection significance of the demagnified image, we computed the magnification at every pixel in the image plane and generated maps with and without the the demagnified flux and evaluated the detection significance of the central image by comparing the two resulting visibility sets.
+In other simulations, where the constrains on parameters were needed, we used a Fisher analysis to compute the full covariance of all parameters.
+We used finite differencing of visibilities to calculate the gradients, and marginalize over the nuisance parameters (e.g., source position, lens ellipticity), assuming uniform priors, to calculate the posterior of the relevant parameters.
 
@@
 \centering
-\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{f_03.eps}
+\includegraphics[trim= 0 0 0 0, clip,width=0.48\textwidth]{figures/f_03.eps}
 \centering
@@
 The solid blue and gray dotted curves show the detections for a source with a radius of 1 kpc and 250 pc respectively.
-%The gray shades correspond to different slopes for the stellar component.
-The solid curves correspond to a case without a SMBH while the dashed curves show the results when a $2\times10^8M_{\odot}$ SMBH is placed at the center of the lens.
-%The source has a Gaussian light profile with an rms of 600 pc. The red curves show the same predictions when $\gamma=1$, for a source with rms of 300 pc.
 \label{fig:3}}
@@
 \subsection{Detection of central images with ALMA}
-%In this section, we estimate the detection significance of central lensed images of molecular lines with ALMA. 
 The fluxes of central images depend principally on the slope of the lensing potential, the core size, and the mass of the central SMBHs.
-Figure \ref{fig:3} shows the detection significance of a central image for a range of these parameters in a 10-h long ALMA observation.
+Figure \ref{fig:3} shows the detection significance of a central image for a range of these parameters in a 10-hr long ALMA observation.
 The figure shows the detection significance of the demagnified central flux, as a function of the stellar core size.
@@
 
-As seen in this figure, larger stellar cores result in brighter images. %Lensing studies have shown that the total profiles of galaxies are very close to isothermal \red{cite{}}. 
-In the absence of a massive black hole, when $\gamma=1.0$ and with a core size larger than 150 pc, such observations should be able to detect the central images with more than $5\sigma$ significance.
-For significantly shallower ($\gamma<0.8$) profiles and larger cores, the central image is \emph{magnified} and its detection should be trivial.
+As seen in this figure, larger stellar cores result in brighter images. 
+In the absence of a massive black hole, when $\gamma_s=1.0$ and with a core size larger than 150 pc, such observations should be able to detect the central images with more than $5\sigma$ significance.
+For significantly shallower ($\gamma_s<0.8$) profiles and larger cores, the central image is \emph{magnified} and its detection should be trivial.
 The magnification and flux of central images is also influenced by SMBHs.
@@
 As seen in Figure \ref{fig:3}, and as pointed out by \citet{Keeton:03}, plausible parameters predict  a wide range of magnifications for   central images.
-Although for some parameter combinations (e.g., $\gamma_{s}=1.1,$ $M_{BH} = 2\times10^8 M_{\odot}$,$R_{core}<200 pc$ ) there is little chance of detecting the central images, over a non-negligable fraction of parameter space the central images may be detectable.
+Although for some parameter combinations (e.g., $\gamma_{s}=1.1,$ $M_{\mathrm{BH}} = 2\times10^8 M_{\odot}$,$R_{\mathrm{core}}<200$ pc ) there is little chance of detecting the central images, they may be detectable over a non-negligible fraction of the parameter space.
 
-We also find that the detection significance of the central images can significantly increase for an extended source with a radius of 1 kpc compared to a point source.
+We also find that the detection significance of the central images can significantly \emph{increase} for an extended source with a radius of 1 kpc compared to a point source.
 Since extended sources occupy a larger area of the source plane, which may cover regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
-The solid blue curve in Figure \ref{fig:3} shows increase in the flux of the demagnified image for a larger source (with a radius of 1 kpc).
+The solid blue curve in Figure \ref{fig:3} shows the increase in the flux of the demagnified image for a larger source (with a radius of 1 kpc).
 In contrast, the flux of a source with a radius of 250 pc can be severely supressed (dotted grey curve).
-As the source galaxies are undergoing prodigious star formation, these large source sizes are reasonable and in agreement with observations \cite{hezaveh:13b}.
-More extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, are therefore the most ideal targets for such observations.
+As the source galaxies are undergoing prodigious star formation, these large source sizes are reasonable and in agreement with observations \citep{hezaveh:13b}.
+More extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, may therefore be the most ideal targets for such observations.
 
@@
 \centering
-\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{f_04.eps}
+\includegraphics[trim= 2 5 0 0, clip, width=0.48\textwidth]{figures/f_04.eps}
 \centering
@@
 
-%\begin{framed}
-%1) We evaluate the detection significance of central images over a range of relevant parameters. \\ \\
-%2) Figure 4 shows our results for a 10-hr long observation with ALMA\\ \\
-%3) we show that, as expected, the image is fainter for steeper profile slopes. \\ \\
-%4) the 0.9 value (combined with 0.1 DM) results in the isothermal profile, which has been shown to be consistent with strong lensing data \\ \\
-%5) if that's the case, and in the absence of massive BHs, then stellar cores as small as $\sim80$ pc should allow a 5$\sigma$ detection of the central images. \\ \\
-%5A) we note that for much shallower density profiles, the central image is actually \emph{magnified}, and therefore it's detection should be trivial.\\ \\
-%6) the flux is significantly supressed by the central SMBH \\  \\
-%7) the dashed curves show the same for a galaxy with a $2e8M_{\odot}$ SMBH. \\ \\
-%8) we note that, as pointed out in Keeton 2003, there's a large range of possibilities for plausible lens parameters: although for some parameter combinations (e.g., $\gamma_{s}=1.2,$ $M_{BH} = 2e8$,$R_{core}<300 pc$ ) there is no chance of detecting the central image, over a significant fraction of allowed parameters the central image could be detected.
-\\ \\
-%9) to calculate this plot we have used a configuration XX, because: it allows us to resolve the central image (if existent), while it is more sensitive that more extended configurations.
-In addition, this is the configuration that will be likely used for other projects/sciences.
-%\end{framed}
-
 \subsection{SMBHs and the core size}
 Here, we study the constraints that could be placed on the slope of the density profile, the size of the stellar core, and the mass of the SMBHs in such deep observations. 
-We performed a Fisher analysis to examine the constrains and parameter degeneracies in simulations in which the central images are detected, as well as those in which they are below the detection limit.
+We performed a Fisher analysis to examine the constraints and parameter degeneracies in simulations in which the central images were detected, as well as those in which they were below the detection limit.
 All model parameters were included in the Fisher matrix, and nuisance parameters were later marginalize over (e.g.
-intrinsic source flux and position) to obtain the marginalized likelihood of the relevant parameters.
- Figure \ref{fig:4} shows the parameter covariance for two simulations with different core radii (black contours:  $R_{core}$=170 pc, red contours: $R_{core}$=400 pc).
-% . As seen in Figure \ref{fig:3},  this parameter combination results in a $\sim3\sigma$ detection of the central image. 
-We found that when $\gamma=1$, core sizes larger than 100 pc can be measured with high significance. As seen in Figure \ref{fig:4}, 
+intrinsic source flux and position).
+ Figure \ref{fig:4} shows the parameter covariance for two simulations with different core radii (black contours:  $R_{\mathrm{core}}$=170 pc, red contours: $R_{\mathrm{core}}$=400 pc).
+We found that when $\gamma_s=1$, core sizes larger than 100 pc can be measured with high significance. As seen in Figure \ref{fig:4}, 
 for small cores, the mass of SMBH is highly degenerate with the core size: larger cores result in brighter images, whose flux can be supressed by a more massive SMBH.
 This degeneracy,  however,  is reduced when the core size is very large: large cores produce more extended central images that are spatially resolved.
-The distortion caused by a SMBH can distort this image on smaller scales, resulting in a distinct \emph{dip} in its surface brightness.
-%, which breaks the degeneracy of the SMBH with the core size (for point sources this will be observed as the plotting of the central image by the SMBH).
-%Rusin  Keeton Winn 2005
+The distortion caused by a SMBH can distort this image on smaller scales, resulting in a distinct, resolved \emph{dip} in its surface brightness.
 We find that for cores with a radius larger than $200$ pc, central SMBH masses can be measured with high significance (e.g., red contours in Figure \ref{fig:4}), but for smaller core sizes, only upper limits can be placed on the mass of SMBHs.
 We also find that when the core size is larger, the constraints on the density profile slope are stronger.
-
-%\begin{framed}
-%9) we note that the constraints in this case will be of similar strength to those of Winn 2004. \\ \\ 
-%12) we note that all these parameter combinations are plausible choices, and therefore long observations such as these will be able to either measure these parameters with confidence or place strong constraints on them.
-%\end{framed}
 
@@
 \centering
-\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{f_05.eps}
+\includegraphics[trim= 20 0 20 0, width=0.46\textwidth]{figures/f_05.eps}
 \centering
@@
 We also investigated the possibility of detecting binary SMBHs using the perturbations that they induce on lensed central images. 
-\red{In principle, several black holes could be held up in ??? orbits in these young massive galaxies.}
+In principle, several black holes could be held up in orbits in these young massive galaxies.
 We placed two SMBHs with masses of $4\times10^8 M_{\odot}$ each in random positions inside a circle of radius of 1 kpc from the center of the galaxy and, using the Fisher analysis, computed the detection significance of their masses.
 We found that in most cases, it is not possible to measure the mass of both SMBHs, either because they are not near the central images or due to the degeneracy between their masses, their positions, and the core radius.
-%, or because the distortions in the central images are unresolved.
 However, when the central images are fairly extended (due to a shallow density slope and a large core size), a larger fraction of the inner 1 kpc region is covered by the central image, increasing the probability of lensing by SMBHs.
@@
 The constraints on SMBH masses in such observations arise from the distortions in the resolved \emph{shape} of the central images.
-Figure \ref{fig:5} shows an example of such configuration when $\gamma = 0.9$ and $R_{\mathrm{core}}=300$ pc.
-Left panel shows the central image without the simulated central image, with the positions of SMBHs marked with red crosses.
+Figure \ref{fig:5} shows an example of such configuration when $\gamma_s = 0.9$ and $R_{\mathrm{core}}=300$ pc.
+Left panel shows the central image with the positions of SMBHs marked with red crosses.
 The distortion in the central image by the SMBHs is clearly visible.
@@
 
-%Such distortions, however, can only be marginally resolved with ALMA, and very long integrations may be required
-
-%The positions of the SMBHs are marked with red crosses.
-
-%found cases with a shallow potential and a large stellar core, which result in bright central images, we found certain configurations in which the resolved shape of the central image can allow a detection of the masses of both SMBHs.
-
-To estimate the probability of configurations which allow detection of binary SMBHs, we simulated many realizations of the positions of the SMBHs for a high resolution (50 mas) 40-h long observation. 
+To estimate the probability of configurations which allow detection of binary SMBHs, we simulated many realizations of the positions of the SMBHs for a high resolution 40-h long observation. 
 We found that $\sim10\%$ of the simulations, in which the core size was larger than 200 pc, both SMBHs were detected. 
 This number is much larger than what is calculated in \citet{Li:12}, since they estimated  the probabilities for point sources, appropriate for lensed quasar samples.
-The extended structure of the background sources studied here can significantly increase the probability of overlapping the black hole caustics, increasing the lensing cross-section by SMBHs.
+The extended structure of the background sources studied here can significantly increase the probability of overlapping the black hole caustics, increasing the lensing cross-section of SMBHs.
 
@@
 The prospects of such measurement will ultimately depend on discoveries of much larger samples of lenses and the dynamical evolution of the black holes.
-
-%The magnified images of the lens allow a detailed reconstruction of the background source.
-It is therefore easy to distinguish that the structure in the central image is not due to the structure of the source, but are caused by lensing by binary SMBHs.
-%Since the suitability for such measurements will depend on the core size and slope of the stellar light, future high resolution observations with thirty meter telescopes, may help select systems with the right range of morphological parameters, to be followed up.
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references}
+
+\begin{thebibliography}{36}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Barnab{\`e}} {et~al.}(2014){Barnab{\`e}}, {Spiniello}, \&
+  {Koopmans}}]{Barnabe:14}
+{Barnab{\`e}}, M., {Spiniello}, C., \& {Koopmans}, L.~V.~E. 2014, ArXiv
+  e-prints, 1409.4197
+
+\bibitem[{{Barnes} \& {Hernquist}(1992)}]{Barnes:92}
+{Barnes}, J.~E., \& {Hernquist}, L. 1992, \araa, 30, 705
+
+\bibitem[{{Begelman} {et~al.}(1980){Begelman}, {Blandford}, \&
+  {Rees}}]{Begelman:80}
+{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1980, \nat, 287, 307
+
+\bibitem[{{Bennert} {et~al.}(2010){Bennert}, {Treu}, {Woo}, {Malkan}, {Le
+  Bris}, {Auger}, {Gallagher}, \& {Blandford}}]{Bennert:10}
+{Bennert}, V.~N., {Treu}, T., {Woo}, J.-H., {et~al.} 2010, \apj, 708, 1507,
+  0911.4107
+
+\bibitem[{{Bolton} {et~al.}(2008){Bolton}, {Treu}, {Koopmans}, {Gavazzi},
+  {Moustakas}, {Burles}, {Schlegel}, \& {Wayth}}]{Bolton:08}
+{Bolton}, A.~S., {Treu}, T., {Koopmans}, L.~V.~E., {et~al.} 2008, \apj, 684,
+  248, 0805.1932
+
+\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
+  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
+  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell:12}
+{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
+  3047, 1205.1511
+
+\bibitem[{{Bussmann} {et~al.}(2013){Bussmann}, {P{\'e}rez-Fournon}, {Amber},
+  {Calanog}, {Gurwell}, {Dannerbauer}, {De Bernardis}, {Fu}, {Harris}, {Krips},
+  {Lapi}, {Maiolino}, {Omont}, {Riechers}, {Wardlow}, {Baker}, {Birkinshaw},
+  {Bock}, {Bourne}, {Clements}, {Cooray}, {De Zotti}, {Dunne}, {Dye}, {Eales},
+  {Farrah}, {Gavazzi}, {Gonz{\'a}lez Nuevo}, {Hopwood}, {Ibar}, {Ivison},
+  {Laporte}, {Maddox}, {Mart{\'{\i}}nez-Navajas}, {Michalowski}, {Negrello},
+  {Oliver}, {Roseboom}, {Scott}, {Serjeant}, {Smith}, {Smith}, {Streblyanska},
+  {Valiante}, {van der Werf}, {Verma}, {Vieira}, {Wang}, \&
+  {Wilner}}]{bussmann:13}
+{Bussmann}, R.~S., {P{\'e}rez-Fournon}, I., {Amber}, S., {et~al.} 2013, \apj,
+  779, 25, 1309.0836
+
+\bibitem[{{Dalal} \& {Kochanek}(2002)}]{dalal:02}
+{Dalal}, N., \& {Kochanek}, C.~S. 2002, \apj, 572, 25, astro-ph/0111456
+
+\bibitem[{{Ebisuzaki} {et~al.}(1991){Ebisuzaki}, {Makino}, \&
+  {Okumura}}]{Ebisuzaki:91}
+{Ebisuzaki}, T., {Makino}, J., \& {Okumura}, S.~K. 1991, \nat, 354, 212
+
+\bibitem[{{Evans} \& {Hunter}(2002)}]{Evans:02}
+{Evans}, N.~W., \& {Hunter}, C. 2002, \apj, 575, 68, astro-ph/0204206
+
+\bibitem[{{Ferrarese} \& {Merritt}(2000)}]{Ferrarese:00}
+{Ferrarese}, L., \& {Merritt}, D. 2000, \apjl, 539, L9, astro-ph/0006053
+
+\bibitem[{{Ferrarese} {et~al.}(2006){Ferrarese}, {C{\^o}t{\'e}}, {Jord{\'a}n},
+  {Peng}, {Blakeslee}, {Piatek}, {Mei}, {Merritt}, {Milosavljevi{\'c}},
+  {Tonry}, \& {West}}]{Ferrarese:06}
+{Ferrarese}, L., {C{\^o}t{\'e}}, P., {Jord{\'a}n}, A., {et~al.} 2006, \apjs,
+  164, 334, astro-ph/0602297
+
+\bibitem[{{Gavazzi} {et~al.}(2007){Gavazzi}, {Treu}, {Rhodes}, {Koopmans},
+  {Bolton}, {Burles}, {Massey}, \& {Moustakas}}]{Gavazzi:07}
+{Gavazzi}, R., {Treu}, T., {Rhodes}, J.~D., {et~al.} 2007, \apj, 667, 176,
+  astro-ph/0701589
+
+\bibitem[{{Gebhardt} {et~al.}(2000){Gebhardt}, {Bender}, {Bower}, {Dressler},
+  {Faber}, {Filippenko}, {Green}, {Grillmair}, {Ho}, {Kormendy}, {Lauer},
+  {Magorrian}, {Pinkney}, {Richstone}, \& {Tremaine}}]{Gebhardt:00}
+{Gebhardt}, K., {Bender}, R., {Bower}, G., {et~al.} 2000, \apjl, 539, L13,
+  astro-ph/0006289
+
+\bibitem[{{Golse} \& {Kneib}(2002)}]{Golse:02}
+{Golse}, G., \& {Kneib}, J.-P. 2002, \aap, 390, 821, astro-ph/0112138
+
+\bibitem[{{Hezaveh} {et~al.}(2014){Hezaveh}, {Dalal}, {Holder}, {Kisner}, \&
+  {Kuhlen}}]{hezaveh:14a}
+{Hezaveh}, Y., {Dalal}, N., {Holder}, G., {Kisner}, T., \& {Kuhlen}, M. 2014,
+  ArXiv e-prints, 1403.2720
+
+\bibitem[{{Hezaveh}(2014)}]{hezaveh:14b}
+{Hezaveh}, Y.~D. 2014, \apjl, 791, L41, 1408.3631
+
+\bibitem[{{Hezaveh} \& {Holder}(2011)}]{hezaveh:11}
+{Hezaveh}, Y.~D., \& {Holder}, G.~P. 2011, \apj, 734, 52, 1010.0998
+
+\bibitem[{{Hezaveh} {et~al.}(2013){Hezaveh}, {Marrone}, {Fassnacht}, {Spilker},
+  {Vieira}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss}, {Benson},
+  {Bleem}, {Bothwell}, {Brodwin}, {Carlstrom}, {Chang}, {Chapman}, {Crawford},
+  {Crites}, {De Breuck}, {de Haan}, {Dobbs}, {Fomalont}, {George}, {Gladders},
+  {Gonzalez}, {Greve}, {Halverson}, {High}, {Holder}, {Holzapfel}, {Hoover},
+  {Hrubes}, {Husband}, {Hunter}, {Keisler}, {Lee}, {Leitch}, {Lueker},
+  {Luong-Van}, {Malkan}, {McIntyre}, {McMahon}, {Mehl}, {Menten}, {Meyer},
+  {Mocanu}, {Murphy}, {Natoli}, {Padin}, {Plagge}, {Reichardt}, {Rest}, {Ruel},
+  {Ruhl}, {Sharon}, {Schaffer}, {Shaw}, {Shirokoff}, {Stalder}, {Staniszewski},
+  {Stark}, {Story}, {Vanderlinde}, {Wei{\ss}}, {Welikala}, \&
+  {Williamson}}]{hezaveh:13b}
+{Hezaveh}, Y.~D., {Marrone}, D.~P., {Fassnacht}, C.~D., {et~al.} 2013, \apj,
+  767, 132, 1303.2722
+
+\bibitem[{{Inada} {et~al.}(2008){Inada}, {Oguri}, {Falco}, {Broadhurst},
+  {Ofek}, {Kochanek}, {Sharon}, \& {Smith}}]{Inada:08}
+{Inada}, N., {Oguri}, M., {Falco}, E.~E., {et~al.} 2008, \pasj, 60, L27,
+  0808.1769
+
+\bibitem[{{Jackson}(2013)}]{Jackson:13}
+{Jackson}, N. 2013, Bulletin of the Astronomical Society of India, 41, 19,
+  1304.4172
+
+\bibitem[{{Keeton}(2003)}]{Keeton:03}
+{Keeton}, C.~R. 2003, \apj, 582, 17, astro-ph/0206243
+
+\bibitem[{{Kormendy} \& {Bender}(2009)}]{Kormendy:09}
+{Kormendy}, J., \& {Bender}, R. 2009, \apjl, 691, L142, 0901.3778
+
+\bibitem[{{Kormendy} \& {Ho}(2013)}]{Kormendy:13}
+{Kormendy}, J., \& {Ho}, L.~C. 2013, \araa, 51, 511, 1304.7762
+
+\bibitem[{{Kormendy} \& {Richstone}(1995)}]{Kormendy:95}
+{Kormendy}, J., \& {Richstone}, D. 1995, \araa, 33, 581
+
+\bibitem[{{Li} {et~al.}(2012){Li}, {Mao}, {Gao}, {Loeb}, \& {di
+  Stefano}}]{Li:12}
+{Li}, N., {Mao}, S., {Gao}, L., {Loeb}, A., \& {di Stefano}, R. 2012, \mnras,
+  419, 2424, 1110.0887
+
+\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
+  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
+  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
+  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
+  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
+  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
+  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
+  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
+  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
+  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
+  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
+  {Maloney}, {Matsuhara}, {Michaowski}, {Murphy}, {Naylor}, {Nguyen},
+  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
+  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{negrello:10}
+{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330,
+  800, 1011.1255
+
+\bibitem[{{Rocha} {et~al.}(2013){Rocha}, {Peter}, {Bullock}, {Kaplinghat},
+  {Garrison-Kimmel}, {O{\~n}orbe}, \& {Moustakas}}]{Rocha:13}
+{Rocha}, M., {Peter}, A.~H.~G., {Bullock}, J.~S., {et~al.} 2013, \mnras, 430,
+  81, 1208.3025
+
+\bibitem[{{Thomas} {et~al.}(2014){Thomas}, {Saglia}, {Bender}, {Erwin}, \&
+  {Fabricius}}]{Thomas:14}
+{Thomas}, J., {Saglia}, R.~P., {Bender}, R., {Erwin}, P., \& {Fabricius}, M.
+  2014, \apj, 782, 39, 1311.3783
+
+\bibitem[{{Tremaine} {et~al.}(2002){Tremaine}, {Gebhardt}, {Bender}, {Bower},
+  {Dressler}, {Faber}, {Filippenko}, {Green}, {Grillmair}, {Ho}, {Kormendy},
+  {Lauer}, {Magorrian}, {Pinkney}, \& {Richstone}}]{Tremaine:02}
+{Tremaine}, S., {Gebhardt}, K., {Bender}, R., {et~al.} 2002, \apj, 574, 740,
+  astro-ph/0203468
+
+\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
+  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
+  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
+  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
+  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
+  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
+  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
+  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
+  {Zenteno}}]{vieira:10}
+{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
+  763, 0912.2338
+
+\bibitem[{{Vieira} {et~al.}(2013){Vieira}, {Marrone}, {Chapman}, {De Breuck},
+  {Hezaveh}, {Wei{$\beta$}}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss},
+  {Benson}, {Biggs}, {Bleem}, {Bock}, {Bothwell}, {Bradford}, {Brodwin},
+  {Carlstrom}, {Chang}, {Crawford}, {Crites}, {de Haan}, {Dobbs}, {Fomalont},
+  {Fassnacht}, {George}, {Gladders}, {Gonzalez}, {Greve}, {Gullberg},
+  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hoover}, {Hrubes}, {Hunter},
+  {Keisler}, {Lee}, {Leitch}, {Lueker}, {Luong-van}, {Malkan}, {McIntyre},
+  {McMahon}, {Mehl}, {Menten}, {Meyer}, {Mocanu}, {Murphy}, {Natoli}, {Padin},
+  {Plagge}, {Reichardt}, {Rest}, {Ruel}, {Ruhl}, {Sharon}, {Schaffer}, {Shaw},
+  {Shirokoff}, {Spilker}, {Stalder}, {Staniszewski}, {Stark}, {Story},
+  {Vanderlinde}, {Welikala}, \& {Williamson}}]{vieira:13}
+{Vieira}, J.~D., {Marrone}, D.~P., {Chapman}, S.~C., {et~al.} 2013, \nat, 495,
+  344, 1303.2723
+
+\bibitem[{{Wallington} \& {Narayan}(1993)}]{Wallington:93}
+{Wallington}, S., \& {Narayan}, R. 1993, \apj, 403, 517
+
+\bibitem[{{Wei{\ss}} {et~al.}(2013){Wei{\ss}}, {De Breuck}, {Marrone},
+  {Vieira}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss}, {Benson},
+  {B{\'e}thermin}, {Biggs}, {Bleem}, {Bock}, {Bothwell}, {Bradford}, {Brodwin},
+  {Carlstrom}, {Chang}, {Chapman}, {Crawford}, {Crites}, {de Haan}, {Dobbs},
+  {Downes}, {Fassnacht}, {George}, {Gladders}, {Gonzalez}, {Greve},
+  {Halverson}, {Hezaveh}, {High}, {Holder}, {Holzapfel}, {Hoover}, {Hrubes},
+  {Husband}, {Keisler}, {Lee}, {Leitch}, {Lueker}, {Luong-Van}, {Malkan},
+  {McIntyre}, {McMahon}, {Mehl}, {Menten}, {Meyer}, {Murphy}, {Padin},
+  {Plagge}, {Reichardt}, {Rest}, {Rosenman}, {Ruel}, {Ruhl}, {Schaffer},
+  {Shirokoff}, {Spilker}, {Stalder}, {Staniszewski}, {Stark}, {Story},
+  {Vanderlinde}, {Welikala}, \& {Williamson}}]{Weiss:13}
+{Wei{\ss}}, A., {De Breuck}, C., {Marrone}, D.~P., {et~al.} 2013, \apj, 767,
+  88, 1303.2726
+
+\bibitem[{{Winn} {et~al.}(2004){Winn}, {Rusin}, \& {Kochanek}}]{Winn:04}
+{Winn}, J.~N., {Rusin}, D., \& {Kochanek}, C.~S. 2004, \nat, 427, 613,
+  astro-ph/0312136
+
+\bibitem[{{Zhang} {et~al.}(2007){Zhang}, {Jackson}, {Porcas}, \&
+  {Browne}}]{Zhang:07}
+{Zhang}, M., {Jackson}, N., {Porcas}, R.~W., \& {Browne}, I.~W.~A. 2007,
+  \mnras, 377, 1623, astro-ph/0703226
+
+\end{thebibliography}
 

### 2015-01-01 ms.tex
incorporating some of referees suggestions

@@
 For double and quad image configurations, the theory of strong lensing predicts a third and a fifth image near the centers of lensing galaxies.
-Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making its detection difficult \citep[e.g.,][]{Jackson:13}.
-It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
+\blue{Realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.}
+\red{Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.}  It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
 
@@
 To avoid the possibility of absorption in the lens, most searches have focused on lensed radio sources.
-The radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies \citep[e.g.,][]{Zhang:07}.
+The radio spectra of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies \citep[e.g.,][]{Zhang:07}.
 
@@
 \end{center}
-\caption{ Left panel shows the strongly lensed images of a background source, when the lensing potential is very steep and cuspy, resulting in large demagnification (and disappearance) of the central image.
+\caption{ Left panel shows the strongly lensed images of a background source \blue{with a Gaussian light profile (FWHM 1170 pc)}, when the lensing potential is very steep and cuspy, resulting in large demagnification (and disappearance) of the central image.
 The right panel shows images for the same lens parameters and a core of 400 pc.
@@
 We modeled the lens potential as a sum of three components: dark matter, stellar population and a single central SMBH.
-The dark matter component was modeled as a singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile in the innermost regions \citep{Golse:02}.
+The dark matter component was modeled as \blue{an elliptical} singular power-law with a slope of 0.1, in agreement with the projected surface mass density of the NFW profile in the innermost regions \citep{Golse:02}.
 As  pointed out by \citet{Keeton:03}, due to its expected flatness in these regimes, the dark matter component has negligible influence on the central images (although models with dark matter cusps have been entertained).
-The stellar population is modeled as a a cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma_s}$.
-Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curve).
+The stellar population is modeled as \blue{an elliptical} cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma_s}$.
+\blue{The deflection angles for elliptical cored power-law models were calculated using FastEll \citep{Barkana:98}.}  Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curve).
 The grey dashed curves show a few examples of core-sersic models with parameters taken from \citet{Ferrarese:06}.
@@
 
-For simulations where we calculated the detection significance of the demagnified image, we computed the magnification at every pixel in the image plane and generated maps with and without the the demagnified flux and evaluated the detection significance of the central image by comparing the two resulting visibility sets.
+For simulations where we calculated the detection significance of the demagnified image, we computed the magnification at every pixel in the image plane and generated maps with and without the demagnified flux and evaluated the detection significance of the central image by comparing the two resulting visibility sets.
 In other simulations, where the constrains on parameters were needed, we used a Fisher analysis to compute the full covariance of all parameters.
@@
 SMBHs demagnify the images on scales comparable to the size of their Einstein radii ($\sim30$ mas for a $2\times10^8M_{\odot}$ SMBH).
-The dashed curves in Figure \ref{fig:3} show the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.
+\red{The dashed curves in Figure \ref{fig:3} show the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.}
+\blue{A comparison of the thick black dashed curve to the solid black curve in Figure \ref{fig:3} shows the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.}
 
@@
 We performed a Fisher analysis to examine the constraints and parameter degeneracies in simulations in which the central images were detected, as well as those in which they were below the detection limit.
-All model parameters were included in the Fisher matrix, and nuisance parameters were later marginalize over (e.g.
+All model parameters were included in the Fisher matrix, and nuisance parameters were later marginalized over (e.g.
 intrinsic source flux and position).
@@
 \bibliographystyle{apj}
-%\bibliography{references}
-
-\begin{thebibliography}{36}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem[{{Barnab{\`e}} {et~al.}(2014){Barnab{\`e}}, {Spiniello}, \&
-  {Koopmans}}]{Barnabe:14}
-{Barnab{\`e}}, M., {Spiniello}, C., \& {Koopmans}, L.~V.~E. 2014, ArXiv
-  e-prints, 1409.4197
-
-\bibitem[{{Barnes} \& {Hernquist}(1992)}]{Barnes:92}
-{Barnes}, J.~E., \& {Hernquist}, L. 1992, \araa, 30, 705
-
-\bibitem[{{Begelman} {et~al.}(1980){Begelman}, {Blandford}, \&
-  {Rees}}]{Begelman:80}
-{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1980, \nat, 287, 307
-
-\bibitem[{{Bennert} {et~al.}(2010){Bennert}, {Treu}, {Woo}, {Malkan}, {Le
-  Bris}, {Auger}, {Gallagher}, \& {Blandford}}]{Bennert:10}
-{Bennert}, V.~N., {Treu}, T., {Woo}, J.-H., {et~al.} 2010, \apj, 708, 1507,
-  0911.4107
-
-\bibitem[{{Bolton} {et~al.}(2008){Bolton}, {Treu}, {Koopmans}, {Gavazzi},
-  {Moustakas}, {Burles}, {Schlegel}, \& {Wayth}}]{Bolton:08}
-{Bolton}, A.~S., {Treu}, T., {Koopmans}, L.~V.~E., {et~al.} 2008, \apj, 684,
-  248, 0805.1932
-
-\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
-  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
-  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell:12}
-{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
-  3047, 1205.1511
-
-\bibitem[{{Bussmann} {et~al.}(2013){Bussmann}, {P{\'e}rez-Fournon}, {Amber},
-  {Calanog}, {Gurwell}, {Dannerbauer}, {De Bernardis}, {Fu}, {Harris}, {Krips},
-  {Lapi}, {Maiolino}, {Omont}, {Riechers}, {Wardlow}, {Baker}, {Birkinshaw},
-  {Bock}, {Bourne}, {Clements}, {Cooray}, {De Zotti}, {Dunne}, {Dye}, {Eales},
-  {Farrah}, {Gavazzi}, {Gonz{\'a}lez Nuevo}, {Hopwood}, {Ibar}, {Ivison},
-  {Laporte}, {Maddox}, {Mart{\'{\i}}nez-Navajas}, {Michalowski}, {Negrello},
-  {Oliver}, {Roseboom}, {Scott}, {Serjeant}, {Smith}, {Smith}, {Streblyanska},
-  {Valiante}, {van der Werf}, {Verma}, {Vieira}, {Wang}, \&
-  {Wilner}}]{bussmann:13}
-{Bussmann}, R.~S., {P{\'e}rez-Fournon}, I., {Amber}, S., {et~al.} 2013, \apj,
-  779, 25, 1309.0836
-
-\bibitem[{{Dalal} \& {Kochanek}(2002)}]{dalal:02}
-{Dalal}, N., \& {Kochanek}, C.~S. 2002, \apj, 572, 25, astro-ph/0111456
-
-\bibitem[{{Ebisuzaki} {et~al.}(1991){Ebisuzaki}, {Makino}, \&
-  {Okumura}}]{Ebisuzaki:91}
-{Ebisuzaki}, T., {Makino}, J., \& {Okumura}, S.~K. 1991, \nat, 354, 212
-
-\bibitem[{{Evans} \& {Hunter}(2002)}]{Evans:02}
-{Evans}, N.~W., \& {Hunter}, C. 2002, \apj, 575, 68, astro-ph/0204206
-
-\bibitem[{{Ferrarese} \& {Merritt}(2000)}]{Ferrarese:00}
-{Ferrarese}, L., \& {Merritt}, D. 2000, \apjl, 539, L9, astro-ph/0006053
-
-\bibitem[{{Ferrarese} {et~al.}(2006){Ferrarese}, {C{\^o}t{\'e}}, {Jord{\'a}n},
-  {Peng}, {Blakeslee}, {Piatek}, {Mei}, {Merritt}, {Milosavljevi{\'c}},
-  {Tonry}, \& {West}}]{Ferrarese:06}
-{Ferrarese}, L., {C{\^o}t{\'e}}, P., {Jord{\'a}n}, A., {et~al.} 2006, \apjs,
-  164, 334, astro-ph/0602297
-
-\bibitem[{{Gavazzi} {et~al.}(2007){Gavazzi}, {Treu}, {Rhodes}, {Koopmans},
-  {Bolton}, {Burles}, {Massey}, \& {Moustakas}}]{Gavazzi:07}
-{Gavazzi}, R., {Treu}, T., {Rhodes}, J.~D., {et~al.} 2007, \apj, 667, 176,
-  astro-ph/0701589
-
-\bibitem[{{Gebhardt} {et~al.}(2000){Gebhardt}, {Bender}, {Bower}, {Dressler},
-  {Faber}, {Filippenko}, {Green}, {Grillmair}, {Ho}, {Kormendy}, {Lauer},
-  {Magorrian}, {Pinkney}, {Richstone}, \& {Tremaine}}]{Gebhardt:00}
-{Gebhardt}, K., {Bender}, R., {Bower}, G., {et~al.} 2000, \apjl, 539, L13,
-  astro-ph/0006289
-
-\bibitem[{{Golse} \& {Kneib}(2002)}]{Golse:02}
-{Golse}, G., \& {Kneib}, J.-P. 2002, \aap, 390, 821, astro-ph/0112138
-
-\bibitem[{{Hezaveh} {et~al.}(2014){Hezaveh}, {Dalal}, {Holder}, {Kisner}, \&
-  {Kuhlen}}]{hezaveh:14a}
-{Hezaveh}, Y., {Dalal}, N., {Holder}, G., {Kisner}, T., \& {Kuhlen}, M. 2014,
-  ArXiv e-prints, 1403.2720
-
-\bibitem[{{Hezaveh}(2014)}]{hezaveh:14b}
-{Hezaveh}, Y.~D. 2014, \apjl, 791, L41, 1408.3631
-
-\bibitem[{{Hezaveh} \& {Holder}(2011)}]{hezaveh:11}
-{Hezaveh}, Y.~D., \& {Holder}, G.~P. 2011, \apj, 734, 52, 1010.0998
-
-\bibitem[{{Hezaveh} {et~al.}(2013){Hezaveh}, {Marrone}, {Fassnacht}, {Spilker},
-  {Vieira}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss}, {Benson},
-  {Bleem}, {Bothwell}, {Brodwin}, {Carlstrom}, {Chang}, {Chapman}, {Crawford},
-  {Crites}, {De Breuck}, {de Haan}, {Dobbs}, {Fomalont}, {George}, {Gladders},
-  {Gonzalez}, {Greve}, {Halverson}, {High}, {Holder}, {Holzapfel}, {Hoover},
-  {Hrubes}, {Husband}, {Hunter}, {Keisler}, {Lee}, {Leitch}, {Lueker},
-  {Luong-Van}, {Malkan}, {McIntyre}, {McMahon}, {Mehl}, {Menten}, {Meyer},
-  {Mocanu}, {Murphy}, {Natoli}, {Padin}, {Plagge}, {Reichardt}, {Rest}, {Ruel},
-  {Ruhl}, {Sharon}, {Schaffer}, {Shaw}, {Shirokoff}, {Stalder}, {Staniszewski},
-  {Stark}, {Story}, {Vanderlinde}, {Wei{\ss}}, {Welikala}, \&
-  {Williamson}}]{hezaveh:13b}
-{Hezaveh}, Y.~D., {Marrone}, D.~P., {Fassnacht}, C.~D., {et~al.} 2013, \apj,
-  767, 132, 1303.2722
-
-\bibitem[{{Inada} {et~al.}(2008){Inada}, {Oguri}, {Falco}, {Broadhurst},
-  {Ofek}, {Kochanek}, {Sharon}, \& {Smith}}]{Inada:08}
-{Inada}, N., {Oguri}, M., {Falco}, E.~E., {et~al.} 2008, \pasj, 60, L27,
-  0808.1769
-
-\bibitem[{{Jackson}(2013)}]{Jackson:13}
-{Jackson}, N. 2013, Bulletin of the Astronomical Society of India, 41, 19,
-  1304.4172
-
-\bibitem[{{Keeton}(2003)}]{Keeton:03}
-{Keeton}, C.~R. 2003, \apj, 582, 17, astro-ph/0206243
-
-\bibitem[{{Kormendy} \& {Bender}(2009)}]{Kormendy:09}
-{Kormendy}, J., \& {Bender}, R. 2009, \apjl, 691, L142, 0901.3778
-
-\bibitem[{{Kormendy} \& {Ho}(2013)}]{Kormendy:13}
-{Kormendy}, J., \& {Ho}, L.~C. 2013, \araa, 51, 511, 1304.7762
-
-\bibitem[{{Kormendy} \& {Richstone}(1995)}]{Kormendy:95}
-{Kormendy}, J., \& {Richstone}, D. 1995, \araa, 33, 581
-
-\bibitem[{{Li} {et~al.}(2012){Li}, {Mao}, {Gao}, {Loeb}, \& {di
-  Stefano}}]{Li:12}
-{Li}, N., {Mao}, S., {Gao}, L., {Loeb}, A., \& {di Stefano}, R. 2012, \mnras,
-  419, 2424, 1110.0887
-
-\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
-  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
-  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
-  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
-  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
-  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
-  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
-  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
-  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
-  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
-  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
-  {Maloney}, {Matsuhara}, {Michaowski}, {Murphy}, {Naylor}, {Nguyen},
-  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
-  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{negrello:10}
-{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330,
-  800, 1011.1255
-
-\bibitem[{{Rocha} {et~al.}(2013){Rocha}, {Peter}, {Bullock}, {Kaplinghat},
-  {Garrison-Kimmel}, {O{\~n}orbe}, \& {Moustakas}}]{Rocha:13}
-{Rocha}, M., {Peter}, A.~H.~G., {Bullock}, J.~S., {et~al.} 2013, \mnras, 430,
-  81, 1208.3025
-
-\bibitem[{{Thomas} {et~al.}(2014){Thomas}, {Saglia}, {Bender}, {Erwin}, \&
-  {Fabricius}}]{Thomas:14}
-{Thomas}, J., {Saglia}, R.~P., {Bender}, R., {Erwin}, P., \& {Fabricius}, M.
-  2014, \apj, 782, 39, 1311.3783
-
-\bibitem[{{Tremaine} {et~al.}(2002){Tremaine}, {Gebhardt}, {Bender}, {Bower},
-  {Dressler}, {Faber}, {Filippenko}, {Green}, {Grillmair}, {Ho}, {Kormendy},
-  {Lauer}, {Magorrian}, {Pinkney}, \& {Richstone}}]{Tremaine:02}
-{Tremaine}, S., {Gebhardt}, K., {Bender}, R., {et~al.} 2002, \apj, 574, 740,
-  astro-ph/0203468
-
-\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
-  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
-  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
-  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
-  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
-  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
-  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
-  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
-  {Zenteno}}]{vieira:10}
-{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
-  763, 0912.2338
-
-\bibitem[{{Vieira} {et~al.}(2013){Vieira}, {Marrone}, {Chapman}, {De Breuck},
-  {Hezaveh}, {Wei{$\beta$}}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss},
-  {Benson}, {Biggs}, {Bleem}, {Bock}, {Bothwell}, {Bradford}, {Brodwin},
-  {Carlstrom}, {Chang}, {Crawford}, {Crites}, {de Haan}, {Dobbs}, {Fomalont},
-  {Fassnacht}, {George}, {Gladders}, {Gonzalez}, {Greve}, {Gullberg},
-  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hoover}, {Hrubes}, {Hunter},
-  {Keisler}, {Lee}, {Leitch}, {Lueker}, {Luong-van}, {Malkan}, {McIntyre},
-  {McMahon}, {Mehl}, {Menten}, {Meyer}, {Mocanu}, {Murphy}, {Natoli}, {Padin},
-  {Plagge}, {Reichardt}, {Rest}, {Ruel}, {Ruhl}, {Sharon}, {Schaffer}, {Shaw},
-  {Shirokoff}, {Spilker}, {Stalder}, {Staniszewski}, {Stark}, {Story},
-  {Vanderlinde}, {Welikala}, \& {Williamson}}]{vieira:13}
-{Vieira}, J.~D., {Marrone}, D.~P., {Chapman}, S.~C., {et~al.} 2013, \nat, 495,
-  344, 1303.2723
-
-\bibitem[{{Wallington} \& {Narayan}(1993)}]{Wallington:93}
-{Wallington}, S., \& {Narayan}, R. 1993, \apj, 403, 517
-
-\bibitem[{{Wei{\ss}} {et~al.}(2013){Wei{\ss}}, {De Breuck}, {Marrone},
-  {Vieira}, {Aguirre}, {Aird}, {Aravena}, {Ashby}, {Bayliss}, {Benson},
-  {B{\'e}thermin}, {Biggs}, {Bleem}, {Bock}, {Bothwell}, {Bradford}, {Brodwin},
-  {Carlstrom}, {Chang}, {Chapman}, {Crawford}, {Crites}, {de Haan}, {Dobbs},
-  {Downes}, {Fassnacht}, {George}, {Gladders}, {Gonzalez}, {Greve},
-  {Halverson}, {Hezaveh}, {High}, {Holder}, {Holzapfel}, {Hoover}, {Hrubes},
-  {Husband}, {Keisler}, {Lee}, {Leitch}, {Lueker}, {Luong-Van}, {Malkan},
-  {McIntyre}, {McMahon}, {Mehl}, {Menten}, {Meyer}, {Murphy}, {Padin},
-  {Plagge}, {Reichardt}, {Rest}, {Rosenman}, {Ruel}, {Ruhl}, {Schaffer},
-  {Shirokoff}, {Spilker}, {Stalder}, {Staniszewski}, {Stark}, {Story},
-  {Vanderlinde}, {Welikala}, \& {Williamson}}]{Weiss:13}
-{Wei{\ss}}, A., {De Breuck}, C., {Marrone}, D.~P., {et~al.} 2013, \apj, 767,
-  88, 1303.2726
-
-\bibitem[{{Winn} {et~al.}(2004){Winn}, {Rusin}, \& {Kochanek}}]{Winn:04}
-{Winn}, J.~N., {Rusin}, D., \& {Kochanek}, C.~S. 2004, \nat, 427, 613,
-  astro-ph/0312136
-
-\bibitem[{{Zhang} {et~al.}(2007){Zhang}, {Jackson}, {Porcas}, \&
-  {Browne}}]{Zhang:07}
-{Zhang}, M., {Jackson}, N., {Porcas}, R.~W., \& {Browne}, I.~W.~A. 2007,
-  \mnras, 377, 1623, astro-ph/0703226
-
-\end{thebibliography}
+\bibliography{references}
 

### 2015-01-05 ms.tex
more revisions for resubmission

@@
 \blue{Realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.}
-\red{Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.}  It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
+%\red{Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.}
+ It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
 
@@
 
-The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.,][]{Wallington:93, Evans:02, Keeton:03}.
-These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}.
+The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.,][]{Wallington:93, Mao:01, Evans:02, Keeton:03}.
+These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}, \blue{and that cuspy profiles (or SMBHs) can suppress the flux of the central images \citep[e.g.,][]{Bowman:04,Rusin:05,Mao:12}.}
 Observational searches for these images have found a number of candidates. Although observations
@@
 SMBHs demagnify the images on scales comparable to the size of their Einstein radii ($\sim30$ mas for a $2\times10^8M_{\odot}$ SMBH).
-\red{The dashed curves in Figure \ref{fig:3} show the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.}
+%\red{The dashed curves in Figure \ref{fig:3} show the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.}
 \blue{A comparison of the thick black dashed curve to the solid black curve in Figure \ref{fig:3} shows the suppression of the fluxes of central images in presence of a $2\times10^8M_{\odot}$ SMBH.}
@@
 
+\begin{figure}
+\begin{center}
+\centering
+\includegraphics[trim= 0 0 0 0, clip, width=0.48\textwidth]{figures/f_06.eps}
+\centering
+\end{center}
+\vspace{-1mm}
+\caption{\blue{The two top panels show the magnification cross-sections of two sources with different sizes (left: 100 pc, right 500 pc in radius) behind a lens containing a black hole with a mass of $1\times 10^8 M_{\odot}$.
+The magnification at the central regions of the left panel approaches zero and the central image does not form (the color scale has been clipped at $10^{-2.5}$).
+The lower panel shows the magnification at the center (when the source is perfectly behind the lens) as a function of source size).}
+\label{figMu}}
+\vspace{-1.5mm}
+\end{figure}
+
 We also find that the detection significance of the central images can significantly \emph{increase} for an extended source with a radius of 1 kpc compared to a point source.
@@
 In contrast, the flux of a source with a radius of 250 pc can be severely supressed (dotted grey curve).
+\blue{This effect is illustrated in Figure \ref{figMu} where the effects of source size on magnification are shown.
+The two top panels of Figure \ref{figMu} show the magnification cross-section (flux magnification as a function of source position behind the lens) for two sources with different sizes (left: 100 pc, right: 500 pc in radius).
+For a compact source (top left panel) in the central regions the magnification approaches zero and the central image does not form.
+For more extended sources, however, even when the source is exactly behind the lens, the large extent of the source allows covering higher magnification regions, increasing the total flux magnification.
+The bottom panel shows the magnification as a function of source size, for a source that is located on the lens axis.}
 As the source galaxies are undergoing prodigious star formation, these large source sizes are reasonable and in agreement with observations \citep{hezaveh:13b}.

### 2015-01-06 ms.tex
more revisions for resubmission

@@
 For double and quad image configurations, the theory of strong lensing predicts a third and a fifth image near the centers of lensing galaxies.
-\blue{Realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.}
+\blue{Realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.
+If the lens galaxies have cuspy central profiles with steep slopes or very massive SMBHs, this central image may not form at all.}
 %\red{Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.}

### 2015-01-06 response.txt
Checked through response with Yashar

We are grateful to the referee for careful reading of the 
manuscript and useful suggestions.

==================================================================================

The paper makes an interesting point that having extended sources 
can significantly increase the detection significance because such 
sources "occupy a larger area of the source plane, which may cover 
regions with higher magnifications".

I think it could be useful to see this point illustrated, perhaps 
with a magnification map and a curve showing magnification as a 
function of source size (at a given position).

Also, the paper argues that central images can offer good 
constraints on the core size and black hole mass.

It would be nice to have some intuition about which image 
properties provide the most information: position, brightness, 
resolved shape, or all of the above?

The text broaches this issue in Section 3.2 but does not go into 
detail. In both of these cases, my personal preference would be to 
have a more extended discussion (with figures) even if that means 
the paper becomes too long for ApJL. I do want to emphasize that 
this is a personal preference; the authors may be satisfied with 
the level of the discussion in its present form.

>> RESPONSE: We have added a figure (Figure 4) showing the magnification 
>> cross-section for two sources with different sizes. We have also 
>> added a few sentences to the text to explain this, as follows:

"This effect is illustrated in Figure 4 where the effects of source 
size on magnification are shown. The two top panels of Figure 4 
show the source plane magnification (flux magnification as a 
function of source position behind the lens) for two sources with 
different sizes (left: 100 pc, right: 500 pc in radius). For a 
compact source (top left panel) in the central regions the 
magnification approaches zero and the central image does not form. 
For more extended sources, however, even when the source is exactly 
behind the lens, the large extent of the source allows the covering of 
higher magnification regions, increasing the total flux 
magnification. The bottom panel shows the magnification as a 
function of source size, for a source that is located on the lens 
axis."

==================================================================================

My second comment is that there is little discussion of existing 
literature on gravitational lensing, central images, and 
supermassive black holes. Here are a few papers that seem worthy of 
mention (there may be others as well):

- Mao, Witt & Koopmans, http://adsabs.harvard.edu/abs/2001MNRAS.323..301M
- Bowman, Hewitt & Kiger, http://adsabs.harvard.edu/abs/2004ApJ...617...81B
- Rusin, Keeton & Winn, http://adsabs.harvard.edu/abs/2005ApJ...627L..93R
- Mao & Witt, http://adsabs.harvard.edu/abs/2012MNRAS.420..792M

>> RESPONSE: The citations and a short description have been added 
>> to the introduction.

==================================================================================

What was the source size used to generate Figure 1?

>> RESPONSE: The source has a Gaussian profile with FWHM of 1170 pc 
>> (rms of 500 pc). We have added this information to the caption:

" a background source with a Gaussian light profile (FWHM 
$\sim1100$ pc)..."

==================================================================================

How was the black hole mass chosen? I assume it follows the M-sigma 
relation, but that is not discussed explicitly (perhaps because the 
effective velocity dispersion of the model galaxy is not 
mentioned).

>> RESPONSE:

==================================================================================

The analysis uses circular mass distributions. How would it be 
affected by ellipticity and/or external shear?

>> We thank the referee for pointing out the ambiguity of the text 
>> about this. In fact, elliptical power-law models were used in 
>> the calculations and the deflection angles were computed using 
>> the FastEll code. We ran simulations with ellipticities of 0.2 
>> and 0.4. We have added a few words to clarify this, as follows:

"The stellar population is modeled as an elliptical cored 
power-law. The deflection angles for elliptical cored power-law 
models were calculated using FastEll (Barkana 1998)."

==================================================================================

"For double and quad image configurations, the theory of strong 
lensing predicts a third and a fifth image near the centers of 
lensing galaxies." Strictly speaking, that statement applies only 
under certain conditions. Even if those conditions are thought to 
apply to realistic galaxy models, it is important to understand 
that the theoretical statement is nuanced. For example, there is no 
central image if the surface mass density has a central cusp that 
is steeper than 1/r, or if the SMBH exceeds a threshold in mass. If 
the black hole mass is below that threshold, there can actually be 
more than one central image.

>> RESPONSE:

==================================================================================

"Unlike the other lensed images, which are magnified..." It is 
possible for non-central images to be demagnified. The only true 
guarantee from lens theory is that at least one image has a 
magnification greater than unity.

>> RESPONSE: We have modified the wording to "Realistic galaxy 
>> density profiles produce central images that are almost always 
>> demagnified, making their detection difficult."

==================================================================================

"The dashed curves in Figure 3 show the suppression of the fluxes 
of central images in presence of a 2e8 Msun SMBH." There is only 
one relevant dashed curve in Figure 3, and it shows a case with no 
black hole. The suppression effect is therefore seen not in the 
dashed curve itself, but in a comparison of the solid curves to the 
dashed curve.

>> RESPONSE: We have changed the wording to clarify this, as follows:

"A comparison of the thick black dashed curve to the solid black 
curve in Figure 3 shows the suppression of the fluxes of central 
images in presence of a 2e8 Msun SMBH."

==================================================================================

"The radio spectrum of candidate central images have been used" -- 
here the noun ("spectrum") is singular while the verb ("have") is 
plural.

>> DONE

==================================================================================

"generated maps with and without the the demagnified flux" -- 
double "the".

>> DONE

==================================================================================

"and nuisance parameters were later marginalize over" -- should be 
"marginalized".

>> DONE

### 2015-01-06 ms.tex
Checked through response with Yashar

@@
 \vspace{-1mm}
-\caption{\blue{The two top panels show the magnification cross-sections of two sources with different sizes (left: 100 pc, right 500 pc in radius) behind a lens containing a black hole with a mass of $1\times 10^8 M_{\odot}$.
-The magnification at the central regions of the left panel approaches zero and the central image does not form (the color scale has been clipped at $10^{-2.5}$).
-The lower panel shows the magnification at the center (when the source is perfectly behind the lens) as a function of source size).}
+\caption{\blue{The two top panels show the source plane magnification 
+maps for two sources, with different sizes (left: 100 pc, 
+right 500 pc in radius) behind a lens containing a black hole with 
+a mass of $1\times 10^8 M_{\odot}$. The magnification at the 
+central regions of the left panel approaches zero and the central 
+image does not form (the color scale has been clipped at 
+$10^{-2.5}$). The lower panel shows the magnification at the center 
+(when the source is perfectly behind the lens) as a function of 
+source size).}
 \label{figMu}}
@@
 
-We also find that the detection significance of the central images can significantly \emph{increase} for an extended source with a radius of 1 kpc compared to a point source.
-Since extended sources occupy a larger area of the source plane, which may cover regions with higher magnifications, the resulting flux can be larger than the flux of more compact sources.
-The solid blue curve in Figure \ref{fig:3} shows the increase in the flux of the demagnified image for a larger source (with a radius of 1 kpc).
-In contrast, the flux of a source with a radius of 250 pc can be severely supressed (dotted grey curve).
-\blue{This effect is illustrated in Figure \ref{figMu} where the effects of source size on magnification are shown.
-The two top panels of Figure \ref{figMu} show the magnification cross-section (flux magnification as a function of source position behind the lens) for two sources with different sizes (left: 100 pc, right: 500 pc in radius).
-For a compact source (top left panel) in the central regions the magnification approaches zero and the central image does not form.
-For more extended sources, however, even when the source is exactly behind the lens, the large extent of the source allows covering higher magnification regions, increasing the total flux magnification.
-The bottom panel shows the magnification as a function of source size, for a source that is located on the lens axis.}
-As the source galaxies are undergoing prodigious star formation, these large source sizes are reasonable and in agreement with observations \citep{hezaveh:13b}.
-More extended and intrinsically brighter emission lines such as C[II], the brightest molecular line in high redshift galaxies, may therefore be the most ideal targets for such observations.
+We also find that the detection significance of the central images 
+can significantly \emph{increase} for an extended source with a 
+radius of 1 kpc compared to a point source. Since extended sources 
+occupy a larger area of the source plane, which may cover regions 
+with higher magnifications, the resulting flux can be larger than 
+the flux of more compact sources.
+
+The solid blue curve in Figure \ref{fig:3} shows the increase in 
+the flux of the demagnified image for a larger source (with a 
+radius of 1 kpc). In contrast, the flux of a source with a radius 
+of 250 pc can be severely supressed (dotted grey curve). \blue{This 
+effect is illustrated in Figure \ref{figMu} where the effects of 
+source size on magnification are shown. The two top panels of 
+Figure~\ref{figMu} show the source plane magnification (flux 
+magnification as a function of source position behind the lens) for 
+two sources with different sizes (left: 100 pc, right: 500 pc in 
+radius). For a compact source (top left panel) in the central 
+regions the magnification approaches zero and the central image 
+does not form. For more extended sources, however, even when the 
+source is exactly behind the lens, the large extent of the source 
+allows covering higher magnification regions, increasing the total 
+flux magnification.
+The bottom panel shows the magnification as a function of source 
+size, for a source that is located on the lens axis.}
+As the source galaxies are undergoing prodigious star formation, 
+these large source sizes are reasonable and in agreement with 
+observations \citep{hezaveh:13b}.
+More extended and intrinsically brighter emission lines such as 
+C[II], the brightest molecular line in high redshift galaxies, may 
+therefore be the most ideal targets for such observations.
 

### 2015-01-06 response.txt
final revisions for resubmission

@@
 We are grateful to the referee for careful reading of the 
-manuscript and useful suggestions.
+manuscript and helpful suggestions.
 
@@
 
-" a background source with a Gaussian light profile (FWHM 
-$\sim1100$ pc)..."
+" a background source with a Gaussian light profile (FWHM 1170 pc)..."
 
@@
 
->> RESPONSE:
+>> RESPONSE: For a lens galaxy with a sigma of 200 km/s the black hole
+mass on the M-sigma relation is about 2e8 Msun (from Kormendy & Ho 2013
+and McConnell et al. 2011). The giant elliptical strong lenses have typical
+velocity dispersions of  200 km/s (Sonnenfeld et al. 2013), so we think that 
+black holes in the 10^8 Msun mass range are plausible for these galaxies.
+We have added this information to the simulation section:
 
+"Lensing galaxies are typically massive ellipticals with velocity dispersions 
+of order 200 km/s (e.g., Sonnenfeld et al. 2013). From the M-σ relation, we predict
+that these galaxies should contain black holes with masses in excess 
+of 2 x 10^8Msun (e.g., Kormendy & Ho 2013). In our simulations we have chosen 
+black holes with masses of 1, 2, and 4 x 108 Msun ."
 ==================================================================================
@@
 
->> RESPONSE:
+>> RESPONSE: We have tried to qualify this with the sentences that
+follow this description:
+
+"For double and quad image configurations, the theory of strong lensing 
+predicts a third and a fifth image near the centers of lensing galaxies. 
+However, realistic galaxy density profiles produce central images that are 
+almost always demagnified, making their detection difficult (e.g., Jackson 2013). 
+If the lens galaxies have cuspy central profiles with steep slopes or very 
+massive SMBHs, this central image may not form at all."
 
@@
 
->> DONE
+>> Corrected
 
@@
 
->> DONE
+>> Corrected

### 2015-01-06 ms.tex
final revisions for resubmission

@@
 For double and quad image configurations, the theory of strong lensing predicts a third and a fifth image near the centers of lensing galaxies.
-\blue{Realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.
+\blue{However, realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.
 If the lens galaxies have cuspy central profiles with steep slopes or very massive SMBHs, this central image may not form at all.}
@@
 The black hole was modeled as a simple point mass at the center of the potential. 
+\blue{Lensing galaxies are typically massive ellipticals with velocity dispersions of order 200 km/s \citep[e.g.,][]{Sonnenfeld:13}.
+From the M-$\sigma$ relation, we predict that these galaxies should contain black holes with masses in excess of $2\times10^8 M_{\odot}$ \citep[e.g.,][]{Kormendy:13}.
+In our simulations we have chosen black holes with masses of 1, 2, and $4 \times 10^8 M_{\odot}$.}
+
 We assumed that all the three components are concentric, though we note that two- and three-black hole interactions may invalidate this assumption.
@@
 The fiducial model (solid black curve) corresponds to $\gamma_{stellar}=1.0$, $M_{\mathrm{BH}}=2\times10^8 M_{\odot}$, and a source size of 500 pc (radius).
-The dashed black curve shows the detection significance when the SMBH is removed and the solid red curve shows the effect of a steeper density profile ($\gamma_{\mathrm{stellar}}=1.1$).
+\blue{The lens has an ellipticity of 0.2.} The dashed black curve shows the detection significance when the SMBH is removed and the solid red curve shows the effect of a steeper density profile ($\gamma_{\mathrm{stellar}}=1.1$).
 The solid blue and gray dotted curves show the detections for a source with a radius of 1 kpc and 250 pc respectively.

### 2015-01-07 response.txt
Tiny corrections, flagged changes in blue to referee.

@@
 We are grateful to the referee for careful reading of the 
-manuscript and helpful suggestions.
+manuscript and helpful suggestions. We have addressed each of their 
+points, highlighting the changes to the manuscript in blue.
 
@@
 Also, the paper argues that central images can offer good 
-constraints on the core size and black hole mass.
-
-It would be nice to have some intuition about which image 
-properties provide the most information: position, brightness, 
-resolved shape, or all of the above?
+constraints on the core size and black hole mass. It would be nice 
+to have some intuition about which image properties provide the 
+most information: position, brightness, resolved shape, or all of 
+the above?
 
@@
 >> RESPONSE: For a lens galaxy with a sigma of 200 km/s the black hole
-mass on the M-sigma relation is about 2e8 Msun (from Kormendy & Ho 2013
-and McConnell et al. 2011). The giant elliptical strong lenses have typical
-velocity dispersions of  200 km/s (Sonnenfeld et al. 2013), so we think that 
-black holes in the 10^8 Msun mass range are plausible for these galaxies.
-We have added this information to the simulation section:
+>> mass on the M-sigma relation is about 2e8 Msun (from Kormendy & Ho 
+>> 2013 and McConnell et al. 2011). The giant elliptical strong lenses 
+>> have typical velocity dispersions of 200 km/s (Sonnenfeld et al. 
+>> 2013), so we think that black holes in the 10^8 Msun mass range are 
+>> plausible for these galaxies. We have added this information to the 
+>> simulation section:
 
-"Lensing galaxies are typically massive ellipticals with velocity dispersions 
-of order 200 km/s (e.g., Sonnenfeld et al. 2013). From the M-σ relation, we predict
-that these galaxies should contain black holes with masses in excess 
-of 2 x 10^8Msun (e.g., Kormendy & Ho 2013). In our simulations we have chosen 
-black holes with masses of 1, 2, and 4 x 108 Msun ."
+"Lensing galaxies are typically massive ellipticals with velocity 
+dispersions of order 200 km/s (e.g., Sonnenfeld et al. 2013). From 
+the M-sigma relation, we predict that these galaxies should contain 
+black holes with masses in excess of 2 x 10^8 Msun (e.g., Kormendy & 
+Ho 2013). In our simulations we have chosen black holes with masses 
+of 1, 2, and 4 x 10^8 Msun."
+
 ==================================================================================
@@
 >> RESPONSE: We have tried to qualify this with the sentences that
-follow this description:
+follow this description in the introduction:
 
-"For double and quad image configurations, the theory of strong lensing 
-predicts a third and a fifth image near the centers of lensing galaxies. 
-However, realistic galaxy density profiles produce central images that are 
-almost always demagnified, making their detection difficult (e.g., Jackson 2013). 
-If the lens galaxies have cuspy central profiles with steep slopes or very 
+"For double and quad image configurations, the theory of strong 
+lensing predicts a third and a fifth image near the centers of 
+lensing galaxies. However, realistic galaxy density profiles 
+produce central images that are almost always demagnified, making 
+their detection difficult (e.g., Jackson 2013). If the lens 
+galaxies have cuspy central profiles with steep slopes or very 
 massive SMBHs, this central image may not form at all."

### 2015-01-07 ms.tex
Tiny corrections, flagged changes in blue to referee.

@@
 \begin{abstract}
-\noindent
-We examine the prospects of detecting demagnified images of gravitational lenses in observations of strongly lensed mm-wave molecular emission lines with ALMA. 
-We model the lensing galaxies as a superposition of a dark matter component, a stellar component, and a central supermassive black hole and assess the detectability of the central images for a range of relevant parameters (e.g., stellar core and black hole mass).
-We find that over a large range of plausible parameters, future deep observations of lensed molecular lines with ALMA should enable  detection of the central images at $\gtrsim 3\sigma$ significance.
-We use a Fisher analysis to examine the  constraints that could be placed on these parameters in various scenarios and find that for large stellar cores, both the core size and the mass of the central SMBHs can be accurately measured.
-We also study the prospects for detecting binary SMBHs with such observations and find that only under rare conditions and with very long integrations ($\sim$40-hr) the masses of both SMBHs may be measured using the distortions of central images.
+
+\noindent We examine the prospects of detecting demagnified images 
+of gravitational lenses in observations of strongly lensed mm-wave 
+molecular emission lines with ALMA. We model the lensing galaxies 
+as a superposition of a dark matter component, a stellar component, 
+and a central supermassive black hole and assess the detectability 
+of the central images for a range of relevant parameters (e.g., 
+stellar core and black hole mass). We find that over a large range 
+of plausible parameters, future deep observations of lensed 
+molecular lines with ALMA should enable detection of the central 
+images at $\gtrsim 3\sigma$ significance. We use a Fisher analysis 
+to examine the constraints that could be placed on these parameters 
+in various scenarios and find that for large stellar cores, both 
+the core size and the mass of the central SMBHs can be accurately 
+measured. We also study the prospects for detecting binary SMBHs 
+with such observations and find that only under rare conditions and 
+with very long integrations ($\sim$40-hr) the masses of both SMBHs 
+may be measured using the distortions of central images.
 
@@
 \section{introduction}
+
 Probing the matter distribution in the innermost kpc of galaxies can answer key questions about super-massive black holes (SMBH), galaxy formation, and dark matter.
@@
 
-Strong gravitational lensing is a powerful tool for probing the matter distribution in distant galaxies.
-Among other things, strong lenses have been used to constrain galaxy masses, density profiles, and abundance of dark matter subhalos \citep[e.g.,][]{dalal:02, Gavazzi:07, Bolton:08}.
-For double and quad image configurations, the theory of strong lensing predicts a third and a fifth image near the centers of lensing galaxies.
-\blue{However, realistic galaxy density profiles produce central images that are almost always \emph{demagnified}\footnote{approximately as $(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface density and $\Sigma_{crit}$ is the critical surface density}, making their detection difficult \citep[e.g.,][]{Jackson:13}.
-If the lens galaxies have cuspy central profiles with steep slopes or very massive SMBHs, this central image may not form at all.}
+Strong gravitational lensing is a powerful tool for probing the 
+matter distribution in distant galaxies. Among other things, strong 
+lenses have been used to constrain galaxy masses, density profiles, 
+and abundance of dark matter subhalos \citep[e.g.,][]{dalal:02, 
+Gavazzi:07, Bolton:08}. For double and quad image configurations, 
+the theory of strong lensing predicts a third and a fifth image 
+near the centers of lensing galaxies.
+\blue{However, realistic galaxy density profiles produce central 
+images that are almost always 
+\emph{demagnified},\footnote{approximately as 
+$(\Sigma/\Sigma_{crit})^{-2}$, where $\Sigma$ is the surface 
+density and $\Sigma_{crit}$ is the critical surface density.} 
+making their detection difficult \citep[e.g.,][]{Jackson:13}. If 
+the lens galaxies have cuspy central profiles with steep slopes or 
+very massive SMBHs, this central image may not form at all.}
 %\red{Unlike the other lensed images, which are magnified, this image can be significantly \emph{demagnified}, making its detection difficult \citep[e.g.,][]{Jackson:13}.}
- It is well-understood that the magnification of the central images is very sensitive to the matter distribution in the innermost regions of lens galaxies: very steep density profiles significantly demagnify the central images, whereas cored or shallow profiles render them brighter (Figure \ref{fig1}).
+It is well-understood that the magnification of the central images 
+is very sensitive to the matter distribution in the innermost 
+regions of lens galaxies: very steep density profiles significantly 
+demagnify the central images, whereas cored or shallow profiles 
+render them brighter (Figure \ref{fig1}).
 

### 2015-01-07 ms.tex
final revisions for resubmission

@@
 of the central images for a range of relevant parameters (e.g., 
-stellar core and black hole mass). We find that over a large range 
+stellar core, black hole mass, and source size). 
+We find that over a large range 
 of plausible parameters, future deep observations of lensed 
 molecular lines with ALMA should enable detection of the central 
-images at $\gtrsim 3\sigma$ significance. We use a Fisher analysis 
+images at $\gtrsim 3\sigma$ significance. 
+We use a Fisher analysis 
 to examine the constraints that could be placed on these parameters 
@@
 the core size and the mass of the central SMBHs can be accurately 
-measured. We also study the prospects for detecting binary SMBHs 
+measured. 
+We also study the prospects for detecting binary SMBHs 
 with such observations and find that only under rare conditions and 
@@
 The stellar population is modeled as \blue{an elliptical} cored power-law, $\Sigma(r)\propto (r^2+R_{\mathrm{core}}^2)^{\gamma_s}$.
-\blue{The deflection angles for elliptical cored power-law models were calculated using FastEll \citep{Barkana:98}.}  Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curve).
+\blue{The deflection angles for elliptical cored power-law models were calculated using FASTELL \citep{Barkana:98}.}  Figure \ref{fig2} shows the stellar component (red curve), dark matter component (black dashed curve) and the sum of the two (black solid curve).
 The grey dashed curves show a few examples of core-sersic models with parameters taken from \citet{Ferrarese:06}.
